### 2015-04-10 documentation/draft.tex
outline of documentation latex file

\documentclass[12pt]{article}

\usepackage{fancyhdr} % Required for custom headers
\usepackage{float}
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{amssymb}
\usepackage{enumerate}

% Margins
\topmargin=-.5in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9in
\headsep=0.25in

\newcommand{\tab}{\hspace*{2em}}

\title{Combined Task and Motion Planner through an Interface Layer}
\author{Alex Gutierrez, Bianca Homberg, and Veronica Lane}

%% ONE SENTENCE PER LINE TO MAKE THIS WORK NICELY IN GIT

\begin{document}

\maketitle

\section{Introduction}

-talk about motion planners and task planners and what they do

-talk about the need to integrate the two together

-why we don't want to just discretize the environment

\section{Problem Statement}

\section{High Level Approach}

\section{Technical Details}

\section{Limitations}

\section{Open Questions}

\section{References}

\end{document}

### 2015-04-11 documentation/draft.tex
wrote intro

@@
 
--talk about motion planners and task planners and what they do
+In order to achieve high level goals a robot must combine task and motion planning.
+A robot uses task planning to determine its long term strategy and motion planning to determine the movements movements it  will execute to achieve the task.
+Effectively combining task and motion planning is an open research problem.
+We developed an interface between the motion and task planning.
+Our system uses off-the-shelf task and motion planners and makes no assumptions about their implementation.
 
--talk about the need to integrate the two together
-
--why we don't want to just discretize the environment
-
+An alternative approach to developing an interface between the task and motion planner is for the task planner to discretize the geometric state space.
+However, the number of required discretizations to solve the problem is generally very large and results in extremely large or infeasible problems.
+The interface allows the task planner state space to use an abstract state space which ignores geometry.
+The interface layer translates geometric constraints and passes them to the task planner.
 \section{Problem Statement}

### 2015-04-11 scripts/pose.py
removed old files

@@ -1,13 +1,0 @@
-class Pose:
-	def __init__(self):
-		self.x = 0
-		self.y = 0
-		self.z = 0
-		self.gripperOpen = True
-	def clone(self):
-		retval = Pose()
-		retval.x = self.x
-		retval.y = self.y
-		retval.z = self.z
-		retval.gripperOpen = self.gripperOpen
-		return retval

### 2015-04-11 scripts/motion_planner_server.py
Covert motion planner service to new message passing protocol

@@ -2,6 +2,7 @@
 
 import sys
 import rospy
+import re
 import moveit_commander
 from task_motion_planner.srv import *
 from task_motion_planner.msg import *
@@ -11,8 +12,8 @@ from std_msgs.msg import String
 
 
 class MotionPlannerServer(object):
-    def __init__(self):
-        pass
+    def __init__(self, max_planning_time):
+        self.max_planning_time = max_planning_time
         
     def get_motion_plan(self, req):
         print "============ Starting Moveit Commander"
@@ -21,60 +22,84 @@ class MotionPlannerServer(object):
         print "============ Setting current state"
         robot = moveit_commander.RobotCommander()
         scene = moveit_commander.PlanningSceneInterface()
+        
+        world_start_state = req.parameters.state.world
+        robot_start_state = req.parameters.state.robot
+        action = re.split(',', req.parameters.action[1:-1])
+        pose_goals = req.parameters.goals
     
         # TODO: Find alternate method for collision objects
         #scene.add_collision_objects(req.parameters.world.collision_objects)
         
-        curr_state = req.parameters.start
+        curr_state = robot_start_state
         res = motion_plan()
     
-        for i in range(len(req.parameters.group_names)):
-            print "============ Move group ", req.parameters.group_names[0]
-            group = moveit_commander.MoveGroupCommander(req.parameters.group_names[0])
+        print "============ Planning actoin ", action[0]
+        for i in range(len(pose_goals)):
+            print "============ Move group ", action[1]
+            group = moveit_commander.MoveGroupCommander(action[1])
         
-            group.set_planning_time(5.0)
+            group.set_planning_time(self.max_planning_time)
             group.set_start_state(curr_state)
-            group.set_pose_target(req.parameters.goals[0])
+            group.set_pose_target(pose_goals[i].pose)
         
             plan = group.plan()
     
-            if len(plan.joint_trajectory.points) > 0 or len(plan.multi_dof_joint_trajectory.points) > 0:
-                print "============ Motion plan succeeded"
+            if len(plan.joint_trajectory.points) > 0:
+                print "============ Component ", i, " of motion plan succeeded"
             
-                if i == 0:
-                    start = RobotState()
-                    start.joint_state.name = plan.joint_trajectory.joint_names
-                    start.joint_state.position = plan.joint_trajectory.points[0].positions
-                    start.joint_state.velocity = plan.joint_trajectory.points[0].velocities
-                    start.joint_state.effort = plan.joint_trajectory.points[0].effort
[…]

### 2015-04-11 scripts/planner_server.py

@@ -49,3 +49,4 @@ class TaskPlannerServer(object):
 if __name__ == "__main__":
     task_planner_server = TaskPlannerServer("~/indigo_ws/src/6834-task-motion-planner/FF-v2.3/", "domain")
     task_planner_server.run()
+    

### 2015-04-11 scripts/server_tests.py

@@ -25,25 +25,27 @@ def motion_planner_client():
         
         msg = motion_plan_parameters()
         
-        msg.world = PlanningSceneWorld()
+        state = world_state()
+        state.world = PlanningSceneWorld()
+        state.robot = RobotState()
+        state.robot.joint_state.name = ['head_pan', 'left_e0', 'left_e1', 'left_s0', 'left_s1', 'left_w0', 'left_w1', 'left_w2', 'right_e0', 'right_e1', 'right_s0', 'right_s1', 'right_w0', 'right_w1', 'right_w2']
+        state.robot.joint_state.position = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
+        state.robot.joint_state.velocity = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
+        state.robot.joint_state.effort = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
+        msg.state = state
         
-        msg.start = RobotState()
-        msg.start.joint_state.name = ['head_pan', 'left_e0', 'left_e1', 'left_s0', 'left_s1', 'left_w0', 'left_w1', 'left_w2', 'right_e0', 'right_e1', 'right_s0', 'right_s1', 'right_w0', 'right_w1', 'right_w2']
-        msg.start.joint_state.position = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
-        msg.start.joint_state.velocity = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
-        msg.start.joint_state.effort = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
+        msg.action = '(pickUp,left_arm,obj1)'
         
-        msg.group_names = ['left_arm']
-        
-        msg.goals = [Pose()]
-        msg.goals[0].position.x = 0.74
-        msg.goals[0].position.y = 0.28
-        msg.goals[0].position.z = 0.34
-        msg.goals[0].orientation.w = 1.0
+        msg.goals = [pose()]
+        msg.goals[0].pose.position.x = 0.74
+        msg.goals[0].pose.position.y = 0.28
+        msg.goals[0].pose.position.z = 0.34
+        msg.goals[0].pose.orientation.w = 1.0
+        msg.goals[0].gripperOpen = True
         
[…]

### 2015-04-12 scripts/pose_generator.py
fixed bug in putdown

@@ -35,7 +35,7 @@ class PoseGenerator:
         elif action[0] == 'putdown':
             print action[-1]
             table = self._search_for_object(action[-1], objects)
-            self.putdown(table,height)
+            return self.putdown(table,height)
         else:
             return
 
@@ -105,7 +105,6 @@ class PoseGenerator:
         poseGen5.gripperOpen = False
 
         # An array of pose_gen messages
-        # return [poseGen1]
         return [poseGen1,poseGen2,poseGen3,poseGen4,poseGen5] 
 
     # Generates a set of gripper poses for a putting down a cylinder,
@@ -133,7 +132,7 @@ class PoseGenerator:
         poseGen1.pose.position.y = random.uniform(y1,y2)
         poseGen1.pose.position.z = CLEARANCE_HEIGHT
         yaw = random.uniform(-math.pi/4,math.pi/4)
-        poseGen1.pose.orientation = _rpy_to_orientation(math.pi/2,0,yaw)
+        poseGen1.pose.orientation = self._rpy_to_orientation(math.pi/2,0,yaw)
         poseGen1.gripperOpen = False
 
         # Set down pose

### 2015-04-12 scripts/pose_generator.py
fixing height for putdown

@@ -122,7 +122,7 @@ class PoseGenerator:
         x2 = table_center.x + table.primitives[0].dimensions[0]/2
         y2 = table_center.y + table.primitives[0].dimensions[1]/2
 
-        CLEARANCE_HEIGHT = table_height + height
+        CLEARANCE_HEIGHT = table_height + 2*height
         X_Y_DIST_FROM_CYLINDER = .05
 
         # Sample an (x,y) point inside the given area
@@ -139,7 +139,7 @@ class PoseGenerator:
         poseGen2 = pose_gen()
         poseGen2.pose.position.x = poseGen1.pose.position.x
         poseGen2.pose.position.y = poseGen1.pose.position.y
-        poseGen2.pose.position.z = table_height + height/2
+        poseGen2.pose.position.z = table_height + height
         poseGen2.pose.orientation = poseGen1.pose.orientation
         poseGen2.gripperOpen = False
 

### 2015-04-12 scripts/pose_generator.py
fixing height for putdown

@@ -139,7 +139,7 @@ class PoseGenerator:
         poseGen2 = pose_gen()
         poseGen2.pose.position.x = poseGen1.pose.position.x
         poseGen2.pose.position.y = poseGen1.pose.position.y
-        poseGen2.pose.position.z = table_height + height
+        poseGen2.pose.position.z = table_height + height/2
         poseGen2.pose.orientation = poseGen1.pose.orientation
         poseGen2.gripperOpen = False
 

### 2015-04-12 scripts/pose_generator.py
fixing height for putdown

@@ -139,7 +139,7 @@ class PoseGenerator:
         poseGen2 = pose_gen()
         poseGen2.pose.position.x = poseGen1.pose.position.x
         poseGen2.pose.position.y = poseGen1.pose.position.y
-        poseGen2.pose.position.z = table_height + height/2
+        poseGen2.pose.position.z = table_height + height
         poseGen2.pose.orientation = poseGen1.pose.orientation
         poseGen2.gripperOpen = False
 

### 2015-04-12 scripts/pose_generator.py
fixed move back pose in put down

@@ -150,8 +150,8 @@ class PoseGenerator:
 
         # Move back pose
         poseGen4 = pose_gen()
-        poseGen4.pose.position.x = poseGen3.pose.position.x + X_Y_DIST_FROM_CYLINDER
-        poseGen4.pose.position.y = poseGen3.pose.position.y + X_Y_DIST_FROM_CYLINDER
+        poseGen4.pose.position.x = poseGen3.pose.position.x - X_Y_DIST_FROM_CYLINDER
+        poseGen4.pose.position.y = poseGen3.pose.position.y - X_Y_DIST_FROM_CYLINDER
         poseGen4.pose.position.z = poseGen3.pose.position.z
         poseGen4.pose.orientation = poseGen3.pose.orientation
         poseGen4.gripperOpen = True

### 2015-04-12 scripts/interface_layer.py
added PDDL test files

@@ -70,7 +70,7 @@ class InterfaceLayer(object):
         msg = task_domain()
         #output state to file
 	f = open('state', 'w')
-        f.write('(define (problem task)')
+        f.write('(define (problemtask)')
         f.write('(:domain taskmotion)')
         f.write('(:objects ')
         for o in state[0]:

### 2015-04-12 scripts/pose_generator.py
fixing pose generator

@@ -27,15 +27,15 @@ class PoseGenerator:
         objects = world.world.collision_objects
         obj = self._search_for_object(action[1], objects)
         height = obj.primitives[0].dimensions[0]
+        radius = obj.primitives[0].dimensions[1]
         
         if action[0] == 'pickup':
             pose = obj.primitive_poses[0]
-            radius = obj.primitives[0].dimensions[1]
             return self.pickup(pose,height,radius)
         elif action[0] == 'putdown':
             print action[-1]
             table = self._search_for_object(action[-1], objects)
-            return self.putdown(table,height)
+            return self.putdown(table,height,radius)
         else:
             return
 
@@ -114,7 +114,7 @@ class PoseGenerator:
     # return =  an array of 6 pose_gen messages containing a pose and a
     #           boolean - true if the gripper is open, false if closed
     #           poses = stage, set-down, let-go, back away, lift arm, standard pose
-    def putdown(self,table,height):
+    def putdown(self,table,height,radius):
         table_center = table.primitive_poses[0].position
         table_height = table.primitive_poses[0].position.z + table.primitives[0].dimensions[2]/2
         x1 = table_center.x - table.primitives[0].dimensions[0]/2
@@ -123,7 +123,7 @@ class PoseGenerator:
         y2 = table_center.y + table.primitives[0].dimensions[1]/2
 
         CLEARANCE_HEIGHT = table_height + 2*height
-        X_Y_DIST_FROM_CYLINDER = .05
+        r = radius .05
 
         # Sample an (x,y) point inside the given area
         # Generate a pose hovering over the point
@@ -150,8 +150,8 @@ class PoseGenerator:
 
         # Move back pose
         poseGen4 = pose_gen()
-        poseGen4.pose.position.x = poseGen3.pose.position.x - X_Y_DIST_FROM_CYLINDER
-        poseGen4.pose.position.y = poseGen3.pose.position.y - X_Y_DIST_FROM_CYLINDER
+        poseGen4.pose.position.x = r / radius * (poseGen3.pose.position.x - 15*self.GRIPPER_OFFSET - obj_pose.position.x) + obj_pose.position.x
+        poseGen4.pose.position.y = r / radius * (poseGen3.pose.position.y - obj_pose.position.y) + obj_pose.position.y
         poseGen4.pose.position.z = poseGen3.pose.position.z
         poseGen4.pose.orientation = poseGen3.pose.orientation
         poseGen4.gripperOpen = True

### 2015-04-13 documentation/draft.tex
fixed move back angle

@@
 The interface layer translates geometric constraints and passes them to the task planner.
+
 \section{Problem Statement}
 
+We implemented an interface between a task and motion planner for the Baxter robot designed by Rethink Robotics.
+For the motion planner we used OMPL from the ROS move-it interface and FF for our task planner.
+We instructed Baxter to pickup and place cylinders standing on a table.
+The cylinders were placed such that Baxter could not reach all of the cylinders in the initial state.
+
 \section{High Level Approach}
+We implemented wrappers to incorporate the motion and task planners with the interface API. The interface layer
 

### 2015-04-13 scripts/pose_generator.py

@@ -17,6 +17,7 @@ import re
 class PoseGenerator:
     def __init__(self, GRIPPER_OFFSET = .015):
         # the height of the table in world coordinates
+        self.DIST_FROM_CYLINDER = .1
         self.GRIPPER_OFFSET = GRIPPER_OFFSET
 
     # Generates a set of gripper poses given an action and a world description
@@ -47,10 +48,9 @@ class PoseGenerator:
     #           poses = stage, pre-grasp, grasp, lifted, standard pose
     def pickup(self, obj_pose, height, radius):
         CLEARANCE_HEIGHT = obj_pose.position.z + height
-        DIST_FROM_CYLINDER = .1
         
         # radius of circle around the cylinder where the gripper origin will lie
-        r = radius + DIST_FROM_CYLINDER
+        r = radius + self.DIST_FROM_CYLINDER
         # height of gripper when grasping cylinder
         z =  obj_pose.position.z
 
@@ -122,7 +122,7 @@ class PoseGenerator:
         y2 = table_center.y + table.primitives[0].dimensions[1]/2
 
         CLEARANCE_HEIGHT = table_height + 2*height
-        r = radius .05
+        r = radius + self.DIST_FROM_CYLINDER
 
         # Sample an (x,y) point inside the given area
         # Generate a pose hovering over the point
@@ -154,8 +154,8 @@ class PoseGenerator:
 
         # Move back pose
         poseGen4 = pose_gen()
-        poseGen4.pose.position.x = r / radius * (poseGen3.pose.position.x - 15*self.GRIPPER_OFFSET - obj_pose.position.x) + obj_pose.position.x
-        poseGen4.pose.position.y = r / radius * (poseGen3.pose.position.y - obj_pose.position.y) + obj_pose.position.y
+        poseGen4.pose.position.x = poseGen3.pose.position.x - r * math.cos(yaw)
+        poseGen4.pose.position.y = (poseGen4.pose.position.x-poseGen3.pose.position.x) * math.tan(theta) + poseGen3.pose.position.x
         poseGen4.pose.position.z = poseGen3.pose.position.z
         poseGen4.pose.orientation = poseGen3.pose.orientation
         poseGen4.gripperOpen = True

### 2015-04-13 scripts/pose_generator.py
fixed move back angle

@@ -155,7 +155,7 @@ class PoseGenerator:
         # Move back pose
         poseGen4 = pose_gen()
         poseGen4.pose.position.x = poseGen3.pose.position.x - r * math.cos(yaw)
-        poseGen4.pose.position.y = (poseGen4.pose.position.x-poseGen3.pose.position.x) * math.tan(theta) + poseGen3.pose.position.x
+        poseGen4.pose.position.y = (poseGen4.pose.position.x-poseGen3.pose.position.x) * math.tan(yaw) + poseGen3.pose.position.x
         poseGen4.pose.position.z = poseGen3.pose.position.z
         poseGen4.pose.orientation = poseGen3.pose.orientation
         poseGen4.gripperOpen = True

### 2015-04-13 scripts/interface_layer.py
add stateUpdate function to interface layer

@@ -44,7 +44,7 @@ class InterfaceLayer(object):
                 # find a partial trajectory -- how far along the high level task plan can we find motion plans for?
                 (partialTraj, pose2, failStep, failCause, state, world) = sub.try_refine(pose1, state, world hlplan, step, partialTraj, mode='partialTraj')
                 # when we eventually failed, we failed because some object(s) were in the way -- we need to update our new task planning problem to incorporate that
-                (state, world) = stateUpdate(state, world, failCause, failStep)
+                (state, world) = stateUpdate(state, world, failCause, failStep, hlplan)
                 # now, call the task planner again on the new state
                 (success, newPlan) = callTaskPlanner(state)
                 if success: # it may not be possible to find a new plan; if it is, update our high level plan 
@@ -100,7 +100,18 @@ class InterfaceLayer(object):
 
         return (resp.plan.error, plan)
 
-    def stateUpdate(state, world, failCause, failStep):
+    def stateUpdate(state, world, failCause, failStep, hlplan):
+        # stateUpdate will need to be updated based on the specific problem
+        action = hlplan[failStep]
+        if action[0] == pickup:
+            obj_to_pickup = action[1]
+            for obj in failCause:
+                state[2].append( ('Obstructs', obj, obj_to_pickup))
+        elif action[0] == putdown:
+            obj_to_putdown = action[1]
+            tloc = action[5]
+            for obj in failCause:
+                state[2].append( ('PDObstructs', obj, obj_to_putdown, tloc))
         return state
 
     def get_motion_plan(world, action, goals):

### 2015-04-13 scripts/pose_generator.py
fixing move back angle

@@ -154,8 +154,8 @@ class PoseGenerator:
 
         # Move back pose
         poseGen4 = pose_gen()
-        poseGen4.pose.position.x = poseGen3.pose.position.x - r * math.cos(yaw)
-        poseGen4.pose.position.y = (poseGen4.pose.position.x-poseGen3.pose.position.x) * math.tan(yaw) + poseGen3.pose.position.x
+        poseGen4.pose.position.x = poseGen3.pose.position.x - r * math.cos(math.pi/2.0 - yaw)
+        poseGen4.pose.position.y = poseGen3.pose.position.y + r * math.sin(math.pi/2.0 - yaw)
         poseGen4.pose.position.z = poseGen3.pose.position.z
         poseGen4.pose.orientation = poseGen3.pose.orientation
         poseGen4.gripperOpen = True

### 2015-04-13 scripts/interface_layer.py
refactored interface layer with an appropriate class structure for easy extnesibility/modularity with different motion and task planners

@@ -13,6 +13,14 @@ motion_server = None
 # TODO: if necessary, add in random seed for pose generators later
 
 class InterfaceLayer(object):
+    # This class is NOT a complete class.  Several functions must be implemented in order
+    # to work with your specific motion planner and your specific task planner.  In particular,
+    # the callTaskPlanner function must be implemented to take inputs in the appropriate format
+    # and return a high level plan in the correct format.  Similarly, get_motion_plan must be
+    # implemented to do the same with the motion planner.  Finally, stateUpdate must be 
+    # implemented to correctly handle updating the state based on errors identified via the
+    # interface layer.
+    
     def __init__(self, ):
         pass
         
@@ -60,6 +68,41 @@ class InterfaceLayer(object):
             partialTraj = None
             pose1 = initialPose
 
+    def MPErrs(pose1, pose2, state, world, action):
+        obstacles = world.world.collision_objects
+	a_whole_new_world = World()
+	a_whole_new_world.robot = world.robot
+	a_whole_new_world.world = world.world
+	
+	for i in range(len(obstacles)):
+            if i == 0:
+                (~, ~, success) = get_motion_plan(world, action, pose2)
+                if success:
+                    return []
+            else:
+                for l in itertools.combinations(range(len(obstacles)), i):
+                    updated_obstacles = obstacles
+                    for item in l:
+                        updated_obstacles.pop(item)
+                    a_whole_new_world.world.collision_objects = updated_obstacles
+                    (~, ~, success) = get_motion_plan(a_whole_new_world, action, pose2)
+                    if success:
+                        return [obstacles[i].id for i in l]
+        print "ERROR!"
+
+    def callTaskPlanner(state, world):
+        # want to return: (success, state)
+        pass
+
+    def stateUpdate(state, world, failCause, failStep, hlplan):
+        # want to return: state
+        pass
+
+    def get_motion_plan(world, action, goals):
+        # want to return: (world, motion plan, success)
+        pass
+
+class SpecificInterfaceLayer(InterfaceLayer):
 
     def callTaskPlanner(state, world):
         # plan is an array of tuples where the first thing is the action and the rest are objects it acts on
@@ -128,29 +171,6 @@ class InterfaceLayer(object):
             print "Service call failed: %s"%e
             return (world, [], False)
 
-    def MPErrs(pose1, pose2, state, world, action):
-        obstacles = world.world.collision_objects
-	a_whole_new_world = World()
[…]

### 2015-04-16 scripts/stateGenerator.py
created stateGenerator to generate state strings, gotta finish it so it will make a file

@@ -1,0 +1,44 @@
+# The number of blocks (including block 0)
+NUMBLOCKS = 10
+
+# Concatenate substrings & add numbers between them, do this for the number of blocks
+# strs = substrings to concatenate (with number between each substring)
+# the final character of the return strign
+# whether or not to add a number after the last substring
+# the block # to start at
+def concatMult(strs,last,end=False,start=0):
+	s = ''
+	r = len(strs) if end else len(strs)-1 
+	for i in range(start, NUMBLOCKS):
+		for x in range(r):
+			s += strs[x]+str(i)
+		if r < len(strs):
+			s += strs[-1]
+		if not i==10:
+			s += ","
+	return s
+
+if __name__ == "__main__":
+	s = ''
+	# environment
+	s += concatMult(["BLOCK"," - physob"],",")
+	s += "LEFTARM - gripper,"
+	s += concatMult(["GP_BLOCK"," - pose"],",")
+	s += concatMult(["PDP_BLOCK","_S - pose"],",")
+	s += concatMult(["PDP_BLOCK","_I - pose"],",")
+	s += "INITPOSE - pose,"
+	s += "S - location,"
+	s += "I - location\n"
+	# initial conditions
+	s += "ROBOTAT INITPOSE,EMPTY LEFTARM,"
+	s += concatMult(["ISGPFG GP_BLOCK", " BLOCK"],",",True)
+	s += concatMult(["ISGPFPD PDP_BLOCK","_S BLOCK", " S"],",")
+	s += concatMult(["ISGPFPD PDP_BLOCK","_I BLOCK", " I"],",")
+	s += concatMult(["ISLFPD S BLOCK"],",",True)
+	s += concatMult(["ISLFPD I BLOCK"],"\n",True)
+	# goal
+	s += "AT BLOCK0 S\n"
+	# initial pose
+	s += "INITPOSE"
+
+	print s

### 2015-04-16 documentation/draft.tex

--- 2015-04-11 documentation/draft.tex
@@
 The interface layer translates geometric constraints and passes them to the task planner.
+
 \section{Problem Statement}
+
+In robotics, it is often necessary to create a plan for a series of motions of the robot in order to complete some high level plan.
+In order to find a task plan which is actually feasible, the task planner must have some knowledge of the geometry of the world.
+Without knowledge of the actual spatial configurations of objects in the world, the task planner would create plans where some actions cannot be completed, due to infeasible motion plans from blocking objects or interference between the robot and the environment.
+
+The high level problem this implementation addresses is to create a combined task and motion planner, following that presented in [1].  
+This approach allows the motion planner to give information to the task planner and allows us to keep the continuous variables continuous, rather than discretizing.  
+This prevents a combinatorial explosion of the state space that the task planner needs to search over.
+
+The main contribution of this implementation is an interface layer.  
+This interface layer is designed to be planner-independent: that is, it can work with any motion planner and task planner, so long as the outputs from each are conformed to the interface specified by the API.
+The interface layer interleaves calls between the task planner and the motion planner, using geometric feasibility determined through the motion planner to affect the state given to the task planner to plan from.
+
+Specifically, we start by generating a high level plan and attempting to generate motion plans corresponding to each action.  
+When it's not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner in an appropriate format.  
+Then, the task planner replans from that set state and the process continues.  
+When necessary, backtracking occurs.
 
@@
 
+Specifically, the interface layer starts by generating a high level plan and attempting to generate motion plans corresponding to each action.  
+When it's not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner in an appropriate format.  
+Then, the task planner replans from that set state and the process continues.  
+When necessary, backtracking occurs.
+
+In order to communicate with the task planner and motion planner, the interface layer utilizes ROS services.  
+For the task planner, the interface layer instantiates a server with a given PDDL domain file.  
+This domain file specifies the different actions that are feasible along with their preconditions and postconditions.  
+For individual service calls, the interface layer takes an internal `state' variable, converts it to PDDL format, and sends it to the server to be solved.  
+The task planner service responds with a high level plan or a notification that finding a plan failed.  
+If finding a plan failed, the interface layer begins backtracking.  
+If a high level plan is found, the interface layer begins searching for refinements of each action as a motion plan.
+
+For the motion planner, the interface layer again communicates via a ROS service.  
+The motion planner is given an action, a world state, and a pose or set of poses corresponding to sub-parts of the action.  
+If it is possible to perform the action using the intermediary poses specified, the motion plan returns the trajectory.  
+If not, it returns an error message.
+
+If the motion plan does not succeed, a variety of poses are tried.  
+Poses are generated randomly from a pose generator.  
+If no poses are successful, the interface layer determines what is blocking the motion plan from succeeding.  
+Specifically, it removes objects from the environment until a feasible motion plan is found.  
+If still no feasible motion plan is found, backtracking is required.  
+If a feasible motion plan is found with some subset of objects removed, then that information is relayed back to the task planner.  
+The task planner replans from the step where we failed to find a motion plan.  
+At that state, we add in predicates corresponding to the object obstructions.  
+Then, the task planner replans from there.
+
+Simple example walkthrough:
+
+Consider the environment in FIGURE.  
+In this environment, we have two objects, blocks 1 and 2, and our goal is to put block 1 into area S.  
+However, we cannot pick up block 1 directly since the walls and block 2 surround it.  
+Here we walk through the steps the interface layer takes when solving this problem in order to explain the details of the interface layer's construction.
+
+\begin{enumerate}[i.]
+
+\item Call the task planner to create a high level plan.  
+In this case, the task planner doesn't yet know that block 2 is blocking block 1, so the plan is simply:
+
+\begin{enumerate}[1.]
+\item PICKUP BLOCK1 with GRIPPER
+
+\item PUTDOWN BLOCK1 on SURFACE S
+\end{enumerate}
+
+\item Next step is to call the motion planner to try and find a trajectory corresponding to each of these actions.  
+In this case, the motion planner fails to find a motion plan for step 1.
+
+\item The interface layer goes through removing objects to try to find what was causing the error for that action.  
+The interface layer discovers that if it removes block 2, then the motion plan can be created just fine, so block 2 must be obstructing the path.
+
+\item We add a predicate corresponding to BLOCK2 OBSTRUCTS BLOCK1 to the planner's state.
+
+\item Now, we try to find a new high level plan.  
+Since block 2 is obstructing block 1, we can't pick up block 1 directly, so the task planner realizes it needs to move block 2 first before moving block 1. 
+The new plan it creates is:
+
+\begin{enumerate}[1.]
+\item PICKUP BLOCK2 	with GRIPPER
+\item PUTDOWN BLOCK2 on SURFACE S
+\item PICKUP BLOCK1 with GRIPPER
+\item PUTDOWN BLOCK1 on SURFACE S
+\end{enumerate}
+
+\item Now, we again go to the motion planner and try to find a motion plan corresponding to every action.
+In this case, there are no more obstructions, so the process works!
+
+\item Ultimately, the algorithm returns the high level plan in conjunction with a motion plan trajectory for every step of the high level plan.
+
+\end{enumerate}
+
 \section{Technical Details}
+
+-zoom into features, explain how they work on a technical level
+
+-enough understanding to derive + implement algorithm on their own
+
+things to talk about:
+
+\subsection{Representing Continuous Variables Symbolically}
+
+-continuous variables represented symbolically
+
+\subsection{Pose Generators}
+
+\subsection{Main Interface Layer}
+
+\subsubsection{walk through the main image}
+
+Insert the figure 4 from the paper!
+
+This figure, included with text from [1], explains the flow of control of
+
+\subsubsection{Algorithm 1}
+
+\subsubsection{Algorithm 2}
 
@@
 
+-realistic expectations for someone interested in applying the reasoning technique
+
+-still need to get a motion planner and a task planner working and need to make them have the right API interface -- not a pure out of the box working thing
+
+-is not guaranteed to find an optimal solution
+
+-cannot do online re-planning
+
+-time to run is based on speed of the motion planner and task planner
+
 \section{Open Questions}
+
+-include more grasp primitives (e.g. push grasps)
+
+-partially observable or non-deterministic environments
+
+-replanning online
 
@@
 
+[1] S.
+Srivastava, E.
+Fang, L.
+Riano, R.
+Chitnis, S.
+Russell, P.
+Abbeel.
+"Combined Task and Motion Planning Through an Extensible Planner-Independent Interface Layer".
+IEEE International Conference on Robotics and Automation (ICRA), 2014.
+
 \end{document}

### 2015-04-16 scripts/stateGenerator.py
state generator generates file and takes in command line arguments

@@ -1,4 +1,9 @@
+#!/usr/bin/python
+
+import sys
+
 # The number of blocks (including block 0)
+# set by command line args
 NUMBLOCKS = 10
 
 # Concatenate substrings & add numbers between them, do this for the number of blocks
@@ -17,8 +22,7 @@ def concatMult(strs,last,end=False,start=0):
 		if not i==10:
 			s += ","
 	return s
-
-if __name__ == "__main__":
+def generateString():
 	s = ''
 	# environment
 	s += concatMult(["BLOCK"," - physob"],",")
@@ -41,4 +45,25 @@ if __name__ == "__main__":
 	# initial pose
 	s += "INITPOSE"
 
-	print s
+	return s
+
+def generateFile(filename):
+	s = generateString()
+	f = open(filename, 'w')
+	f.write(s)
+	f.close()
+
+if __name__ == "__main__":
+	# single argument: Number of blocks
+	# 2 arguments: filename, number of blocks
+	if len(sys.argv) == 1:
+		filename = 'state'
+		NUMBLOCKS = 10
+	if len(sys.argv) == 2:
+		filename = 'state'
+		NUMBLOCKS = int(sys.argv[1])
+	else:
+		filename = sys.argv[1]
+		NUMBLOCKS = int(sys.argv[2])
+
+	generateFile(filename)

### 2015-04-16 scripts/mockPoseGenerator.py
mockPoseGenerator generates pose messages

@@ -1,5 +1,11 @@
+#!/usr/bin/python
+
+import rospy
+import roslib
+from task_motion_planner.msg import *
 from random import shuffle
 import numpy
+import re
 
 # TODO: Change to message type instead of dict, also add second action
 
@@ -7,11 +13,28 @@ class MockPoseGenerator:
     def __init__(self):
         self.state = dict()
 
-    def next(self, action):
+    def next(self, action_tuple):
+        # TODO: remove parens
+        action_tuple = re.split("[\(,\)]?",action_tuple)
+        action_tuple = action_tuple[1:-1]
+        action = action_tuple[0]
+        obj = action_tuple[1]
+
+        msg = pose()
+        msg.object_id = obj
+        
+        # TODO get surface/obj
         if action in self.state:
             # if there are letters left, return it
             if len(self.state[action]) > 0:
-                return self.state[action].pop()
+                if action == 'PICKUP':
+                    msg.direction = self.state[action].pop()
+                else:
+                    location = self.state[action].pop()
+                    msg.x = location[0]
+                    msg.y = location[1]
+                    msg.surface_id = action_tuple[-1]
+                return msg
             else:
                 return None
         else:
@@ -19,15 +42,19 @@ class MockPoseGenerator:
             if action == 'PICKUP':
                 self.state[action] = ['N','NE','E','SE','S','SW','W','NW']
                 shuffle(self.state[action])
+                msg.direction = self.state[action].pop()
             else:
                 x_poses =  list(xrange(17))
                 y_poses = list(xrange(17))
                 shuffle(x_poses)
                 shuffle(y_poses)
                 self.state[action]=numpy.transpose([x_poses,y_poses]).tolist()
-            # randomize the order
+                location = self.state[action].pop()
+                msg.x = location[0]
+                msg.y = location[1]
+                msg.surface_id = action_tuple[-1]
             # return a pose
-            return self.state[action].pop()
+            return msg
 
     def reset(self, action):
         if action in self.state:
@@ -36,10 +63,10 @@ class MockPoseGenerator:
 if __name__ == "__main__":
     m = MockPoseGenerator()
     for i in range(9):
-        print m.next('PICKUP')
+        print m.next('(PICKUP,1)')
     for i in range(18):
-        print m.next('PUTDOWN')
+        print m.next('(PUTDOWN,1,surface)')
     m.reset('PICKUP')
[…]

### 2015-04-16 documentation/draft.tex
added documentation section about continuous variables

@@
 
-Simple example walkthrough:
+\subsection{Simple Example Walkthrough}
 
@@
 
--continuous variables represented symbolically
+One of the key insights of this paper is that continuous variables can be referenced symbolically in the task planner.  
+For instance, consider the pose of the robot: this is a continuous, geometric state.  However, the task planner only keeps track of poses symbolically.  
+The task planner knows that there is some GPFG\_obj\_1 -- a Gripper Pose For Grasping -- for object 1, and it doesn't really care what that pose is, so long as it exists.  
+The task planner reasons over a variety of these symbolic variables, corresponding to poses and trajectories.  
+The motion planner and pose generators take these symbolic variables and associate them with corresponding real locations and motions in the world.  
+This is the key insight which allows the task planner to reason about continuous variables without discretizing.
 
@@
 
+veronica can probably write this section
+
 \subsection{Main Interface Layer}
+
+Bianca will finish writing this section and the corresponding subsections tomorrow
 
@@
 \subsubsection{Algorithm 2}
+
+\subsection{API and Interfaces}
+
+Alex should write this section, probably mostly the same as the stuff he's writing for the readme/etc.
 

### 2015-04-16 documentation/draft.tex
various bug fixes getting interface layer up and working in organized format

@@
 
+-discussion of pose and traj variables
+
+-discussion of pick primitive and place primitive
+
 \subsection{Pose Generators}
@@
 
-\subsubsection{walk through the main image}
-
 Insert the figure 4 from the paper!
 
-This figure, included with text from [1], explains the flow of control of
+This figure, included with text from [1], explains the flow of control of the interface layer through a variety of situations, including more than the simple case covers.
+The subfigures in this diagram explain on a high level the different steps the interface layer takes when solving a problem.
+The subfigure a shows the motion planner's backtracking search when trying to instantiate motions for each of the high level actions.
+Subfigure b shows the first possible scenario, where the backtracking search succeeds.
+Subfigure c shows a second possible scenario, where the backtracking search doesn't succeed.
+There are multiple options of what can happen within this scenario: subfigure d shows an option where they determine that the block2 obstructs the trajectory.
+This triggers the behavior discussed earlier, where the state is updated for the task planner.
+Subfigure e shows the new task plan after replanning occurs.
+After this, the interface layer will repeat the process of attempting to refine this new plan.
+Subfigure f shows an alternative option, where the blocking object is determined to be the table, which is not movable.
+Then, the state is updated as before and the task planner is called, but no solution is found, so backtracking occurs.
 
@@
 
+Include algorithm block 1 from paper
+
+The outer loop of the algorithm interfaces with the high level task planner.  We start with an initial state where no objects obstruct any motions.  From there, we
+
 \subsubsection{Algorithm 2}
+
+include algorithm block 2 from paper!  go with the one from the short version of the paper, since it's the version we're actually going with.
 

### 2015-04-16 scripts/full_test.py

@@ -2,15 +2,15 @@
 
 from mockPoseGenerator import *
 from mockMotionPlanner import *
-from mockStateUpdate import *
-from interface_layer import *
-from plannerServer import *
+import mockStateUpdate
+from interface_layer_organized import *
+from planner_server import *
 from generateWorldMsg import *
 
 if __name__ == '__main__':
     genWorld = generateWorldMsg()
     
-    f = open('../states/one_cover','r')
+    f = open('/home/bhomberg/indigo_ws/src/6834-task-motion-planner/states/one_cover','r')
     init_state_string = f.read()
     
     state = [[]]*3
@@ -23,12 +23,15 @@ if __name__ == '__main__':
     pose = l[3]
 
     world = genWorld.generateWorld('SQUARE',3)
-    pose = None
 
-    task_planner_server = TaskPlannerServer("~/indigo_ws/src/6834-task-motion-planner/FF-v2.3/", "~/indigo_ws/src/6834-task-motion-planner/domain")
-    motion_planner_server = MockMotionPlannerServer(17)
-    interfaceLayer = InterfaceLayer('task_server_service', 'motion_server_service', MockPoseGenerator, mockStateUpdate, '~/indigo_ws/src/6834-task-motion-planner/')
+    #task_planner_server = TaskPlannerServer("/home/bhomberg/indigo_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/bhomberg/indigo_ws/src/6834-task-motion-planner/domain")
+    #task_planner_server.run()
+    #motion_planner_server = MockMotionPlannerServer(17)
+    #motion_planner_server.run()
+    interfaceLayer = InterfaceLayer('task_server_service', 'motion_server_service', MockPoseGenerator, mockStateUpdate, '/home/bhomberg/indigo_ws/src/6834-task-motion-planner/')
     (hlplan, traj) = interfaceLayer.run(state, world, pose)
     
+
+    print "\n\n\n OUTPUT FROM INTERFACE LAYER\n\n"
     print hlplan
     print traj

### 2015-04-16 scripts/generateWorldMsg.py

@@ -12,12 +12,13 @@ class generateWorldMsg:
 		self.CENTER = self.WORLD_GRID_SIZE/2 + 1
 
 	def generateWorld(self,block_shape,shape_size):
-		my_world = world()
+		my_world = world_state()
+                my_world.world = world_obj()
 		surfaceS = obj()
 		surfaceS.id = 'S'
 		surfaceI = obj()
 		surfaceI.id = 'I'
-		my_world.surfaces = [surfaceS,surfaceI]
+		my_world.world.surfaces = [surfaceS,surfaceI]
 		if block_shape=='SQUARE':
 			self.generateBlockGrid(my_world,shape_size)
 		elif block_shape=='CROSS':
@@ -33,7 +34,7 @@ class generateWorldMsg:
 		bound = block_grid_size/2
 		for j in xrange(-bound,bound+1):
 			for i in xrange(-bound,bound+1):
-				idx = self._add_block(my_world,i,j,idx)
+				idx = self._add_block(my_world, i,j,idx)
 
 	def generateBlockCross(self,my_world,block_grid_size):
 		idx = 1
@@ -67,7 +68,7 @@ class generateWorldMsg:
 		o.loc.x = self.CENTER + i
 		o.loc.y = self.CENTER + j
 		o.loc.grasped = False
-		my_world.movable_objects.append(o)
+		my_world.world.movable_objects.append(o)
 		return idx
 if __name__ == "__main__":
 	g = generateWorldMsg()

### 2015-04-16 scripts/interface_layer_organized.py

@@ -9,6 +9,12 @@ from geometry_msgs.msg import *
 import copy
 import itertools
 from random import shuffle
+from mockPoseGenerator import *
+from mockMotionPlanner import *
+import mockStateUpdate
+from interface_layer_organized import *
+from planner_server import *
+from generateWorldMsg import *
 
 MAX_TRAJ_COUNT = 3
 MAX_ITERS = 1
@@ -25,6 +31,7 @@ class InterfaceLayer(object):
         self.stateUpdate = stateUpdate
         
         self.directory = directory
+        print "Initialized interface layer!"
         
     def _callTaskPlanner(self, state):
         # plan is an array of tuples where the first thing is the action and the rest are objects it acts on
@@ -34,7 +41,7 @@ class InterfaceLayer(object):
         #    list of predicates for the goal
         msg = task_domain()
         #output state to file
-	    f = open(self.directory + 'state', 'w')
+        f = open(self.directory + 'state', 'w')
         f.write('(define (problem problemtask)\n')
         f.write('(:domain taskmotion)\n')
         f.write('(:objects ')
@@ -65,11 +72,11 @@ class InterfaceLayer(object):
         f.write(')\n)')
         f.close()
         msg.task_file = self.directory + 'state'
-        resp = task_server(msg)
+        resp = self.taskServer(msg)
         # parse plan file into appropriate action tuple
         plan = []
-	    l = resp.plan.plan.split('\n')
-	    plan = [tuple(line.split(' ')) for line in l]
+        l = resp.plan.plan.split('\n')
+        plan = [tuple(line.split(' ')) for line in l]
         plan[-1] = ('BUFFER DEFAULT ACTION', 'BLAH', 'BLAH', 'BLAH', 'BLAH')
         #print "PLAN: ", plan
         return (resp.plan.error, plan)
@@ -79,7 +86,12 @@ class InterfaceLayer(object):
         try:
             msg = motion_plan_parameters()
             msg.state = world
-            msg.action = action
+
+            str_action = '('
+            for elem in action:
+                str_action += elem + ','
+            msg.action = str_action[:-1] + ')'
+
             msg.goals = goals
         
             res = self.motionServer(msg)
@@ -113,16 +125,15 @@ class InterfaceLayer(object):
         print "ERROR IN MP ERRORS!"
         
     def run(self, state, world, pose):
-        rospy.init_node('interface_node')
-    
+        
[…]

### 2015-04-16 scripts/mockMotionPlanner.py

@@ -15,6 +15,7 @@ class MockMotionPlannerServer(object):
         world = req.parameters.state.world
         action = re.split(',', req.parameters.action[1:-1])
         goals = req.parameters.goals
+        print "Goals: ", goals
         
         #(pickup,obj1,left_arm,pose1,pose2)
         #(putdown,obj1,left_arm,pose1,pose2,tloc)
@@ -29,7 +30,7 @@ class MockMotionPlannerServer(object):
             y = wall.loc.y
             surfaces[surface_id][y][x] = 1
             
-        for moveable_object in world.movable_objects:
+        for movable_object in world.movable_objects:
             surface_id = movable_object.loc.surface_id
             x = movable_object.loc.x
             y = movable_object.loc.y
@@ -49,6 +50,7 @@ class MockMotionPlannerServer(object):
                 return
             
             obj = world.movable_objects[obj_idx]
+            print "Direction: ", direction
             can_pickup = self._can_pickup(obj, direction, surfaces)
             
             if can_pickup:
@@ -172,7 +174,7 @@ class MockMotionPlannerServer(object):
         return False
         
     def _can_putdown(self, obj, surfaces, goal_surface_id, goal_x, goal_y):
-        if obj.loc.grasped
+        if obj.loc.grasped:
             if surfaces[goal_surface_id][goal_y][goal_x] == 0:
                 return True
         else:
@@ -183,7 +185,7 @@ class MockMotionPlannerServer(object):
     def run(self):
         rospy.init_node('motion_planner_server')
         s = rospy.Service('motion_server_service', motion_service, self.getMotionPlan)
-        print "============ Ready to serve motion plans"
+        print "Ready to serve motion plans"
         rospy.spin()
     
 if __name__ == "__main__":

### 2015-04-16 scripts/mockPoseGenerator.py

@@ -14,9 +14,6 @@ class MockPoseGenerator:
         self.state = dict()
 
     def next(self, action_tuple):
-        # TODO: remove parens
-        action_tuple = re.split("[\(,\)]?",action_tuple)
-        action_tuple = action_tuple[1:-1]
         action = action_tuple[0]
         obj = action_tuple[1]
 
@@ -58,6 +55,10 @@ class MockPoseGenerator:
 
     def reset(self, action):
         if action in self.state:
+            del self.state[action]
+
+    def resetAll(self):
+        for action in self.state.keys():
             del self.state[action]
 
 if __name__ == "__main__":

### 2015-04-16 scripts/mockStateUpdate.py

@@ -6,7 +6,7 @@ from task_motion_planner.msg import *
 
 # TODO: change world to message type not dictionary
 
-def stateUpdate(self, state, failCause, failStep, hlplan, world):
+def mockStateUpdate(self, state, failCause, failStep, hlplan, world):
         # stateUpdate will need to be updated based on the specific problem
         # currently set up for mocks
         for i in range(failStep):

### 2015-04-16 scripts/full_test.py
more debugging

@@ -8,6 +8,7 @@ from planner_server import *
 from generateWorldMsg import *
 
 if __name__ == '__main__':
+
     genWorld = generateWorldMsg()
     
     f = open('/home/bhomberg/indigo_ws/src/6834-task-motion-planner/states/one_cover','r')
@@ -23,6 +24,7 @@ if __name__ == '__main__':
     pose = l[3]
 
     world = genWorld.generateWorld('SQUARE',3)
+    print world
 
     #task_planner_server = TaskPlannerServer("/home/bhomberg/indigo_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/bhomberg/indigo_ws/src/6834-task-motion-planner/domain")
     #task_planner_server.run()
@@ -35,3 +37,4 @@ if __name__ == '__main__':
     print "\n\n\n OUTPUT FROM INTERFACE LAYER\n\n"
     print hlplan
     print traj
+w

### 2015-04-16 scripts/interface_layer_organized.py

@@ -77,7 +77,8 @@ class InterfaceLayer(object):
         plan = []
         l = resp.plan.plan.split('\n')
         plan = [tuple(line.split(' ')) for line in l]
-        plan[-1] = ('BUFFER DEFAULT ACTION', 'BLAH', 'BLAH', 'BLAH', 'BLAH')
+        plan.insert(0, ('BUFFER DEFAULT ACTION', 'BLAH', 'BLAH', 'BLAH', 'BLAH'))
+        plan = plan[0:-1]
         #print "PLAN: ", plan
         return (resp.plan.error, plan)
         
@@ -110,6 +111,7 @@ class InterfaceLayer(object):
 	
         for i in range(len(obstacles)):
             if i == 0:
+                print "Pose: ", pose2
                 (a, b, success) = self._callMotionPlanner(world, action, pose2)
                 if success:
                     return []
@@ -246,8 +248,8 @@ class TryRefine(object):
             self.pose2 = self.interface.poseGenerator.next(self.nextaxn)
             
             if self.pose2 == None: # pose 2 is already defined, so we should backtrack if in Error free mode, otherwise return that we've failed
-                if mode == 'partialTraj': # we failed -- don't bother backtracking since we're just looking for a partial trajectory, so let's figure out what's blocking it -- BIANCA's MODIFICATION
-                    return (False, self.pose1, self.traj, self.index, self.interface._mpErrs(self.pose1, self.pose2, self.state, self.world, self.axn), self.state, self.world)
+                #if mode == 'partialTraj': # we failed -- don't bother backtracking since we're just looking for a partial trajectory, so let's figure out what's blocking it -- BIANCA's MODIFICATION
+                #    return (False, self.pose1, self.traj, self.index, self.interface._mpErrs(self.pose1, self.pose2, self.state, self.world, self.axn), self.state, self.world)
                 self.interface.poseGenerator.reset(self.nextaxn)
                 self.pose1 = self.interface.poseGenerator.next(self.axn)
                 self.index-=1
@@ -258,17 +260,17 @@ class TryRefine(object):
                 #print 'world: ', self.world
                 #print 'axn: ', self.axn
                 #print 'pose2: ', self.pose2
-                (world, motionPlan, succeeds) = self.interface._callMotionPlanner(self.world, self.axn, self.pose2) # TODO: fix how we access the motion plan
+                (world, motionPlan, succeeds) = self.interface._callMotionPlanner(self.world, self.nextaxn, self.pose2) # TODO: fix how we access the motion plan
[…]

### 2015-04-16 scripts/mockMotionPlanner.py

@@ -3,6 +3,7 @@
 import sys
 import rospy
 import re
+from copy import deepcopy
 from task_motion_planner.srv import *
 from task_motion_planner.msg import *
 
@@ -22,23 +23,28 @@ class MockMotionPlannerServer(object):
         
         surfaces = dict()
         for surface in world.surfaces:
-            surfaces[surface.id] = self.surface_dim*[self.surface_dim*[0]]
+            surfaces[surface.id] = self.surface_dim*deepcopy([self.surface_dim*[0]])
             
         for wall in world.walls:
             surface_id = wall.loc.surface_id
             x = wall.loc.x
             y = wall.loc.y
             surfaces[surface_id][y][x] = 1
-            
+    
+        print surfaces['I']
+        
         for movable_object in world.movable_objects:
             surface_id = movable_object.loc.surface_id
             x = movable_object.loc.x
             y = movable_object.loc.y
             grasped = movable_object.loc.grasped
-            
+    
             if not grasped:
+                print "Surface: ", surface_id
+                print "X: ", x
+                print "Y: ", y
                 surfaces[surface_id][y][x] = 1
-            
+        print surfaces     
         res = motion_plan()
         if action[0] == 'PICKUP':
             object_id = goals.object_id
@@ -111,6 +117,11 @@ class MockMotionPlannerServer(object):
         surface_id = obj.loc.surface_id
         x = obj.loc.x
         y = obj.loc.y
+
+        #for s_id in surfaces.keys():
+        #    print "Surface: ", s_id
+        #    for row in surfaces[s_id]:
+        #        print str(row) + "\n"
         
         if direction == 'N':
             if y == 0 or surfaces[surface_id][y-1][x] == 0:
@@ -127,7 +138,7 @@ class MockMotionPlannerServer(object):
                 return True
             
         elif direction == 'E':
-            if x == self.serface_dim-1 or surfaces[surface_id][y][x+1] == 0:
+            if x == self.surface_dim-1 or surfaces[surface_id][y][x+1] == 0:
                 return True
             
         elif direction == 'SE':
@@ -141,7 +152,7 @@ class MockMotionPlannerServer(object):
                 return True
             
         elif direction == 'S':
-            if y == self.surface_dim-1 or surfaces_id[y+1][x] == 0:
+            if y == self.surface_dim-1 or surface_id[y+1][x] == 0:
                 return True
             
         elif direction == 'SW':

### 2015-04-16 scripts/mockPoseGenerator.py

@@ -38,13 +38,13 @@ class MockPoseGenerator:
             # generate list of poses
             if action == 'PICKUP':
                 self.state[action] = ['N','NE','E','SE','S','SW','W','NW']
-                shuffle(self.state[action])
+                #shuffle(self.state[action])
                 msg.direction = self.state[action].pop()
             else:
                 x_poses =  list(xrange(17))
                 y_poses = list(xrange(17))
-                shuffle(x_poses)
-                shuffle(y_poses)
+                #shuffle(x_poses)
+                #shuffle(y_poses)
                 self.state[action]=numpy.transpose([x_poses,y_poses]).tolist()
                 location = self.state[action].pop()
                 msg.x = location[0]

### 2015-04-17 documentation/draft.tex
added text about interface layer and continuous variables to paper

@@
 
-Consider the environment in FIGURE.  
+Consider the environment in FIGURE.  ***** include Fig 2 from the paper
+
 In this environment, we have two objects, blocks 1 and 2, and our goal is to put block 1 into area S.  
@@
 
-One of the key insights of this paper is that continuous variables can be referenced symbolically in the task planner.  
+One of the key insights of this paper is that continuous variables can be referenced symbolically in the task planner within the PDDL domain.  
 For instance, consider the pose of the robot: this is a continuous, geometric state.  However, the task planner only keeps track of poses symbolically.  
@@
 
--discussion of pose and traj variables
+We will follow [1] in using manipulation as an example environment.
+For any planning domain with some continuous variables and some discrete variables, it will be possible to transform the continuous variables to discrete symbolic references to continuous positions.
+For this example, we talk through the PICKUP action for a simple manipulator; the PUTDOWN action is analagous.
 
--discussion of pick primitive and place primitive
+Veronica: probably should fix this to be a nice alignment environment within LaTeX
+$PICKUP(obj_1, gripper, pose_1, pose_2, traj)$
+
+$\; precon \; EMPTY(gripper), ROBOTAT(pose_1), $
+
+$\; \; \;\; \; \; ISGPFG(pose_2, obj), ISMP(traj, pose_1, pose_2), $
+
+$\; \; \; \; \; \;\forall obj' \neg OBSTRUCTS(obj', traj, obj_1)$
+
+$\; effect \; IN(obj_1, gripper), \neg EMPTY(gripper), $
+
+$\; \; \;\; \; \; \forall obj', traj' \neg OBSTRUCTS(obj_1, traj', obj'), $
+
+$\; \; \; \; \; \;\forall obj' traj', tloc' \neg PDOBSTRUCTS(obj_1, traj', obj', tloc')$
+
+Here, we have three continuous variables that we represent symbolically: $traj$, for each of the trajectories, and $pose_1$ and $pose_2$, representing start and end locations for the robot's gripper.
+The preconditions and effects can also iterate over all of these symbolic variables, allowing us to mark that a picked up object doesn't obstruct any other objects, etc. 
+We have various predicates which describe different things about both the discrete variables and the continuous variables.
+
+$EMPTY(gripper)$ -- this specifies whether the gripper is empty and thus available to hold a block.
+
+$ROBOTAT(pose_1)$ -- this specifies where the robot is.  $pose_1$ is a symbolic reference to a continuous variable.
+
+$ISGPFG(pose, obj)$ -- this specifies whether a pose is a Gripper Pose For Grasping (GPFG) an object.
+
+$ISMP(traj, pose_1, pose_2)$ -- this specifies whether a trajectory is a motion plan from one pose to another.
+
+$OBSTRUCTS(obj_1, traj, obj_2)$ -- this specifies whether an object blocks another object from being picked up along a trajectory.
+
+$PDOBSTRUCTS(obj_1, traj, obj_2, tloc)$ -- this specifies whether an object blocks another object from being put down at a particular location along a trajectory.
+
+$IN(obj_1, gripper)$ -- this specifies whether an object is currently grasped by the gripper.
+
+How do we come up with all of these symbolic references?  
+We create as many as we need.  
+In this case, we need to have a pose where we can pick up each object and put each object down.  
+Neither the interface layer nor the task planner know what the poses correspond to in the real world.
+The pose generators instantiate specific poses which the motion planner verifies or discounts if it doesn't work.
+Similarly, we have one trajectory for each potential pair of poses.  
+However, since the trajectory isn't actually used in any of the effects, we actually can ignore it entirely -- it doesn't change the high level plan and the interface layer will still know to have the motion planner create the relevant trajectories.
+So to make the plan more efficient, we actually cut out the $ISMP$ predicate and all references to trajectories.
+
+How do we pass geometric information from the environment back to the task planner?  
+We do this via the $OBSTRUCTS$ and $PDOBSTRUCTS$ predicates.  
+These tell the task planner that certain objects are blocking motions related to other objects.  
+This allows the task planner to have the robot first move the blocking objects so it can get to the other objects.
 
@@
 The subfigure a shows the motion planner's backtracking search when trying to instantiate motions for each of the high level actions.  
-Subfigure b shows the first possible scenario, where the backtracking search succeeds.
-Subfigure c shows a second possible scenario, where the backtracking search doesn't succeed.
+Subfigure b shows the first possible scenario, where the backtracking search succeeds.  Subfigure c shows a second possible scenario, where the backtracking search doesn't succeed.  
 There are multiple options of what can happen within this scenario: subfigure d shows an option where they determine that the block2 obstructs the trajectory.  
@@
 
-The outer loop of the algorithm interfaces with the high level task planner.  We start with an initial state where no objects obstruct any motions.  From there, we
+The outer loop of the algorithm interfaces with the high level task planner.  
+We start with an initial state where no objects obstruct any motions.  
+From there, we look for a high level plan.  
+If the problem is not solvable without any problematic environmental information, then the problem is unsolvable and we immediately return that information.  
+If we do succeed at finding a high level task plan, we begin the process of attempting to find a motion corresponding to each action.
+
+First, we start by attempting to find a full refinement of the whole plan,calling the TryRefine subroutine in error-free mode.  
+If that succeeds, then we return the plan.
+
+If that doesn't succeed, we find a partial trajectory that goes as far as it can by calling the TryRefine subroutine in partial trajectory mode.  
+This function returns a partial trajectory along with the step where it failed and the determined cause for failure.  
+Then, we update the state based on the actions up until that point and add in the obstructing obstacles corresponding to the failure.  
+Now, we attempt to find a new high level plan, and iterate.
+
+If we fail to find a new high level plan at any point, we re-run the TryRefine subroutine on the original high level plan from the previous step.  
+Since the TryRefine subroutine has randomization from pose generators, re-running it may yield a better solution.
+
+We have several checks where, if we fail to find a solution, we clear all of our information and start over.
+Due to the randomization of the pose generators, we may make better choices during subsequent iterations.
+
+NOTE TO BIANCA: include paragraph about how our version differs from the paper's version as a speedup
 
@@
 
-include algorithm block 2 from paper!  go with the one from the short version of the paper, since it's the version we're actually going with.
+include algorithm block 2 from paper!  go with the one from the short version of the paper, since it's the version we're actually going with.  the algorithm block is shorter too
+
+In the TryRefine subroutine, the interface layer attempts to find motion plans corresponding to the various actions.  
+It has two modes: error free and partial trajectory.  
+In error free mode, it performs backtracking search to try to find a full plan from start to finish.  
+In partial trajectory mode, it goes as far as it can, but when it finds an infeasible motion plan, it returns the step at which it failed.  
+In addition to returning the failed step, it returns the cause of the errors.  
+The function MPErrs removes various objects from the environment until it find a plan which succeeds.  
+It then marks all of those objects which were removed as blocking objects.
+
+NOTE TO BIANCA: include paragraph about how we utilize pose generators here
+
+there will be another couple paragraphs here extending this
 

### 2015-04-17 scripts/stateGenerator.py
fixed out of bounds errors in mockPoseGenerator, numObstructs

@@ -45,7 +45,8 @@ class StateGenerator:
 		s += self.concatMult(["ISGPFPD PDP_BLOCK","_S BLOCK", " S"],",")
 		s += self.concatMult(["ISGPFPD PDP_BLOCK","_I BLOCK", " I"],",")
 		s += self.concatMult(["ISLFPD S BLOCK"],",",True)
-		s += self.concatMult(["ISLFPD I BLOCK"],"\n",True)
+		s += self.concatMult(["ISLFPD I BLOCK"],",",True)
+		s += self.concatMult(["AT BLOCK", " I"],"\n",True)
 		# goal
 		s += "AT BLOCK0 S\n"
 		# initial pose

### 2015-04-17 documentation/draft.tex
backtracking worlds

@@
 
-Bianca will finish writing this section and the corresponding subsections tomorrow
-
 Insert the figure 4 from the paper!
@@
 
-NOTE TO BIANCA: include paragraph about how our version differs from the paper's version as a speedup
+The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.
+Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.
+In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the plan more complicated.
+In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.
+An analysis of the benefits of this approach are outlined in the benchmarking section.
 
@@
 Alex should write this section, probably mostly the same as the stuff he's writing for the readme/etc.
+
+\section{Benchmarking}
+
+\subsection{Testing}
+
+\subsection{Procedure}
+
+\subsection{Results}
+
+to include:
+
+-tables of results
+
+-description of how we did benchmarking
+
+-in particular, description of why we did number of calls to task and motion planner instead of total time taken
+
+-discussion of testing procedure as well
 

### 2015-04-17 scripts/interface_layer_organized.py

@@ -168,13 +168,14 @@ class InterfaceLayer(object):
             partialTraj = []
             pose1 = initPose
             if error:
-                return "Error! Cannot find any high level plan. :("
+                print "Error! Cannot find any high level plan. :("
+                return (False, False)
             hlplan.insert(0, (' ', ' ', ' ',' ', ' '))
-            # print "HLPlan: ", hlplan
+            print "HLPlan: ", hlplan
             # now that we have a high level plan, we try to actually turn it into motions in the real world
             
         while(num_iters < MAX_ITERS):
-            # print "HIGHEST LEVEL ALG 1 ITERATION: ", num_iters
+            print "HIGHEST LEVEL ALG 1 ITERATION: ", num_iters
             num_iters+=1
             
             # try to refine our plan, allowing for no errors
@@ -187,7 +188,7 @@ class InterfaceLayer(object):
             
             # if it didn't work, we need to start piece by piece
             while not success and trajCount < MAX_TRAJ_COUNT:
-                # print "INNER LEVEL ALG 1 ITERATION: ", trajCount
+                print "INNER LEVEL ALG 1 ITERATION: ", trajCount
 
                 # find a partial trajectory -- how far along the high level task plan can we find motion plans for?
                 (success, pose2, partialTraj, failStep, failCause, tstate, tworld) = trajRefiner.tryRefine(pose1, state, world, hlplan, step, partialTraj, mode='partialTraj')
@@ -209,7 +210,7 @@ class InterfaceLayer(object):
                 if not error: # it may not be possible to find a new plan; if it is, update our high level plan 
                     # if it wasn't possible to find a new plan, we'll start over to try and refine, but we'll pick different things because of the randomization
                     hlplan = hlplan[0:failStep+1] + newPlan
-                    # print "HLPlan: ", hlplan
+                    print "HLPlan: ", hlplan
                     pose1 = pose2
                     prev_fail_step = failStep
                     state = tempstate
@@ -232,7 +233,7 @@ class InterfaceLayer(object):
                 pose1 = copy.deepcopy(initPose)
                 (error, hlplan) = self._callTaskPlanner(state) # find a high level task plan
                 hlplan.insert(0, (' ', ' ', ' ',' ', ' '))
-                # print "HLPlan: ", hlplan
+                print "HLPlan: ", hlplan
                 if error:
[…]

### 2015-04-17 scripts/generateSmallWorldMsg.py
fixed wall id numbering

@@ -8,6 +8,7 @@ class GenerateSmallWorldMsg:
 		self.WORLD_GRID_SIZE = 17
 		self.CENTER = self.WORLD_GRID_SIZE/2
 		self.block_idx = 0
+		self.wall_idx = 0
 
 	# surface_and_blocks = a dictionary of surfaces and the number of blocks on each one
 	def generateWorld(self,surface_and_blocks):
@@ -29,28 +30,30 @@ class GenerateSmallWorldMsg:
 			self._add_block(my_world,surface_id,i)
 
 	def generateWalls(self,my_world,surface_id,lb,ub):
-		idx = 0
 		for i in xrange(lb,ub):
 			# left wall
 			o = obj()
-			o.id = "WALL" + str(idx)
+			o.id = "WALL" + str(self.wall_idx)
+			self.wall_idx += 1
 			o.loc.surface_id = surface_id
 			o.loc.x = self.CENTER - 1
 			o.loc.y = self.CENTER + i
 			my_world.walls.append(o)
 			# right wall
-			o2 = obj()
-			o2.loc.surface_id = surface_id
-			o2.loc.x = self.CENTER + 1
-			o2.loc.y = self.CENTER + i
-			my_world.walls.append(o2)
-			idx += 1
+			o = obj()
+			o.id = "WALL" + str(self.wall_idx)
+			self.wall_idx += 1
+			o.loc.surface_id = surface_id
+			o.loc.x = self.CENTER + 1
+			o.loc.y = self.CENTER + i
+			my_world.walls.append(o)
 		# top wall
-		o3 = obj()
-		o3.loc.surface_id = surface_id
-		o3.loc.x = self.CENTER
-		o3.loc.y = self.CENTER + ub
-		my_world.walls.append(o3)
+		o = obj()
+		o.id = "WALL" + str(self.wall_idx)
+		o.loc.surface_id = surface_id
+		o.loc.x = self.CENTER
+		o.loc.y = self.CENTER + ub
+		my_world.walls.append(o)
 
 
 
@@ -70,40 +73,40 @@ def generateWorlds():
 	surfaces = dict()
 	surfaces['I'] = 2
 	surfaces['S'] = 1
-	worlds['state3blocks_1'] = g.generateWorld(surfaces)
+	worlds['state3Blocks_1'] = g.generateWorld(surfaces)
 	surfaces = dict()
 	surfaces['I'] = 2
[…]

### 2015-04-17 scripts/stateGeneratorSmall.py
fixed state generator ISGPFPD bug

@@ -46,8 +46,9 @@ class StateGeneratorSmall:
 		s += "ROBOTAT INITPOSE,EMPTY LEFTARM,"
 		s += self.concatMult(["ISGPFG GP_BLOCK", " BLOCK"],",",True)
 		for s_id in surface_ids:
-			end = "_" + s_id
-			s += self.concatMult(["ISGPFPD PDP_BLOCK", end],",")
+			middle = "_" + s_id + " BLOCK"
+			end = " " + s_id
+			s += self.concatMult(["ISGPFPD PDP_BLOCK",middle, end],",")
 		for s_id in surface_ids:
 			s2 = "ISLFPD " + s_id + " BLOCK"
 			s += self.concatMult([s2],",",True)

### 2015-04-17 scripts/interface_layer_organized.py
added proper handling for complex goal states

@@ -65,14 +65,14 @@ class InterfaceLayer(object):
         f.write(')\n')
         f.write('(:goal ')
         for g in state[2]:
-            f.write('(')
+            f.write('(and (')
             for a in g:
                 f.write(a + ' ')
                 if a == 'NOT':
                     f.write('(')
             if g[0] == 'NOT':
                 f.write(')')
-            f.write(')\n')
+            f.write('))\n')
         f.write(')\n)')
         f.close()
         msg.task_file = self.directory + 'state'
@@ -377,7 +377,7 @@ if __name__ == '__main__':
     genWorld = generateWorldMsg()
     
     #f = open('/home/vmlane/catkin_ws/src/6834-task-motion-planner/states/one_cover','r')
-    f = open('/home/bhomberg/indigo_ws/src/6834-task-motion-planner/states/thirteenby','r')
+    f = open('/home/bhomberg/indigo_ws/src/6834-task-motion-planner/states/state3Blocks_1','r')
     init_state_string = f.read()
     
     state = [[]]*3

### 2015-04-17 scripts/interface_layer_organized.py
fixed and for goal

@@ -63,17 +63,17 @@ class InterfaceLayer(object):
                 f.write(')')
             f.write(')\n')
         f.write(')\n')
-        f.write('(:goal ')
+        f.write('(:goal (and ')
         for g in state[2]:
-            f.write('(and (')
+            f.write('(')
             for a in g:
                 f.write(a + ' ')
                 if a == 'NOT':
                     f.write('(')
             if g[0] == 'NOT':
                 f.write(')')
-            f.write('))\n')
-        f.write(')\n)')
+            f.write(')\n')
+        f.write('))\n)')
         f.close()
         msg.task_file = self.directory + 'state'
         resp = self.taskServer(msg)

### 2015-04-17 scripts/interface_layer.py
added DIR variable at top of files

@@ -15,6 +15,7 @@ MAX_ITERS = 1
 task_server = None
 motion_server = None
 # TODO: if necessary, add in random seed for pose generators later
+DIR = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/state'
 
 class InterfaceLayer(object):
     # This class is NOT a complete class.  Several functions must be implemented in order
@@ -136,7 +137,7 @@ class SpecificInterfaceLayer(InterfaceLayer):
         #    list of predicates for the goal
         msg = task_domain()
         #output state to file
-	f = open('/home/bhomberg/indigo_ws/src/6834-task-motion-planner/state', 'w')
+	f = open(DIR, 'w')
         f.write('(define (problem problemtask)\n')
         f.write('(:domain taskmotion)\n')
         f.write('(:objects ')
@@ -166,7 +167,7 @@ class SpecificInterfaceLayer(InterfaceLayer):
             f.write(')\n')
         f.write(')\n)')
         f.close()
-        msg.task_file = '/home/bhomberg/indigo_ws/src/6834-task-motion-planner/state'
+        msg.task_file = DIR
         resp = task_server(msg)
         # parse plan file into appropriate action tuple
         plan = []

### 2015-04-17 scripts/interface_layer_organized.py

@@ -18,6 +18,7 @@ from generateWorldMsg import *
 
 MAX_TRAJ_COUNT = 50
 MAX_ITERS = 1000
+DIR = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
 
 class InterfaceLayer(object):    
     def __init__(self, taskServerName, motionServerName, poseGenerator, stateUpdate, directory):        
@@ -376,8 +377,7 @@ if __name__ == '__main__':
 
     genWorld = generateWorldMsg()
     
-    #f = open('/home/vmlane/catkin_ws/src/6834-task-motion-planner/states/one_cover','r')
-    f = open('/home/bhomberg/indigo_ws/src/6834-task-motion-planner/states/state3Blocks_1','r')
+    f = open(DIR + 'states/state3Blocks_1','r')
     init_state_string = f.read()
     
     state = [[]]*3
@@ -394,8 +394,7 @@ if __name__ == '__main__':
 
     poseGen = MockPoseGenerator()
 
-    #interfaceLayer = InterfaceLayer('task_server_service', 'motion_server_service', poseGen, mockStateUpdate, '/home/vmlane/catkin_ws/src/6834-task-motion-planner/')
-    interfaceLayer = InterfaceLayer('task_server_service', 'motion_server_service', poseGen, mockStateUpdate, '/home/bhomberg/indigo_ws/src/6834-task-motion-planner/')
+    interfaceLayer = InterfaceLayer('task_server_service', 'motion_server_service', poseGen, mockStateUpdate, DIR)
     (hlplan, traj) = interfaceLayer.run(state, world, pose)
     
     print "\n\n\n OUTPUT FROM INTERFACE LAYER\n\n"

### 2015-04-17 scripts/planner_server.py

@@ -46,7 +46,7 @@ class TaskPlannerServer(object):
         rospy.spin()
 
 if __name__ == "__main__":
-    #task_planner_server = TaskPlannerServer("/home/vmlane/catkin_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/vmlane/catkin_ws/src/6834-task-motion-planner/domain")
-    task_planner_server = TaskPlannerServer("/home/bhomberg/indigo_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/bhomberg/indigo_ws/src/6834-task-motion-planner/domain")
+    DIR = "/home/vmlane/catkin_ws/src/6834-task-motion-planner"
+    task_planner_server = TaskPlannerServer(DIR+"/FF-v2.3/", DIR + "/domain")
     task_planner_server.run()
     

### 2015-04-17 documentation/draft.tex
initial pass of algorithm discussion in tutorial

@@
 
--zoom into features, explain how they work on a technical level
-
--enough understanding to derive + implement algorithm on their own
-
-things to talk about:
+In this section, we discuss the key insight of the original paper: the ability to avoid discretization by representing continuous variables symbolically via references.  
+We also discuss the pose generators which propose real-world instantiations of these references.  
+Finally, we walk through the algorithm in detail.
 
@@
 In error free mode, it performs backtracking search to try to find a full plan from start to finish.  
-In partial trajectory mode, it goes as far as it can, but when it finds an infeasible motion plan, it returns the step at which it failed.  
+The backtracking search is over possible pose instantiations: since some poses may be infeasible and since previous choices may affect future choices, the backtracking search iterates over all possible poses in order to find a full solution if a full solution exists.
+
+In partial trajectory mode, TryRefine goes as far as it can, but when it finds an infeasible motion plan for some action, it returns the step at which it failed.  
 In addition to returning the failed step, it returns the cause of the errors.  
@@
 
-NOTE TO BIANCA: include paragraph about how we utilize pose generators here
+To find the blocking objects, we start by iterating through a randomized list of the objects.  We continue removing objects until we find a successful motion plan.  
+We will eventually find a successful motion plan since if there are no other objects in the world, the motion should succeed.  
+After we find this possible list of removed objects, we iterate through all of the objects we removed.  
+We attempt to add these objects in one by one, leaving added in all of those which don't obstruct our found motion plan.  
+This leaves us with a local minimum of removed objects: it may be possible to find another smaller set of objects that, if removed, allow a valid motion plan.  
+However, for this set of this set of objects, no object can be added back in without obstructing the motion plan.
 
-there will be another couple paragraphs here extending this
-
-\subsection{API and Interfaces}
-
-Alex should write this section, probably mostly the same as the stuff he's writing for the readme/etc.
+As described above in Algorithm 1, once the list of blocking objects is returned, the interface layer updates the state and attempts to replan from there.
 

### 2015-04-17 scripts/interface_layer_organized.py
added handling for interface layer for walls

@@ -18,7 +18,8 @@ from generateWorldMsg import *
 
 MAX_TRAJ_COUNT = 50
 MAX_ITERS = 1000
-DIR = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
+DIR = '/home/bhomberg/indigo_ws/src/6834-task-motion-planner/'
+#DIR = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
 
 class InterfaceLayer(object):    
     def __init__(self, taskServerName, motionServerName, poseGenerator, stateUpdate, directory):        
@@ -150,26 +151,8 @@ class InterfaceLayer(object):
             #print "MPErrs obstacles: ", [obstacle.id for obstacle in actual]
             return [obstacle.id for obstacle in actual]
         else:
-            print "ERROR IN MP ERRORS!"
-        
-        '''for i in range(len(obstacles)):
-            if i == 0:
-                (a, b, success) = self._callMotionPlanner(world, action, pose2)
-                if success:
-                    return []
-            else:
-                for l_tuple in itertools.combinations(range(len(obstacles)), i):
-                    updated_obstacles = copy.deepcopy(obstacles)
-                    l = list(l_tuple)
-                    l.reverse()
-                    for item in l:
-                        updated_obstacles.pop(item)
-                    if action[1] in [obstacle.id for obstacle in updated_obstacles]:
-                        a_whole_new_world.world.movable_objects = updated_obstacles
-                        (a, b, success) = self._callMotionPlanner(a_whole_new_world, action, pose2)
-                        if success:
-                            return [obstacles[i].id for i in l]'''
-        print "ERROR IN MP ERRORS!"
+            # if this doesn't work, there must be an immovable object in the way
+            return ['immovable']
         
     def resetCallCounts(self):
         self.numMotionPlannerCalls = 0
@@ -233,27 +216,28 @@ class InterfaceLayer(object):
                 if success: # if we succeeded, return!
                     return (hlplan[1:], partialTraj)
                     
-                # when we eventually failed, we failed because some object(s) were in the way -- we need to update our new task planning problem to incorporate that
-                (tempstate) = self.stateUpdate(state, failCause, failStep, prev_fail_step, hlplan, tworld)
-                # now, call the task planner again on the new state
-                (error, newPlan) = self._callTaskPlanner(tempstate)
+                if failCause[0] != 'immovable':
[…]

### 2015-04-17 scripts/interface_layer_organized.py
update dinterface

@@ -216,7 +216,7 @@ class InterfaceLayer(object):
                 if success: # if we succeeded, return!
                     return (hlplan[1:], partialTraj)
                     
-                if failCause[0] != 'immovable':
+                if len(failCause) == 0 || failCause[0] == 'immovable':
                     # when we eventually failed, we failed because some object(s) were in the way -- we need to update our new task planning problem to incorporate that
                     (tempstate) = self.stateUpdate(state, failCause, failStep, prev_fail_step, hlplan, tworld)
                     # now, call the task planner again on the new state
@@ -361,7 +361,7 @@ if __name__ == '__main__':
 
     genWorld = generateWorldMsg()
     
-    f = open(DIR + 'states/state3Blocks_1','r')
+    f = open(DIR + 'states/fivebyfive','r')
     init_state_string = f.read()
     
     state = [[]]*3
@@ -374,7 +374,7 @@ if __name__ == '__main__':
     pose = l[3]
     print state
 
-    world = genWorld.generateWorld('SQUARE',13)
+    world = genWorld.generateWorld('SQUARE',5)
 
     poseGen = MockPoseGenerator()
 

### 2015-04-17 scripts/interface_layer_organized.py
fixed typo

@@ -216,7 +216,7 @@ class InterfaceLayer(object):
                 if success: # if we succeeded, return!
                     return (hlplan[1:], partialTraj)
                     
-                if len(failCause) == 0 || failCause[0] == 'immovable':
+                if len(failCause) == 0 || failCause[0] != 'immovable':
                     # when we eventually failed, we failed because some object(s) were in the way -- we need to update our new task planning problem to incorporate that
                     (tempstate) = self.stateUpdate(state, failCause, failStep, prev_fail_step, hlplan, tworld)
                     # now, call the task planner again on the new state

### 2015-04-17 scripts/generateSmallWorldMsg.py
fixed bugs

@@ -12,6 +12,8 @@ class GenerateSmallWorldMsg:
 
 	# surface_and_blocks = a dictionary of surfaces and the number of blocks on each one
 	def generateWorld(self,surface_and_blocks):
+		self.block_idx = 0
+		self.wall_idx = 0
 		my_world = world_state()
 		my_world.world = world_obj()
 		for s,numBlocks in surface_and_blocks.iteritems():

### 2015-04-17 scripts/interface_layer_organized.py

@@ -216,7 +216,7 @@ class InterfaceLayer(object):
                 if success: # if we succeeded, return!
                     return (hlplan[1:], partialTraj)
                     
-                if len(failCause) == 0 || failCause[0] != 'immovable':
+                if len(failCause) == 0 or failCause[0] != 'immovable':
                     # when we eventually failed, we failed because some object(s) were in the way -- we need to update our new task planning problem to incorporate that
                     (tempstate) = self.stateUpdate(state, failCause, failStep, prev_fail_step, hlplan, tworld)
                     # now, call the task planner again on the new state

### 2015-04-17 scripts/stateGeneratorSmall.py

@@ -103,7 +103,7 @@ class StateGeneratorSmall:
 		goals = [("BLOCK0","S"),("BLOCK1","S"),("BLOCK2","S")]
 		self.generateFile(filename,["I","A","S"],initialPoses,goals)
 		
-		NUMBLOCKS = 4
+		self.NUMBLOCKS = 4
 
 		# state4Blocks_1
 		filename = "state4Blocks_1"

### 2015-04-17 scripts/interface_layer_organized.py
commented out printouts

@@ -190,11 +190,11 @@ class InterfaceLayer(object):
                 print "Error! Cannot find any high level plan. :("
                 return (False, False)
             hlplan.insert(0, (' ', ' ', ' ',' ', ' '))
-            print "HLPlan: ", hlplan
+            #print "HLPlan: ", hlplan
             # now that we have a high level plan, we try to actually turn it into motions in the real world
             
         while(num_iters < MAX_ITERS):
-            print "HIGHEST LEVEL ALG 1 ITERATION: ", num_iters
+            #print "HIGHEST LEVEL ALG 1 ITERATION: ", num_iters
             num_iters+=1
             
             # try to refine our plan, allowing for no errors
@@ -207,7 +207,7 @@ class InterfaceLayer(object):
             
             # if it didn't work, we need to start piece by piece
             while not success and trajCount < MAX_TRAJ_COUNT:
-                print "INNER LEVEL ALG 1 ITERATION: ", trajCount
+                #print "INNER LEVEL ALG 1 ITERATION: ", trajCount
 
                 # find a partial trajectory -- how far along the high level task plan can we find motion plans for?
                 (success, pose2, partialTraj, failStep, failCause, tstate, tworld) = trajRefiner.tryRefine(pose1, state, world, hlplan, step, partialTraj, mode='partialTraj')
@@ -230,7 +230,7 @@ class InterfaceLayer(object):
                     if not error: # it may not be possible to find a new plan; if it is, update our high level plan 
                         # if it wasn't possible to find a new plan, we'll start over to try and refine, but we'll pick different things because of the randomization
                         hlplan = hlplan[0:failStep+1] + newPlan
-                        print "HLPlan: ", hlplan
+                        #print "HLPlan: ", hlplan
                         pose1 = pose2
                         prev_fail_step = failStep
                         state = tempstate
@@ -253,7 +253,7 @@ class InterfaceLayer(object):
                 pose1 = copy.deepcopy(initPose)
                 (error, hlplan) = self._callTaskPlanner(state) # find a high level task plan
                 hlplan.insert(0, (' ', ' ', ' ',' ', ' '))
-                print "HLPlan: ", hlplan
+                #print "HLPlan: ", hlplan
                 if error:
                     print "ERROR ON TASK PLAN!"
                 
@@ -281,7 +281,7 @@ class TryRefine(object):
     def tryRefine(self, initPose, state, world, hlplan, step, trajprefix, mode):
[…]

### 2015-04-17 scripts/benchmark.py
bug in benchmark

@@ -33,9 +33,9 @@ DIR_6834 = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
 
 # One Cover Bechmark
 out_file = open('benchmark.output','w')
-# world_shapes = ["SQUARE","CROSS","X","HLINE","VLINE"]
-world_shapes = ["CROSS","X","HLINE","VLINE"]
-world_sizes = xrange(3,18,2)
+world_shapes = ["SQUARE","CROSS","X","HLINE","VLINE"]
+# world_shapes = ["CROSS","X","HLINE","VLINE"]
+world_sizes = xrange(3,14,2)
 
 for shape in world_shapes:
 	for size in world_sizes:
@@ -73,7 +73,7 @@ for shape in world_shapes:
 			numMotionPlannerCalls.append(interfaceLayer.numMotionPlannerCalls)
 			numTaskPlannerCalls.append(interfaceLayer.numTaskPlannerCalls)
 			runTimes.append(runTime)
-			fname=DIR_6834+"output/"+shape+str(size)+"_"+str(i)+".output"
+			fname=DIR_6834+"outputResults/"+shape+str(size)+"_"+str(i)+".output"
 			plan_traj = open(fname,'w')
 			# save hlplan & trajectory to output folder
 			plan_traj.write(str(hlplan)+"\n"+"\n")

### 2015-04-17 scripts/small_tests.py

@@ -24,7 +24,7 @@ from generateSmallWorldMsg import *
 # rosrun mock motion planner srv
 # rosrun mock task planner srv
 
-numTests = 1
+numTests = 10
 
 genState =  StateGeneratorSmall()
 
@@ -36,60 +36,58 @@ out_file = open('smallTests.output','w')
 # set up the world
 worlds = generateWorlds()
 genState.generateStates()
-i = 0
+
 for filename,world in worlds.iteritems():
-	if i == 0:
-		i = 1
-		print world
-		
-		filepath = DIR_6834+"states/" + filename		
-		f = open(filepath,'r')
-		init_state_string = f.read()
-		state = [[]]*3
-		l = init_state_string.split('\n')
-		state[0] = l[0].split(',')
-		k = l[1].split(',')
-		state[1] = [tuple(i.split(' ')) for i in k]
-		k = l[2].split(',')
-		state[2] = [tuple(i.split(' ')) for i in k]
-		pose = l[3]
+	print world
+	
+	filepath = DIR_6834+"states/" + filename		
+	f = open(filepath,'r')
+	init_state_string = f.read()
+	state = [[]]*3
+	l = init_state_string.split('\n')
+	state[0] = l[0].split(',')
+	k = l[1].split(',')
+	state[1] = [tuple(i.split(' ')) for i in k]
+	k = l[2].split(',')
+	state[2] = [tuple(i.split(' ')) for i in k]
+	pose = l[3]
 
-		# Difficulty Metric
-		numBlocks = len(world.world.movable_objects)
-		numObs = numObstructsWorld(world, 17)
+	# Difficulty Metric
+	numBlocks = len(world.world.movable_objects)
+	numObs = numObstructsWorld(world, 17)
 
-		numMotionPlannerCalls = []
-		numTaskPlannerCalls = []
-		runTimes = []
+	numMotionPlannerCalls = []
+	numTaskPlannerCalls = []
+	runTimes = []
 
-		# run multiple tests for this world
-		for i in range(numTests):
-			poseGen = MockPoseGenerator()
-			interfaceLayer = InterfaceLayer('task_server_service', 'motion_server_service', poseGen, mockStateUpdate, DIR_6834)
-			tic = time.time()
-			ret = interfaceLayer.run(state, world, pose)
-			print ret
-			runTime = time.time() - tic
[…]

### 2015-04-17 scripts/full_test.py
Path change

@@ -36,4 +36,4 @@ if __name__ == '__main__':
     print "\n\n\n OUTPUT FROM INTERFACE LAYER\n\n"
     print hlplan
     print traj
-w
+

### 2015-04-17 scripts/planner_server.py

@@ -47,6 +47,7 @@ class TaskPlannerServer(object):
 
 if __name__ == "__main__":
     #task_planner_server = TaskPlannerServer("/home/vmlane/catkin_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/vmlane/catkin_ws/src/6834-task-motion-planner/domain")
-    task_planner_server = TaskPlannerServer("/home/bhomberg/indigo_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/bhomberg/indigo_ws/src/6834-task-motion-planner/domain")
+    task_planner_server = TaskPlannerServer("/home/ragtz/Downloads/FF-v2.3/", "/home/ragtz/indigo_workspace/src/6834-task-motion-planner/domain")
+    #task_planner_server = TaskPlannerServer("/home/bhomberg/indigo_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/bhomberg/indigo_ws/src/6834-task-motion-planner/domain")
     task_planner_server.run()
     

### 2015-04-17 documentation/draft.tex

@@
 
--realistic expectations for someone interested in applying the reasoning technique
+The most important limitation of this implementation is to remember that it is an interface layer.  
+It does not include a task planner and a motion planner: you must set those up yourself as ROS services and make sure that the output and input message types specify those outlined in the API.  
+Depending on what planners you use, setting them up and installing them may be nontrivial.  
+Different planners are effective for different tasks and some planners may require extensive installation.  
+When you pick your task and motion planners, remember that this interface layer is set up to only work with task planners that use the PDDL specification language.  
+If you choose to use another specification system, you will need to translate between PDDL and your system.
 
--still need to get a motion planner and a task planner working and need to make them have the right API interface -- not a pure out of the box working thing
+On a more detailed level, it is important to note that this planner is not guaranteed to find an optimal solution, or even to find a solution at all.  
+We refer you to [1] for a proof that this algorithm is guaranteed to find a solution for problems with certain properties.  
+However, due to the random nature of the pose generators and that there are limits set on the number of iterations, a valid plan may not be found for all problems.
 
--is not guaranteed to find an optimal solution
+Furthermore, this system is not intended for online replanning.  
+It may be possible to use it for online replanning for some systems if it runs quickly on the particular problem, but it is not an intended feature of this algorithm.
 
--cannot do online re-planning
-
--time to run is based on speed of the motion planner and task planner
+Finally, the runtime of this algorithm is based on the speed of the motion planner and the task planner used within it.  
+If the motion planner and task planner are not efficient, the interface layer will not produce answers quickly.
 

### 2015-04-17 scripts/interface_layer_organized.py
finally got the bug, knock on wood

@@ -236,8 +236,8 @@ class InterfaceLayer(object):
                         state = tempstate
                         world = tworld
                         step = failStep
-                    if error:
-                        print "Failed to find high level plan, trying again."
+                    #if error:
+                    #    print "Failed to find high level plan, trying again."
                     
                 trajCount+=1
                 
@@ -289,11 +289,18 @@ class TryRefine(object):
             self.called = True
             self.old_hlplan = hlplan
             self.hlplan = hlplan
-            if len(self.worlds) > 1:
+            if len(self.worlds) > 1 and step > 0:
+                #print "step: ", step
+                #print 'here ', len(self.worlds)
                 self.worlds = self.worlds[0:step-1].append(copy.deepcopy(world))
+                #print 'there ', len(self.worlds)
             else:
+                #print 'and here too ', len(self.worlds)
                 self.worlds = [copy.deepcopy(world)]
+                #print 'and here ', len(self.worlds)
             #print "index: ", self.index
+            #print "world: ", world
+            #print "self.world: ", self.world
             #print "len worlds: ", len(self.worlds)
             self.interface.poseGenerator.resetAll()
             self.world = world
@@ -310,8 +317,17 @@ class TryRefine(object):
             self.pose2 = self.interface.poseGenerator.next(self.nextaxn)
             
             if self.pose2 == None: # pose 2 is already defined, so we should backtrack if in Error free mode, otherwise return that we've failed
-                self.interface.poseGenerator.reset(self.axn)
+                self.interface.poseGenerator.reset(self.nextaxn)
                 self.pose1 = self.interface.poseGenerator.next(self.axn)
+                if self.pose1 == None:
+                    #self.worlds.append(copy.deepcopy(self.world))
+                    self.interface.poseGenerator.resetAll()
+                    #print "index: ", self.index
+                    #print "worlds: ", len(self.worlds)
+                    #print "world", self.world
+                    return (False, self.pose1, self.traj, self.index, [], self.state, self.world)
+                    #print "ERRRRRRRRRRRR"
+                    #return 'woeighwoe'
                 #print "index: ", self.index
                 #print "worlds: ", len(self.worlds)
                 self.index-=1
@@ -329,6 +345,7 @@ class TryRefine(object):
                 #print "action: ", self.nextaxn
                 #print "pose: ", self.pose2
                 #print "index: ", self.index, "   worlds: ", len(self.worlds)
[…]

### 2015-04-17 scripts/interface_layer_organized.py
hacky fix but seems to be holding water

@@ -293,6 +293,8 @@ class TryRefine(object):
                 #print "step: ", step
                 #print 'here ', len(self.worlds)
                 self.worlds = self.worlds[0:step-1].append(copy.deepcopy(world))
+                if self.worlds == None:
+                    self.worlds = [copy.deepcopy(world)]
                 #print 'there ', len(self.worlds)
             else:
                 #print 'and here too ', len(self.worlds)

### 2015-04-18 documentation/draft.tex

@@
 In order to achieve high level goals a robot must combine task and motion planning. 
-A robot uses task planning to determine its long term strategy and motion planning to determine the movements movements it  will execute to achieve the task. 
+A robot uses task planning to determine its long term strategy and motion planning to determine the movements it  will execute to achieve the task. 
 Effectively combining task and motion planning is an open research problem. 
-We developed an interface between the motion and task planning. 
-Our system uses off-the-shelf task and motion planners and makes no assumptions about their implementation.
+We implemented an interface between the motion and task planning. 
+Our system uses off-the-shelf task and motion planners and makes few assumptions about their implementation.
 
@@
 The main contribution of this implementation is an interface layer.  
-This interface layer is designed to be planner-independent: that is, it can work with any motion planner and task planner, so long as the outputs from each are conformed to the interface specified by the API.
+This interface layer is designed to be planner-independent: that is, it can work with any motion planner and task planner, so long as the outputs from each are conformed to the interface specification.
 The interface layer interleaves calls between the task planner and the motion planner, using geometric feasibility determined through the motion planner to affect the state given to the task planner to plan from.
@@
 
-Specifically, the interface layer starts by generating a high level plan and attempting to generate motion plans corresponding to each action.  
-When it's not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner in an appropriate format.  
-Then, the task planner replans from that set state and the process continues.  
+The interface layer starts by asking the task planner to generate a high level plan and has the motion planner instaniate motion plans corresponding to each action.  
+When it's not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner.  
+Then, the task planner replans from that state and the process continues.  
 When necessary, backtracking occurs.
 
-In order to communicate with the task planner and motion planner, the interface layer utilizes ROS services.  
-For the task planner, the interface layer instantiates a server with a given PDDL domain file.  
-This domain file specifies the different actions that are feasible along with their preconditions and postconditions.  
-For individual service calls, the interface layer takes an internal `state' variable, converts it to PDDL format, and sends it to the server to be solved.  
-The task planner service responds with a high level plan or a notification that finding a plan failed.  
+At start time, the task planner is given a PDDL domain specifying the different actions that are feasible along with their preconditions and postconditions.  
+For individual calls to the task planner, the interface layer takes an internal `state' variable, converts it to PDDL format, and sends it along to be solved.  
+The task planner responds with a high level plan or a notification that finding a plan failed.  
 If finding a plan failed, the interface layer begins backtracking.  
@@
 
-For the motion planner, the interface layer again communicates via a ROS service.  
-The motion planner is given an action, a world state, and a pose or set of poses corresponding to sub-parts of the action.  
-If it is possible to perform the action using the intermediary poses specified, the motion plan returns the trajectory.  
+On each call to the motion planner, the interface layer provides the motion planner with the intended action, the world state, and a pose or set of poses  
+corresponding to sub-parts of the action. These poses are randomly generated for each action by a pose generator within the interface layer. 
+If it is possible to perform the action using the intermediary poses specified, the motion plan returns the trajectory and the updated world state.  
 If not, it returns an error message.
@@
 If the motion plan does not succeed, a variety of poses are tried.  
-Poses are generated randomly from a pose generator.  
-If no poses are successful, the interface layer determines what is blocking the motion plan from succeeding.  
-Specifically, it removes objects from the environment until a feasible motion plan is found.  
+Again, poses are generated randomly from a pose generator.  
+If no poses are successful, the interface layer determines what is blocking the motion plan from succeeding by removing objects from the environment until a feasible motion plan is found.  
 If still no feasible motion plan is found, backtracking is required.  
-If a feasible motion plan is found with some subset of objects removed, then that information is relayed back to the task planner.  
-The task planner replans from the step where we failed to find a motion plan.  
-At that state, we add in predicates corresponding to the object obstructions.  
-Then, the task planner replans from there.
+If a feasible motion plan is found with some subset of objects removed, then that information is relayed back to the task planner after the PDDL state is appropriatedly updated.
+This update adds predicates corresponding to the object obstructions, and the task planner is asked to replan starting from the step where we failed to find a motion plan.
+This whole process continues until a feasible motion plan has been found.
 
@@
 
-Veronica: probably should fix this to be a nice alignment environment within LaTeX
+\vspace{10}
 $PICKUP(obj_1, gripper, pose_1, pose_2, traj)$
@@
 
+\vspace{10}
+
 Here, we have three continuous variables that we represent symbolically: $traj$, for each of the trajectories, and $pose_1$ and $pose_2$, representing start and end locations for the robot's gripper.
@@
 
-$EMPTY(gripper)$ -- this specifies whether the gripper is empty and thus available to hold a block.
+\vspace{10}
 
-$ROBOTAT(pose_1)$ -- this specifies where the robot is.  $pose_1$ is a symbolic reference to a continuous variable.
+$EMPTY(gripper)$ -- gripper is empty and thus available to hold a block.
 
-$ISGPFG(pose, obj)$ -- this specifies whether a pose is a Gripper Pose For Grasping (GPFG) an object.
+$ROBOTAT(pose_1)$ -- robot pose,  $pose_1$ is a symbolic reference to a continuous variable.
 
-$ISMP(traj, pose_1, pose_2)$ -- this specifies whether a trajectory is a motion plan from one pose to another.
+$ISGPFG(pose, obj)$ -- $pose$ is a Gripper Pose For Grasping (GPFG) an object $obj$.
 
-$OBSTRUCTS(obj_1, traj, obj_2)$ -- this specifies whether an object blocks another object from being picked up along a trajectory.
+$ISMP(traj, pose_1, pose_2)$ -- $traj$ is a motion plan from $pose_1$ to $pose_2$.
 
-$PDOBSTRUCTS(obj_1, traj, obj_2, tloc)$ -- this specifies whether an object blocks another object from being put down at a particular location along a trajectory.
+$OBSTRUCTS(obj_1, traj, obj_2)$ -- $obj_1$ blocks $obj_2$ from being picked up along $traj$.
 
-$IN(obj_1, gripper)$ -- this specifies whether an object is currently grasped by the gripper.
+$PDOBSTRUCTS(obj_1, traj, obj_2, tloc)$ -- $obj_1$ blocks $obj_2$ from placement at $tloc$ along $traj$.
+
+$IN(obj_1, gripper)$ -- $obj_1$ currently grasped by $gripper$.
+
+\vspace{10}
 
@@
 
-The most important limitation of this implementation is to remember that it is an interface layer.  
-It does not include a task planner and a motion planner: you must set those up yourself as ROS services and make sure that the output and input message types specify those outlined in the API.  
-Depending on what planners you use, setting them up and installing them may be nontrivial.  
-Different planners are effective for different tasks and some planners may require extensive installation.  
-When you pick your task and motion planners, remember that this interface layer is set up to only work with task planners that use the PDDL specification language.  
-If you choose to use another specification system, you will need to translate between PDDL and your system.
-
-On a more detailed level, it is important to note that this planner is not guaranteed to find an optimal solution, or even to find a solution at all.  
+It is important to note that this planner is not guaranteed to find an optimal solution, or even to find a solution at all.  
 We refer you to [1] for a proof that this algorithm is guaranteed to find a solution for problems with certain properties.  

### 2015-04-18 documentation/draft.tex
worked on tutorial

--- 2015-04-17 documentation/draft.tex
@@
 
-veronica can probably write this section
+When the pose generator is called by the interface layer, it generates a set of random poses for each action.
+Each pose is made up of a set of waypoints.
+For example for the \textit{pickup} action, it generates the following waypoints: near the cylinder and pointing towards it, touching the cylinder, lifting the cylinder, and a standard home position.
+It passes one pose to the interface layer at a time, if none of the poses are feasible, the interface layer backtracks resets the pose generator.
+The TryRefine method of the interface layer attempts to generate a feasible motion plan linking a set of waypoints.
 
@@
 \subsection{Testing}
+We generated a set of small-scale tests to check the correctness of the interface layer.
+ref{fig-smallTest} Each test had three to four blocks initially placed on one or two surfaces.
+Some blocks were surrounded by three walls, and others were surrounded by 3 walls.
+This required the interface layer to find the pose that picked up the block in the correct location.
+Furthermore, some blocks which needed to be moved in order to achieve the goal were obstructed by other blocks, meaning that the other block had to be moved first.
 
@@
 
+We performed a variety of benchmarking tests to measure the performance of the interface.
+We measured the performance of each test by the number of calls to both the task planner and motion planner and the runtime.
+ref{table-benchmarkTable}
+The difficulty of a benchmark increased as the total number \textit{obstructions} increased.
+The total number of obstructions was counted by summing the number of directions around each block that were obstructed.
+For the ordinal directions, a neighboring block in any one of three locations obstructs the direction.
+For example, a neighboring block above, to the right or to the top right corner of a block obstructs the northeast direction of the block.
+Furthermore, as the number of blocks for a particular grid shape increased, the test difficulty increased, since the total number of obstructions increased.
+
 \subsection{Results}
+The goal of each test was to move the green block, at the center of a grid of blocks, to a goal surface.
+We tested a variety of different grid shapes, including a square grid, an X, a cross, and lines.
+We tested each grid shape over a range of sizes ranging from 3 to 13.
+ref{fig-benchmarks} The most difficult benchmark we tested was the 13x13 square grid.
+Larger tests caused the FF planner to segfault.
+The interface layer is designed to be independent of any specific task and motion planner libraries, therefore number of calls to the motion and task planner measures the performance of the interface layer.
 
-to include:
+\begin{figure}
+\begin{tabular}[t]{|l|l|l|l|l|l|}
+\hline
+Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
+Horizontal Line & 3 & ? & ? & ? & ?\\
+& 5 & ? & ? & ? & ?\\
+& 7 & ? & ? & ? & ?\\
+& 9 & ? & ? & ? & ?\\
+& 11 & ? & ? & ? & ?\\
+& 13 & ? & ? & ? & ?\\
+\hline
+Vertical lLne & 3 & ? & ? & ? & ?\\
+& 5 & ? & ? & ? & ?\\
+& 7 & ? & ? & ? & ?\\
+& 9 & ? & ? & ? & ?\\
+& 11 & ? & ? & ? & ?\\
+& 13 & ? & ? & ? & ?\\ 
+\hline
+X & 5 & ? & ? & ? & ?\\
+& 9 & ? & ? & ? & ?\\
+& 13 & ? & ? & ? & ?\\
+& 17 & ? & ? & ? & ?\\
+& 21 & ? & ? & ? & ?\\
+& 25 & ? & ? & ? & ?\\ 
+\hline
+Cross & 5 & ? & ? & ? & ?\\
+& 9 & ? & ? & ? & ?\\
+& 13 & ? & ? & ? & ?\\
+& 17 & ? & ? & ? & ?\\
+& 21 & ? & ? & ? & ?\\
+& 25 & ? & ? & ? & ?\\ 
+\hline
+Square & 9 & ? & ? & ? & ?\\
+& 25 & ? & ? & ? & ?\\
+& 49 & ? & ? & ? & ?\\
+& 81 & ? & ? & ? & ?\\
+& 121 & ? & ? & ? & ?\\
+& 169 & ? & ? & ? & ?\\ 
+\hline
 
--tables of results
-
--description of how we did benchmarking
-
--in particular, description of why we did number of calls to task and motion planner instead of total time taken
-
--discussion of testing procedure as well
-
+\end {tabular}
+\caption{Benchmark Tests}
+\label{benchmark}
+\end{figure}
 \section{Limitations}

### 2015-04-18 documentation/draft.tex
edits to tutorial

@@
 Effectively combining task and motion planning is an open research problem. 
-We implemented an interface between the motion and task planning. 
+We implemented an interface between the motion and task planning based on that outlined in [1]. 
 Our system uses off-the-shelf task and motion planners and makes few assumptions about their implementation.
@@
 The interface layer interleaves calls between the task planner and the motion planner, using geometric feasibility determined through the motion planner to affect the state given to the task planner to plan from.
-
-Specifically, we start by generating a high level plan and attempting to generate motion plans corresponding to each action.  
-When it's not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner in an appropriate format.  
-Then, the task planner replans from that set state and the process continues.  
-When necessary, backtracking occurs.
 
@@
 
-\vspace{10}
+\vspace{10pt}
+
 $PICKUP(obj_1, gripper, pose_1, pose_2, traj)$
@@
 
-\vspace{10}
+\vspace{10pt}
 
@@
 Each pose is made up of a set of waypoints.
-For example for the \textit{pickup} action, it generates the following waypoints: near the cylinder and pointing towards it, touching the cylinder, lifting the cylinder, and a standard home position.
-It passes one pose to the interface layer at a time, if none of the poses are feasible, the interface layer backtracks resets the pose generator.
-The TryRefine method of the interface layer attempts to generate a feasible motion plan linking a set of waypoints.
+For example for the PICKUP action, it generates the following waypoints: near the cylinder and pointing towards it, touching the cylinder, lifting the cylinder, and a standard home position.
+It passes one pose to the interface layer at a time.
+if none of the poses are feasible, the interface layer backtracks and resets the pose generator.
+The TryRefine method of the interface layer attempts to generate a feasible motion plan between each pose.
+The motion planner is called to create this motion plan, including motion plans between waypoints.
 
@@
 From there, we look for a high level plan.  
-If the problem is not solvable without any problematic environmental information, then the problem is unsolvable and we immediately return that information.  
+If the problem is not solvable even without any obstructions from the environment, then the problem is unsolvable and we immediately return that information.  
 If we do succeed at finding a high level task plan, we begin the process of attempting to find a motion corresponding to each action.
 
-First, we start by attempting to find a full refinement of the whole plan,calling the TryRefine subroutine in error-free mode.  
+First, we start by attempting to find a full refinement of the whole plan, calling the TryRefine subroutine in error-free mode.  
 If that succeeds, then we return the plan.
@@
 
+The two immediately relevant open questions are whether it's possible to design a similar interface between task and motion plans which returns optimal plans or which can be used to do online planning.
+
 -include more grasp primitives (e.g. push grasps)

### 2015-04-18 documentation/draft.tex

@@
 The two immediately relevant open questions are whether it's possible to design a similar interface between task and motion plans which returns optimal plans or which can be used to do online planning.
+Currently, the interface layer works only in deterministic, fully observable environments.  
+It would be very interesting to develop similar algorithms to work in non-deterministic or partially observable environments as well.
 
--include more grasp primitives (e.g. push grasps)
-
--partially observable or non-deterministic environments
-
--replanning online
+Other interesting and relevant extensions could include the addition of more grasp primitives, for instance, push grasp primitives.
 

### 2015-04-18 bechmarks/benchmark.py
Clean up

@@ -1,0 +1,100 @@
+#!/usr/bin/env python
+
+import time
+import sys
+import rospy
+from task_motion_planner.srv import *
+from task_motion_planner.msg import *
+from moveit_msgs.msg import *
+from geometry_msgs.msg import *
+import copy
+import itertools
+from random import shuffle
+from mockPoseGenerator import *
+from mockMotionPlanner import *
+from mockStateUpdate import *
+from interface_layer_organized import *
+from planner_server import *
+from generateWorldMsg import *
+from numObstructs import *
+import re
+from stateGenerator import *
+from generateWorldMsg import *
+
+# rosrun mock motion planner srv
+# rosrun mock task planner srv
+
+numTests = 10
+
+genWorld = generateWorldMsg()
+genState = StateGenerator()
+
+DIR_6834 = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
+
+# One Cover Bechmark
+out_file = open('benchmark.output','w')
+world_shapes = ["SQUARE","CROSS","X","HLINE","VLINE"]
+# world_shapes = ["CROSS","X","HLINE","VLINE"]
+world_sizes = xrange(3,14,2)
+
+for shape in world_shapes:
+	for size in world_sizes:
+		# set up the world
+		world = genWorld.generateWorld(shape,size)
+		filename = DIR_6834+"states/" + shape + "_" + str(size)
+		state = genState.genStateFromWorld(world,filename)
+		
+		f = open(filename,'r')
+		init_state_string = f.read()
+		state = [[]]*3
+		l = init_state_string.split('\n')
+		state[0] = l[0].split(',')
+		k = l[1].split(',')
+		state[1] = [tuple(i.split(' ')) for i in k]
+		k = l[2].split(',')
+		state[2] = [tuple(i.split(' ')) for i in k]
+		pose = l[3]
+
+		# Difficulty Metric
+		numBlocks = len(world.world.movable_objects)
+		numObs = numObstructsWorld(world, 17)
+
+		numMotionPlannerCalls = []
+		numTaskPlannerCalls = []
+		runTimes = []
+
+		# run multiple tests for this world
+		for i in range(numTests):
+			poseGen = MockPoseGenerator()
[…]

### 2015-04-18 src/full_test.py

@@ -1,0 +1,41 @@
+#!/usr/bin/env python
+
+from mockPoseGenerator import *
+from mockMotionPlanner import *
+import mockStateUpdate
+from interface_layer_organized import *
+from planner_server import *
+from generateWorldMsg import *
+
+DIR = '/home/vmlane/catkin_workspace/src/6834-task-motion-planner/'
+
+if __name__ == '__main__':
+
+    genWorld = generateWorldMsg()
+    
+    f = open(DIR+'states/one_cover','r')
+    init_state_string = f.read()
+    
+    state = [[]]*3
+    l = init_state_string.split('\n')
+    state[0] = l[0].split(',')
+    k = l[1].split(',')
+    state[1] = [i.split(' ') for i in k]
+    k = l[2].split(',')
+    state[2] = [i.split(' ') for i in k]
+    pose = l[3]
+
+    world = genWorld.generateWorld('SQUARE',3)
+
+    #task_planner_server = TaskPlannerServer(DIR+"/FF-v2.3/", DIR+"/domain")
+    #task_planner_server.run()
+    #motion_planner_server = MockMotionPlannerServer(17)
+    #motion_planner_server.run()
+    interfaceLayer = InterfaceLayer('task_server_service', 'motion_server_service', MockPoseGenerator, mockStateUpdate, DIR)
+    (hlplan, traj) = interfaceLayer.run(state, world, pose)
+    
+
+    print "\n\n\n OUTPUT FROM INTERFACE LAYER\n\n"
+    print hlplan
+    print traj
+

### 2015-04-18 src/generateSmallWorldMsg.py

@@ -1,0 +1,115 @@
+#!/usr/bin/python
+
+import roslib
+from task_motion_planner.msg import *
+
+class GenerateSmallWorldMsg:
+	def __init__(self):
+		self.WORLD_GRID_SIZE = 17
+		self.CENTER = self.WORLD_GRID_SIZE/2
+		self.block_idx = 0
+		self.wall_idx = 0
+
+	# surface_and_blocks = a dictionary of surfaces and the number of blocks on each one
+	def generateWorld(self,surface_and_blocks):
+		self.block_idx = 0
+		self.wall_idx = 0
+		my_world = world_state()
+		my_world.world = world_obj()
+		for s,numBlocks in surface_and_blocks.iteritems():
+			# add the surface to the world
+			surface = obj()
+			surface.id = s
+			my_world.world.surfaces.append(surface)
+			# add the blocks
+			self.generateBlockVLine(my_world.world,s,numBlocks)
+			if not numBlocks == 0:
+				self.generateWalls(my_world.world,s,-1,numBlocks)
+		return my_world
+
+	def generateBlockVLine(self,my_world,surface_id,length):
+		for i in xrange(self.CENTER,self.CENTER+length):
+			self._add_block(my_world,surface_id,i)
+
+	def generateWalls(self,my_world,surface_id,lb,ub):
+		for i in xrange(lb,ub):
+			# left wall
+			o = obj()
+			o.id = "WALL" + str(self.wall_idx)
+			self.wall_idx += 1
+			o.loc.surface_id = surface_id
+			o.loc.x = self.CENTER - 1
+			o.loc.y = self.CENTER + i
+			my_world.walls.append(o)
+			# right wall
+			o = obj()
+			o.id = "WALL" + str(self.wall_idx)
+			self.wall_idx += 1
+			o.loc.surface_id = surface_id
+			o.loc.x = self.CENTER + 1
+			o.loc.y = self.CENTER + i
+			my_world.walls.append(o)
+		# top wall
+		o = obj()
+		o.id = "WALL" + str(self.wall_idx)
+		o.loc.surface_id = surface_id
+		o.loc.x = self.CENTER
+		o.loc.y = self.CENTER + ub
+		my_world.walls.append(o)
+
+
+
+	def _add_block(self,my_world,surface_id,j):
[…]

### 2015-04-18 src/generateWorldMsg.py

@@ -1,0 +1,92 @@
+#!/usr/bin/python
+
+import roslib
+from task_motion_planner.msg import *
+
+MIN_BLOCK_GRID_SIZE = 3
+MAX_BLOCK_GRID_SIZE = 17
+
+class generateWorldMsg:
+	def __init__(self):
+		self.WORLD_GRID_SIZE = 17
+		self.CENTER = self.WORLD_GRID_SIZE/2
+
+	def generateWorld(self,block_shape,shape_size):
+		my_world = world_state()
+		my_world.world = world_obj()
+		surfaceS = obj()
+		surfaceS.id = 'S'
+		surfaceI = obj()
+		surfaceI.id = 'I'
+		my_world.world.surfaces = [surfaceS,surfaceI]
+		if block_shape=='SQUARE':
+			self.generateBlockGrid(my_world,shape_size)
+		elif block_shape=='CROSS':
+			self.generateBlockCross(my_world,shape_size)		
+		elif block_shape=='X':
+			self.generateBlockX(my_world,shape_size)
+		elif block_shape=='HLINE':
+			self.generateBlockHLine(my_world,shape_size)		
+		elif block_shape=='VLINE':
+			self.generateBlockVLine(my_world,shape_size)
+		return my_world
+
+	def generateBlockGrid(self,my_world,block_grid_size):
+		idx = 1
+		bound = block_grid_size/2
+		for j in xrange(-bound,bound+1):
+			for i in xrange(-bound,bound+1):
+				idx = self._add_block(my_world, i,j,idx)
+
+	def generateBlockCross(self,my_world,block_grid_size):
+		idx = 1
+		bound = block_grid_size/2
+		for j in xrange(-bound,bound+1):
+			for i in xrange(-bound,bound+1):
+				if i==0 or j==0:
+					idx = self._add_block(my_world,i,j,idx)	
+
+	def generateBlockHLine(self,my_world,length):
+		idx = 1
+		bound = length/2
+		for i in xrange(-bound,bound+1):
+			idx = self._add_block(my_world,i,0,idx)	
+
+	def generateBlockVLine(self,my_world,length):
+		idx = 1
+		bound = length/2
+		for i in xrange(-bound,bound+1):
+			idx = self._add_block(my_world,0,i,idx)
+
+	def generateBlockX(self,my_world,shape_size):
+		idx = 1
[…]

### 2015-04-18 src/interface_layer_organized.py

@@ -1,0 +1,410 @@
+#!/usr/bin/env python
+
+import sys
+import rospy
+from task_motion_planner.srv import *
+from task_motion_planner.msg import *
+from moveit_msgs.msg import *
+from geometry_msgs.msg import *
+import copy
+import itertools
+from random import shuffle
+from mockPoseGenerator import *
+from mockMotionPlanner import *
+from mockStateUpdate import *
+from interface_layer_organized import *
+from planner_server import *
+from generateWorldMsg import *
+
+MAX_TRAJ_COUNT = 50
+MAX_ITERS = 1000
+DIR = '/home/bhomberg/indigo_ws/src/6834-task-motion-planner/'
+#DIR = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
+
+class InterfaceLayer(object):    
+    def __init__(self, taskServerName, motionServerName, poseGenerator, stateUpdate, directory):        
+        self.taskServerName = taskServerName
+        self.taskServer = None
+        
+        self.motionServerName = motionServerName
+        self.motionServer = None
+        
+        self.poseGenerator = poseGenerator
+        self.stateUpdate = stateUpdate
+        
+        self.directory = directory
+        
+        self.numTaskPlannerCalls = 0
+        self.numMotionPlannerCalls = 0
+        
+        print "Initialized interface layer!"
+        
+    def _callTaskPlanner(self, state):
+        # plan is an array of tuples where the first thing is the action and the rest are objects it acts on
+        # state is organized as follows:
+        #    list of objects in the world
+        #    list of predicates true in the initial state
+        #    list of predicates for the goal
+        msg = task_domain()
+        #output state to file
+        f = open(self.directory + 'state', 'w')
+        f.write('(define (problem problemtask)\n')
+        f.write('(:domain taskmotion)\n')
+        f.write('(:objects ')
+        for o in state[0]:
+            f.write(o + ' ')
+        f.write(')\n')
+        f.write('(:init ')
+        for i in state[1]:
+            f.write('(')
+            for a in i:
+                f.write(a + ' ')
+                if a == 'NOT':
+                    f.write('(')
+            if i[0] == 'NOT':
+                f.write(')')
+            f.write(')\n')
+        f.write(')\n')
+        f.write('(:goal (and ')
+        for g in state[2]:
+            f.write('(')
+            for a in g:
+                f.write(a + ' ')
+                if a == 'NOT':
+                    f.write('(')
[…]

### 2015-04-18 src/mockMotionPlanner.py

@@ -1,0 +1,220 @@
+#!/usr/bin/env python
+
+import sys
+import rospy
+import re
+from copy import deepcopy
+from task_motion_planner.srv import *
+from task_motion_planner.msg import *
+
+class MockMotionPlannerServer(object):
+    def __init__(self, surface_dim):
+        self.surface_dim = surface_dim
+        
+    def getMotionPlan(self, req):
+        state = req.parameters.state
+        world = req.parameters.state.world
+        action = re.split(',', req.parameters.action[1:-1])
+        goals = req.parameters.goals
+        
+        #(pickup,obj1,left_arm,pose1,pose2)
+        #(putdown,obj1,left_arm,pose1,pose2,tloc)
+        
+        surfaces = dict()
+        for surface in world.surfaces:
+            surfaces[surface.id] = [[0 for i in range(self.surface_dim)] for j in range(self.surface_dim)]
+            
+        for wall in world.walls:
+            surface_id = wall.loc.surface_id
+            x = wall.loc.x
+            y = wall.loc.y
+            surfaces[surface_id][y][x] = 1
+        
+        for movable_object in world.movable_objects:
+            surface_id = movable_object.loc.surface_id
+            x = movable_object.loc.x
+            y = movable_object.loc.y
+            grasped = movable_object.loc.grasped
+    
+            if not grasped:
+                surfaces[surface_id][y][x] = 1
+    
+        res = motion_plan()
+        if action[0] == 'PICKUP':
+            object_id = goals.object_id
+            direction = goals.direction
+            
+            obj_idx = self._search_for_object(object_id, world.movable_objects)
+            if obj_idx == -1:
+                print "The object does not exist or is not movable"
+                return
+            
+            obj = world.movable_objects[obj_idx]
+            can_pickup = self._can_pickup(obj, direction, surfaces)
+            
+            if can_pickup:
+                state.world.movable_objects[obj_idx].loc.surface_id = ''
+                state.world.movable_objects[obj_idx].loc.x = -1
+                state.world.movable_objects[obj_idx].loc.y = -1
+                state.world.movable_objects[obj_idx].loc.grasped = True
+                
+                res.state = state
+                res.motion = 'picked up ' + obj.id + " from " + direction
+                res.success = True
+            else:
+                res.state = state
+                res.motion = ''
+                res.success = False
+            
+        elif action[0] == 'PUTDOWN':
+            object_id = goals.object_id
+            goal_surface_id = goals.surface_id
+            goal_x = goals.x
+            goal_y = goals.y
[…]

### 2015-04-18 src/mockPoseGenerator.py

@@ -1,0 +1,73 @@
+#!/usr/bin/python
+
+import rospy
+import roslib
+from task_motion_planner.msg import *
+from random import shuffle
+import numpy
+import re
+
+# TODO: Change to message type instead of dict, also add second action
+
+class MockPoseGenerator:
+    def __init__(self):
+        self.state = dict()
+
+    def next(self, action_tuple):
+        action = action_tuple[0]
+        obj = action_tuple[1]
+
+        msg = pose()
+        msg.object_id = obj
+        
+        # TODO get surface/obj
+        if action_tuple in self.state:
+            # if there are letters left, return it
+            if len(self.state[action_tuple]) > 0:
+                if action == 'PICKUP':
+                    msg.direction = self.state[action_tuple].pop()
+                else:
+                    location = self.state[action_tuple].pop()
+                    msg.x = location[0]
+                    msg.y = location[1]
+                    msg.surface_id = action_tuple[-1]
+                return msg
+            else:
+                return None
+        else:
+            # generate list of poses
+            if action == 'PICKUP':
+                self.state[action_tuple] = ['N','NE','E','SE','S','SW','W','NW']
+                shuffle(self.state[action_tuple])
+                msg.direction = self.state[action_tuple].pop()
+            else:
+                x_poses =  list(xrange(17))
+                y_poses = list(xrange(17))
+                shuffle(x_poses)
+                shuffle(y_poses)
+                self.state[action_tuple]=numpy.transpose([x_poses,y_poses]).tolist()
+                location = self.state[action_tuple].pop()
+                msg.x = location[0]
+                msg.y = location[1]
+                msg.surface_id = action_tuple[-1]
+            # return a pose
+            return msg
+
+    def reset(self, action):
+        if action in self.state:
+            del self.state[action]
+
+    def resetAll(self):
+        for action in self.state.keys():
+            del self.state[action]
+
+if __name__ == "__main__":
+    m = MockPoseGenerator()
+    for i in range(9):
+        print m.next('(PICKUP,1)')
+    for i in range(18):
+        print m.next('(PUTDOWN,1,surface)')
+    m.reset('PICKUP')
+    m.reset('PUTDOWN')
+    print m.next('(PICKUP,1)')
+    print m.next('(PUTDOWN,1,surface)')

### 2015-04-18 src/mockStateUpdate.py

@@ -1,0 +1,57 @@
+#!/usr/bin/env python
+
+import sys
+import rospy
+from task_motion_planner.msg import *
+import copy
+
+def mockStateUpdate(state_input, failCause, failStep, prev_fail_step, hlplan, world):
+        # stateUpdate will need to be updated based on the specific problem
+        state = copy.deepcopy(state_input)
+        for i in range(failStep-prev_fail_step):
+            action = hlplan[i+prev_fail_step+1]
+            if action[0] == 'PICKUP':
+                state[1].remove( ('EMPTY', action[2]) )
+                state[1].append( ('NOT', 'EMPTY', action[2]) )
+                state[1].remove( ('ROBOTAT', action[3]) )
+                state[1].append( ('ROBOTAT', action[4]) )
+                state[1].append( ('NOT', 'ROBOTAT', action[3]) )
+                state[1].append( ('IN', action[1], action[2]) )
+                for obj in world.world.movable_objects:
+                    state[1].append( ('NOT', 'OBSTRUCTS', action[1], obj.id) )                    
+                    t = ('OBSTRUCTS', action[1], obj.id)
+                    if t in state[1]:
+                        state[1].remove(t)
+                    for loc in world.world.surfaces:
+                            state[1].append( ('NOT', 'PDOBSTRUCTS', action[1], obj.id, loc.id) )
+                            t = ('PDOBSTRUCTS', action[1], obj.id, loc.id)
+                            if t in state[1]:
+                                    state[1].remove(t)
+                for loc in world.world.surfaces: 
+                    t = ('AT', action[1], loc.id)
+                    if t in state[1]:
+                        state[1].remove(t)
+            if action[0] == 'PUTDOWN':
+                state[1].remove( ('IN', action[1], action[2]) )
+                state[1].append( ('NOT', 'IN', action[1], action[2]) )
+                state[1].append( ('EMPTY', action[2]) )
+                state[1].remove( ('NOT', 'EMPTY', action[2]) )
+                state[1].append( ('AT', action[1], action[5]) )
+                t = ('NOT', 'AT', action[1], action[5])
+                if t in state[1]:
+                    state[1].remove(t)
+                state[1].remove( ('ROBOTAT', action[3]) )
+                state[1].append( ('ROBOTAT', action[4]) )
+
+
+        action = hlplan[failStep+1]
+        if action[0] == 'PICKUP':
+            obj_to_pickup = action[1]
[…]

### 2015-04-18 src/numObstructs.py

@@ -1,0 +1,158 @@
+#!/usr/bin/env python
+
+from task_motion_planner.msg import *
+
+# world is a world msg from generateWorldMsg
+# surface dim --> size of grid (default 17)
+def numObstructsWorld(world, surface_dim):
+    world = world.world
+    
+    surfaces = dict()
+    for surface in world.surfaces:
+        surfaces[surface.id] = [[0 for i in range(surface_dim)] for j in range(surface_dim)]
+    
+    for movable_object in world.movable_objects:
+        surface_id = movable_object.loc.surface_id
+        x = movable_object.loc.x
+        y = movable_object.loc.y
+        grasped = movable_object.loc.grasped
+
+        if not grasped:
+            surfaces[surface_id][y][x] = 1
+            
+    numObs = 0
+    for movable_object in world.movable_objects:
+        numObs += numObstructsObject(movable_object, surface_dim, surfaces)
+            
+    return numObs
+            
+def numObstructsObject(obj, surface_dim, surfaces):
+    numObs = 0
+    numObs += obstructsN(obj, surface_dim, surfaces)
+    numObs += obstructsNE(obj, surface_dim, surfaces)
+    numObs += obstructsE(obj, surface_dim, surfaces)
+    numObs += obstructsSE(obj, surface_dim, surfaces)
+    numObs += obstructsS(obj, surface_dim, surfaces)
+    numObs += obstructsSW(obj, surface_dim, surfaces)
+    numObs += obstructsW(obj, surface_dim, surfaces)
+    numObs += obstructsNW(obj, surface_dim, surfaces)
+    return numObs
+    
+def obstructsN(obj, surface_dim, surfaces):
+    surface_id = obj.loc.surface_id
+    x = obj.loc.x
+    y = obj.loc.y
+    
+    if y == 0 or surfaces[surface_id][y-1][x] == 0:
+        return False
+    else:
+        return True
+    
+def obstructsNE(obj, surface_dim, surfaces):
+    surface_id = obj.loc.surface_id
+    x = obj.loc.x
+    y = obj.loc.y
+    
+    if y == 0:
+        # cell to the right empty
+        if x < surface_dim-1 and surfaces[surface_id][y][x+1] == 0:
+                return False
+        else:
+            return False
+    elif x < surface_dim-1:
+        # above, above & right, right
[…]

### 2015-04-18 src/planner_server.py

@@ -1,0 +1,53 @@
+#!/usr/bin/env python
+
+from task_motion_planner.srv import *
+from task_motion_planner.msg import *
+import rospy
+import os
+
+class TaskPlannerServer(object):
+    def __init__(self, path, domain_file):
+        self.path = path
+        self.domain_file = domain_file
+        
+    def handle_pddl(self, req):
+        print "Serving task plan"
+        domain_file = "domain"
+        task_file = req.domain.task_file
+        ff_call = self.path + "./ff -o " + self.domain_file + " -f " + task_file + " > output" 
+        os.system(ff_call)
+
+        msg = hl_plan()
+        msg.error = True
+        actions = False
+
+        f = open('output')
+        s = ""
+        for line in f:
+            if line[0:4]=='step':
+                msg.error = False
+                actions = True
+                s = s + line[11:-1]
+            elif actions == True:
+                if line  == '\n':
+                    actions = False
+                else:
+                    s = s + '\n' + line[11:-1]
+        f.close()
+        msg.plan = s
+        #print "string: ", s
+
+        return msg
+
+    def run(self):
+        rospy.init_node('task_planner_server')
+        s = rospy.Service('task_server_service', task_service, self.handle_pddl)
+        print "Ready to serve task plans"
+        rospy.spin()
+
+if __name__ == "__main__":
+    #task_planner_server = TaskPlannerServer("/home/vmlane/catkin_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/vmlane/catkin_ws/src/6834-task-motion-planner/domain")
+    task_planner_server = TaskPlannerServer("/home/ragtz/Downloads/FF-v2.3/", "/home/ragtz/indigo_workspace/src/6834-task-motion-planner/domain")
+    #task_planner_server = TaskPlannerServer("/home/bhomberg/indigo_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/bhomberg/indigo_ws/src/6834-task-motion-planner/domain")
+    task_planner_server.run()
+    

### 2015-04-18 src/stateGenerator.py

@@ -1,0 +1,82 @@
+#!/usr/bin/python
+
+import sys
+
+# The number of blocks (including block 0)
+# set by command line args
+
+
+# Concatenate substrings & add numbers between them, do this for the number of blocks
+# strs = substrings to concatenate (with number between each substring)
+# the final character of the return strign
+# whether or not to add a number after the last substring
+# the block # to start at
+class StateGenerator:
+	def __init__(self):
+		self.NUMBLOCKS = 10
+
+	def concatMult(self,strs,last,end=False,start=0):
+		s = ''
+		r = len(strs) if end else len(strs)-1 
+		for i in range(start, self.NUMBLOCKS):
+			for x in range(r):
+				s += strs[x]+str(i)
+			if r < len(strs):
+				s += strs[-1]
+			if not i == self.NUMBLOCKS-1:
+				s += ","
+		s += last
+		return s
+
+	def generateString(self):
+		s = ''
+		# environment
+		s += self.concatMult(["BLOCK"," - physob"],",")
+		s += "LEFTARM - gripper,"
+		s += self.concatMult(["GP_BLOCK"," - pose"],",")
+		s += self.concatMult(["PDP_BLOCK","_S - pose"],",")
+		s += self.concatMult(["PDP_BLOCK","_I - pose"],",")
+		s += "INITPOSE - pose,"
+		s += "S - location,"
+		s += "I - location\n"
+		# initial conditions
+		s += "ROBOTAT INITPOSE,EMPTY LEFTARM,"
+		s += self.concatMult(["ISGPFG GP_BLOCK", " BLOCK"],",",True)
+		s += self.concatMult(["ISGPFPD PDP_BLOCK","_S BLOCK", " S"],",")
+		s += self.concatMult(["ISGPFPD PDP_BLOCK","_I BLOCK", " I"],",")
+		s += self.concatMult(["ISLFPD S BLOCK"],",",True)
+		s += self.concatMult(["ISLFPD I BLOCK"],",",True)
+		s += self.concatMult(["AT BLOCK", " I"],"\n")
+		# goal
+		s += "AT BLOCK0 S\n"
+		# initial pose
+		s += "INITPOSE"
+
+		return s
+
+	def generateFile(self,filename):
+		s = self.generateString()
+		f = open(filename, 'w')
+		f.write(s)
+		f.close()
+
+	def genStateFromWorld(self,world,filename):
[…]

### 2015-04-18 src/stateGeneratorSmall.py

@@ -1,0 +1,132 @@
+#!/usr/bin/python
+
+DIR = '../states/'
+
+class StateGeneratorSmall:
+	def __init__(self):
+		self.NUMBLOCKS = 10
+
+	# Concatenate substrings & add numbers between them, do this for the number of blocks
+	# strs = substrings to concatenate (with number between each substring)
+	# the final character of the return strign
+	# whether or not to add a number after the last substring
+	# the block # to start at
+	def concatMult(self,strs,last,end=False,start=0):
+		s = ''
+		r = len(strs) if end else len(strs)-1 
+		for i in range(start, self.NUMBLOCKS):
+			for x in range(r):
+				s += strs[x]+str(i)
+			if r < len(strs):
+				s += strs[-1]
+			if not i == self.NUMBLOCKS-1:
+				s += ","
+		s += last
+		return s
+
+	def generateString(self, surface_ids, initialPoses, goals):
+		s = ''
+		# environment
+		s += self.concatMult(["BLOCK"," - physob"],",")
+		s += "LEFTARM - gripper,"
+		s += self.concatMult(["GP_BLOCK"," - pose"],",")
+		for s_id in surface_ids:
+			s2 = "_" + s_id + " - pose"
+			s += self.concatMult(["PDP_BLOCK",s2],",")
+		s += "INITPOSE - pose,"
+
+		for i in range(len(surface_ids)):
+			s += surface_ids[i] + " - location"
+			if i < len(surface_ids) - 1:
+				s += ","
+			else:
+				s += "\n"
+		
+		# initial conditions
+		s += "ROBOTAT INITPOSE,EMPTY LEFTARM,"
+		s += self.concatMult(["ISGPFG GP_BLOCK", " BLOCK"],",",True)
+		for s_id in surface_ids:
+			middle = "_" + s_id + " BLOCK"
+			end = " " + s_id
+			s += self.concatMult(["ISGPFPD PDP_BLOCK",middle, end],",")
+		for s_id in surface_ids:
+			s2 = "ISLFPD " + s_id + " BLOCK"
+			s += self.concatMult([s2],",",True)
+		# initial block locations
+		for block in initialPoses:
+			s += "AT " + block[0] + " " + block[1] + ","
[…]

### 2015-04-18 tests/small_tests.py

@@ -1,0 +1,94 @@
+#!/usr/bin/env python
+
+import time
+import sys
+import rospy
+from task_motion_planner.srv import *
+from task_motion_planner.msg import *
+from moveit_msgs.msg import *
+from geometry_msgs.msg import *
+import copy
+import itertools
+from random import shuffle
+from mockPoseGenerator import *
+from mockMotionPlanner import *
+from mockStateUpdate import *
+from interface_layer_organized import *
+from planner_server import *
+from generateWorldMsg import *
+from numObstructs import *
+import re
+from stateGeneratorSmall import *
+from generateSmallWorldMsg import *
+
+# rosrun mock motion planner srv
+# rosrun mock task planner srv
+
+numTests = 10
+
+genState =  StateGeneratorSmall()
+
+DIR_6834 = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
+
+# One Cover Bechmark
+out_file = open('smallTests.output','w')
+
+# set up the world
+worlds = generateWorlds()
+genState.generateStates()
+
+for filename,world in worlds.iteritems():
+	print world
+	
+	filepath = DIR_6834+"states/" + filename		
+	f = open(filepath,'r')
+	init_state_string = f.read()
+	state = [[]]*3
+	l = init_state_string.split('\n')
+	state[0] = l[0].split(',')
+	k = l[1].split(',')
+	state[1] = [tuple(i.split(' ')) for i in k]
+	k = l[2].split(',')
+	state[2] = [tuple(i.split(' ')) for i in k]
+	pose = l[3]
+
+	# Difficulty Metric
+	numBlocks = len(world.world.movable_objects)
+	numObs = numObstructsWorld(world, 17)
+
+	numMotionPlannerCalls = []
+	numTaskPlannerCalls = []
+	runTimes = []
+
+	fname=DIR_6834+"outputResults/"+filename+".output"
+	outFile = open(fname,'w')
+	# run multiple tests for this world
+	for i in range(numTests):
+		poseGen = MockPoseGenerator()
+		interfaceLayer = InterfaceLayer('task_server_service', 'motion_server_service', poseGen, mockStateUpdate, DIR_6834)
+		tic = time.time()
+		ret = interfaceLayer.run(state, world, pose)
+		runTime = time.time() - tic
[…]

### 2015-04-18 documentation/draft.tex
added test and benchmark figures

@@
 \usepackage{enumerate}
+\usepackage{svg}
 
@@
 \headsep=0.25in
+
+\DeclareGraphicsExtensions{.jpg,.png,.svg}
 
@@
 ref{fig-smallTest} Each test had three to four blocks initially placed on one or two surfaces.
-Some blocks were surrounded by three walls, and others were surrounded by 3 walls.
-This required the interface layer to find the pose that picked up the block in the correct location.
-Furthermore, some blocks which needed to be moved in order to achieve the goal were obstructed by other blocks, meaning that the other block had to be moved first.
+Some blocks were surrounded on 3 sides and others on all sides by walls and blocks.
+For blocks surrounded on 3 sides, the interface layer had to find the pose that picked up the block in the correct direction.
+For blocks surrounded on all sides, the interface layer needed to generate actions to move blocks in the way.
+
+\begin{figure}[t]
+\centering
+\def\svgwidth{0.5\textwidth}
+\input{figures/smallEnv.pdf_tex}
+\caption{Small Environment Test Example. The goal was for the blue blocks to be on surface I and the red blocks to be on surface S.}
+\end{figure}
 
@@
 Furthermore, as the number of blocks for a particular grid shape increased, the test difficulty increased, since the total number of obstructions increased.
+
+\begin{figure}[t]
+\centering
+\def\svgwidth{\textwidth}
+\input{figures/benchmarks.pdf_tex}
+\caption{Benchmarking Test Examples. The goal was to move the green block to another surface.}
+\end{figure}
 

### 2015-04-18 documentation/draft.tex
filled in table

--- 2015-04-18 documentation/draft.tex
@@
 
+\subsubsection{Algorithm Improvements}
+
+The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.
+Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.
+In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the high level plan more complicated.
+In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.
+An analysis of the benefits of this approach are outlined in the benchmarking section.
+
 \subsubsection{Algorithm 1}
@@
 The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.
-Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.
-In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the plan more complicated.
-In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.
-An analysis of the benefits of this approach are outlined in the benchmarking section.
+For our version of the algorithm, every time a new partial plan is generated, we first try to fill it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.
 
@@
 Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
-Horizontal Line & 3 & ? & ? & ? & ?\\
-& 5 & ? & ? & ? & ?\\
-& 7 & ? & ? & ? & ?\\
-& 9 & ? & ? & ? & ?\\
-& 11 & ? & ? & ? & ?\\
-& 13 & ? & ? & ? & ?\\
+Horizontal Line & 3 & 12 & 3 & 1 & .023\\
+& 5 & 24 & 4 & 1 & .028\\
+& 7 & 36 & 4 & 1 & .029\\
+& 9 & 48 & 4 & 1 & .029\\
+& 11 & 60 & 4 & 1 & .034\\
+& 13 & 72 & 4 & 1 & .037\\
 \hline
-Vertical lLne & 3 & ? & ? & ? & ?\\
-& 5 & ? & ? & ? & ?\\
-& 7 & ? & ? & ? & ?\\
-& 9 & ? & ? & ? & ?\\
-& 11 & ? & ? & ? & ?\\
-& 13 & ? & ? & ? & ?\\ 
+Vertical Line & 3 & 12 & 4 & 1 & .024\\
+& 5 & 24 & 4 & 1 & .027\\
+& 7 & 36 & 4 & 1 & .028\\
+& 9 & 48 & 4 & 1 & .028\\
+& 11 & 60 & 4 & 1 & .037\\
+& 13 & 72 & 4 & 1 & .036\\ 
 \hline
-X & 5 & ? & ? & ? & ?\\
-& 9 & ? & ? & ? & ?\\
-& 13 & ? & ? & ? & ?\\
-& 17 & ? & ? & ? & ?\\
-& 21 & ? & ? & ? & ?\\
-& 25 & ? & ? & ? & ?\\ 
+X & 5 & 8 & 2 & 1 & .026\\
+& 9 & 16 & 2 & 1 & .034\\
+& 13 & 24 & 2 & 1 & .036\\
+& 17 & 32 & 2 & 1 & .047\\
+& 21 & 40 & 2 & 1 & .066\\
+& 25 & 48 & 2 & 1 & .079\\ 
 \hline
-Cross & 5 & ? & ? & ? & ?\\
-& 9 & ? & ? & ? & ?\\
-& 13 & ? & ? & ? & ?\\
-& 17 & ? & ? & ? & ?\\
-& 21 & ? & ? & ? & ?\\
-& 25 & ? & ? & ? & ?\\ 
+Cross & 5 & 20 & 39 & 3 & .16\\
+& 9 & 44 & 50 & 2 & .20\\
+& 13 & 68 & 59 & 2 & .23\\
+& 17 & 92 & 71 & 3 & .26\\
+& 21 & 116 & 78 & 3 & .31\\
+& 25 & 140 & 77 & 3 & .39\\ 
 \hline
-Square & 9 & ? & ? & ? & ?\\
-& 25 & ? & ? & ? & ?\\
-& 49 & ? & ? & ? & ?\\
-& 81 & ? & ? & ? & ?\\
-& 121 & ? & ? & ? & ?\\
-& 169 & ? & ? & ? & ?\\ 
+Square & 9 & 56 & 54 & 2 & .16\\
+& 25 & 176 & 294 & 6 & 1.06\\
+& 49 & 360 & 818 & 10 & 5.07\\
+& 81 & 608 & 3177 & 24 & 34.68\\
+& 121 & 920 & 3681 & 22 & 87.06\\
+& 169 & 1296 & 14216 & 57 & 518.61\\ 
 \hline

### 2015-04-18 scripts/benchmark.py
Cleanup

@@ -1,100 +1,0 @@
-#!/usr/bin/env python
-
-import time
-import sys
-import rospy
-from task_motion_planner.srv import *
-from task_motion_planner.msg import *
-from moveit_msgs.msg import *
-from geometry_msgs.msg import *
-import copy
-import itertools
-from random import shuffle
-from mockPoseGenerator import *
-from mockMotionPlanner import *
-from mockStateUpdate import *
-from interface_layer_organized import *
-from planner_server import *
-from generateWorldMsg import *
-from numObstructs import *
-import re
-from stateGenerator import *
-from generateWorldMsg import *
-
-# rosrun mock motion planner srv
-# rosrun mock task planner srv
-
-numTests = 10
-
-genWorld = generateWorldMsg()
-genState = StateGenerator()
-
-DIR_6834 = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
-
-# One Cover Bechmark
-out_file = open('benchmark.output','w')
-world_shapes = ["SQUARE","CROSS","X","HLINE","VLINE"]
-# world_shapes = ["CROSS","X","HLINE","VLINE"]
-world_sizes = xrange(3,14,2)
-
-for shape in world_shapes:
-	for size in world_sizes:
-		# set up the world
-		world = genWorld.generateWorld(shape,size)
-		filename = DIR_6834+"states/" + shape + "_" + str(size)
-		state = genState.genStateFromWorld(world,filename)
-		
-		f = open(filename,'r')
-		init_state_string = f.read()
-		state = [[]]*3
-		l = init_state_string.split('\n')
-		state[0] = l[0].split(',')
-		k = l[1].split(',')
-		state[1] = [tuple(i.split(' ')) for i in k]
-		k = l[2].split(',')
-		state[2] = [tuple(i.split(' ')) for i in k]
-		pose = l[3]
-
-		# Difficulty Metric
-		numBlocks = len(world.world.movable_objects)
-		numObs = numObstructsWorld(world, 17)
-
-		numMotionPlannerCalls = []
-		numTaskPlannerCalls = []
-		runTimes = []
-
-		# run multiple tests for this world
-		for i in range(numTests):
-			poseGen = MockPoseGenerator()
[…]

### 2015-04-18 scripts/generateSmallWorldMsg.py

@@ -1,115 +1,0 @@
-#!/usr/bin/python
-
-import roslib
-from task_motion_planner.msg import *
-
-class GenerateSmallWorldMsg:
-	def __init__(self):
-		self.WORLD_GRID_SIZE = 17
-		self.CENTER = self.WORLD_GRID_SIZE/2
-		self.block_idx = 0
-		self.wall_idx = 0
-
-	# surface_and_blocks = a dictionary of surfaces and the number of blocks on each one
-	def generateWorld(self,surface_and_blocks):
-		self.block_idx = 0
-		self.wall_idx = 0
-		my_world = world_state()
-		my_world.world = world_obj()
-		for s,numBlocks in surface_and_blocks.iteritems():
-			# add the surface to the world
-			surface = obj()
-			surface.id = s
-			my_world.world.surfaces.append(surface)
-			# add the blocks
-			self.generateBlockVLine(my_world.world,s,numBlocks)
-			if not numBlocks == 0:
-				self.generateWalls(my_world.world,s,-1,numBlocks)
-		return my_world
-
-	def generateBlockVLine(self,my_world,surface_id,length):
-		for i in xrange(self.CENTER,self.CENTER+length):
-			self._add_block(my_world,surface_id,i)
-
-	def generateWalls(self,my_world,surface_id,lb,ub):
-		for i in xrange(lb,ub):
-			# left wall
-			o = obj()
-			o.id = "WALL" + str(self.wall_idx)
-			self.wall_idx += 1
-			o.loc.surface_id = surface_id
-			o.loc.x = self.CENTER - 1
-			o.loc.y = self.CENTER + i
-			my_world.walls.append(o)
-			# right wall
-			o = obj()
-			o.id = "WALL" + str(self.wall_idx)
-			self.wall_idx += 1
-			o.loc.surface_id = surface_id
-			o.loc.x = self.CENTER + 1
-			o.loc.y = self.CENTER + i
-			my_world.walls.append(o)
-		# top wall
-		o = obj()
-		o.id = "WALL" + str(self.wall_idx)
-		o.loc.surface_id = surface_id
-		o.loc.x = self.CENTER
-		o.loc.y = self.CENTER + ub
-		my_world.walls.append(o)
-
-
-
-	def _add_block(self,my_world,surface_id,j):
[…]

### 2015-04-18 scripts/generateWorldMsg.py

@@ -1,92 +1,0 @@
-#!/usr/bin/python
-
-import roslib
-from task_motion_planner.msg import *
-
-MIN_BLOCK_GRID_SIZE = 3
-MAX_BLOCK_GRID_SIZE = 17
-
-class generateWorldMsg:
-	def __init__(self):
-		self.WORLD_GRID_SIZE = 17
-		self.CENTER = self.WORLD_GRID_SIZE/2
-
-	def generateWorld(self,block_shape,shape_size):
-		my_world = world_state()
-		my_world.world = world_obj()
-		surfaceS = obj()
-		surfaceS.id = 'S'
-		surfaceI = obj()
-		surfaceI.id = 'I'
-		my_world.world.surfaces = [surfaceS,surfaceI]
-		if block_shape=='SQUARE':
-			self.generateBlockGrid(my_world,shape_size)
-		elif block_shape=='CROSS':
-			self.generateBlockCross(my_world,shape_size)		
-		elif block_shape=='X':
-			self.generateBlockX(my_world,shape_size)
-		elif block_shape=='HLINE':
-			self.generateBlockHLine(my_world,shape_size)		
-		elif block_shape=='VLINE':
-			self.generateBlockVLine(my_world,shape_size)
-		return my_world
-
-	def generateBlockGrid(self,my_world,block_grid_size):
-		idx = 1
-		bound = block_grid_size/2
-		for j in xrange(-bound,bound+1):
-			for i in xrange(-bound,bound+1):
-				idx = self._add_block(my_world, i,j,idx)
-
-	def generateBlockCross(self,my_world,block_grid_size):
-		idx = 1
-		bound = block_grid_size/2
-		for j in xrange(-bound,bound+1):
-			for i in xrange(-bound,bound+1):
-				if i==0 or j==0:
-					idx = self._add_block(my_world,i,j,idx)	
-
-	def generateBlockHLine(self,my_world,length):
-		idx = 1
-		bound = length/2
-		for i in xrange(-bound,bound+1):
-			idx = self._add_block(my_world,i,0,idx)	
-
-	def generateBlockVLine(self,my_world,length):
-		idx = 1
-		bound = length/2
-		for i in xrange(-bound,bound+1):
-			idx = self._add_block(my_world,0,i,idx)
-
-	def generateBlockX(self,my_world,shape_size):
-		idx = 1
[…]

### 2015-04-18 scripts/interface_layer.py

@@ -1,433 +1,0 @@
-#!/usr/bin/env python
-
-import sys
-import rospy
-from task_motion_planner.srv import *
-from task_motion_planner.msg import *
-from moveit_msgs.msg import *
-from geometry_msgs.msg import *
-import copy
-import itertools
-from random import shuffle
-
-MAX_TRAJ_COUNT = 3
-MAX_ITERS = 1
-task_server = None
-motion_server = None
-# TODO: if necessary, add in random seed for pose generators later
-DIR = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/state'
-
-class InterfaceLayer(object):
-    # This class is NOT a complete class.  Several functions must be implemented in order
-    # to work with your specific motion planner and your specific task planner.  In particular, 
-    # the callTaskPlanner function must be implemented to take inputs in the appropriate format
-    # and return a high level plan in the correct format.  Similarly, get_motion_plan must be
-    # implemented to do the same with the motion planner.  Finally, stateUpdate must be 
-    # implemented to correctly handle updating the state based on errors identified via the
-    # interface layer.  The class SpecificInterfaceLayer in this file properly extends
-    # InterfaceLayer and implements the appropriate methods.
-    
-    def __init__(self, ):
-        pass
-        
-    def run_interface_layer(self, state, initialPose, world):
-        # set up initial variables
-        initial_state = state
-        initial_world = world
-        step = None
-        hlplan = None
-        partialTraj = []
-        pose1 = None
-        num_iters = 0
-        # create our tryRefine object, since that function needs to maintain its local variables
-        sub = tryRefineClass()
-        print state
-        print world
-        
-        if hlplan == None: # ie, we haven't started planning yet
-            (error, hlplan) = self.callTaskPlanner(state) # find a high level task plan
-            step = 0
-            partialTraj = []
-            pose1 = initialPose
-            if error:
-                return "Error! Cannot find any high level plan. :("
-            print "HLPlan: ", hlplan
-            # now that we have a high level plan, we try to actually turn it into motions in the real world
-        while(num_iters < MAX_ITERS):
-            print "HIGHEST LEVEL ALG 1 ITERATION: ", num_iters
-            num_iters+=1
-            # try to refine our plan, allowing for no errors
-            (success, t6, traj, t1, t2, t3, t4) = sub.try_refine(pose1, state, world, hlplan, step, partialTraj, 'errorFree')
-            #print "blaH
-            print traj
[…]

### 2015-04-18 scripts/interface_layer_organized.py

@@ -1,410 +1,0 @@
-#!/usr/bin/env python
-
-import sys
-import rospy
-from task_motion_planner.srv import *
-from task_motion_planner.msg import *
-from moveit_msgs.msg import *
-from geometry_msgs.msg import *
-import copy
-import itertools
-from random import shuffle
-from mockPoseGenerator import *
-from mockMotionPlanner import *
-from mockStateUpdate import *
-from interface_layer_organized import *
-from planner_server import *
-from generateWorldMsg import *
-
-MAX_TRAJ_COUNT = 50
-MAX_ITERS = 1000
-DIR = '/home/bhomberg/indigo_ws/src/6834-task-motion-planner/'
-#DIR = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
-
-class InterfaceLayer(object):    
-    def __init__(self, taskServerName, motionServerName, poseGenerator, stateUpdate, directory):        
-        self.taskServerName = taskServerName
-        self.taskServer = None
-        
-        self.motionServerName = motionServerName
-        self.motionServer = None
-        
-        self.poseGenerator = poseGenerator
-        self.stateUpdate = stateUpdate
-        
-        self.directory = directory
-        
-        self.numTaskPlannerCalls = 0
-        self.numMotionPlannerCalls = 0
-        
-        print "Initialized interface layer!"
-        
-    def _callTaskPlanner(self, state):
-        # plan is an array of tuples where the first thing is the action and the rest are objects it acts on
-        # state is organized as follows:
-        #    list of objects in the world
-        #    list of predicates true in the initial state
-        #    list of predicates for the goal
-        msg = task_domain()
-        #output state to file
-        f = open(self.directory + 'state', 'w')
-        f.write('(define (problem problemtask)\n')
-        f.write('(:domain taskmotion)\n')
-        f.write('(:objects ')
-        for o in state[0]:
-            f.write(o + ' ')
-        f.write(')\n')
-        f.write('(:init ')
-        for i in state[1]:
-            f.write('(')
-            for a in i:
-                f.write(a + ' ')
-                if a == 'NOT':
-                    f.write('(')
-            if i[0] == 'NOT':
-                f.write(')')
-            f.write(')\n')
-        f.write(')\n')
-        f.write('(:goal (and ')
-        for g in state[2]:
-            f.write('(')
-            for a in g:
-                f.write(a + ' ')
-                if a == 'NOT':
-                    f.write('(')
[…]

### 2015-04-18 scripts/mockMotionPlanner.py

@@ -1,220 +1,0 @@
-#!/usr/bin/env python
-
-import sys
-import rospy
-import re
-from copy import deepcopy
-from task_motion_planner.srv import *
-from task_motion_planner.msg import *
-
-class MockMotionPlannerServer(object):
-    def __init__(self, surface_dim):
-        self.surface_dim = surface_dim
-        
-    def getMotionPlan(self, req):
-        state = req.parameters.state
-        world = req.parameters.state.world
-        action = re.split(',', req.parameters.action[1:-1])
-        goals = req.parameters.goals
-        
-        #(pickup,obj1,left_arm,pose1,pose2)
-        #(putdown,obj1,left_arm,pose1,pose2,tloc)
-        
-        surfaces = dict()
-        for surface in world.surfaces:
-            surfaces[surface.id] = [[0 for i in range(self.surface_dim)] for j in range(self.surface_dim)]
-            
-        for wall in world.walls:
-            surface_id = wall.loc.surface_id
-            x = wall.loc.x
-            y = wall.loc.y
-            surfaces[surface_id][y][x] = 1
-        
-        for movable_object in world.movable_objects:
-            surface_id = movable_object.loc.surface_id
-            x = movable_object.loc.x
-            y = movable_object.loc.y
-            grasped = movable_object.loc.grasped
-    
-            if not grasped:
-                surfaces[surface_id][y][x] = 1
-    
-        res = motion_plan()
-        if action[0] == 'PICKUP':
-            object_id = goals.object_id
-            direction = goals.direction
-            
-            obj_idx = self._search_for_object(object_id, world.movable_objects)
-            if obj_idx == -1:
-                print "The object does not exist or is not movable"
-                return
-            
-            obj = world.movable_objects[obj_idx]
-            can_pickup = self._can_pickup(obj, direction, surfaces)
-            
-            if can_pickup:
-                state.world.movable_objects[obj_idx].loc.surface_id = ''
-                state.world.movable_objects[obj_idx].loc.x = -1
-                state.world.movable_objects[obj_idx].loc.y = -1
-                state.world.movable_objects[obj_idx].loc.grasped = True
-                
-                res.state = state
-                res.motion = 'picked up ' + obj.id + " from " + direction
-                res.success = True
-            else:
-                res.state = state
-                res.motion = ''
-                res.success = False
-            
-        elif action[0] == 'PUTDOWN':
-            object_id = goals.object_id
-            goal_surface_id = goals.surface_id
-            goal_x = goals.x
-            goal_y = goals.y
[…]

### 2015-04-18 scripts/mockPoseGenerator.py

@@ -1,73 +1,0 @@
-#!/usr/bin/python
-
-import rospy
-import roslib
-from task_motion_planner.msg import *
-from random import shuffle
-import numpy
-import re
-
-# TODO: Change to message type instead of dict, also add second action
-
-class MockPoseGenerator:
-    def __init__(self):
-        self.state = dict()
-
-    def next(self, action_tuple):
-        action = action_tuple[0]
-        obj = action_tuple[1]
-
-        msg = pose()
-        msg.object_id = obj
-        
-        # TODO get surface/obj
-        if action_tuple in self.state:
-            # if there are letters left, return it
-            if len(self.state[action_tuple]) > 0:
-                if action == 'PICKUP':
-                    msg.direction = self.state[action_tuple].pop()
-                else:
-                    location = self.state[action_tuple].pop()
-                    msg.x = location[0]
-                    msg.y = location[1]
-                    msg.surface_id = action_tuple[-1]
-                return msg
-            else:
-                return None
-        else:
-            # generate list of poses
-            if action == 'PICKUP':
-                self.state[action_tuple] = ['N','NE','E','SE','S','SW','W','NW']
-                shuffle(self.state[action_tuple])
-                msg.direction = self.state[action_tuple].pop()
-            else:
-                x_poses =  list(xrange(17))
-                y_poses = list(xrange(17))
-                shuffle(x_poses)
-                shuffle(y_poses)
-                self.state[action_tuple]=numpy.transpose([x_poses,y_poses]).tolist()
-                location = self.state[action_tuple].pop()
-                msg.x = location[0]
-                msg.y = location[1]
-                msg.surface_id = action_tuple[-1]
-            # return a pose
-            return msg
-
-    def reset(self, action):
-        if action in self.state:
-            del self.state[action]
-
-    def resetAll(self):
-        for action in self.state.keys():
-            del self.state[action]
-
-if __name__ == "__main__":
-    m = MockPoseGenerator()
-    for i in range(9):
-        print m.next('(PICKUP,1)')
-    for i in range(18):
-        print m.next('(PUTDOWN,1,surface)')
-    m.reset('PICKUP')
-    m.reset('PUTDOWN')
-    print m.next('(PICKUP,1)')
-    print m.next('(PUTDOWN,1,surface)')

### 2015-04-18 scripts/mockStateUpdate.py

@@ -1,57 +1,0 @@
-#!/usr/bin/env python
-
-import sys
-import rospy
-from task_motion_planner.msg import *
-import copy
-
-def mockStateUpdate(state_input, failCause, failStep, prev_fail_step, hlplan, world):
-        # stateUpdate will need to be updated based on the specific problem
-        state = copy.deepcopy(state_input)
-        for i in range(failStep-prev_fail_step):
-            action = hlplan[i+prev_fail_step+1]
-            if action[0] == 'PICKUP':
-                state[1].remove( ('EMPTY', action[2]) )
-                state[1].append( ('NOT', 'EMPTY', action[2]) )
-                state[1].remove( ('ROBOTAT', action[3]) )
-                state[1].append( ('ROBOTAT', action[4]) )
-                state[1].append( ('NOT', 'ROBOTAT', action[3]) )
-                state[1].append( ('IN', action[1], action[2]) )
-                for obj in world.world.movable_objects:
-                    state[1].append( ('NOT', 'OBSTRUCTS', action[1], obj.id) )                    
-                    t = ('OBSTRUCTS', action[1], obj.id)
-                    if t in state[1]:
-                        state[1].remove(t)
-                    for loc in world.world.surfaces:
-                            state[1].append( ('NOT', 'PDOBSTRUCTS', action[1], obj.id, loc.id) )
-                            t = ('PDOBSTRUCTS', action[1], obj.id, loc.id)
-                            if t in state[1]:
-                                    state[1].remove(t)
-                for loc in world.world.surfaces: 
-                    t = ('AT', action[1], loc.id)
-                    if t in state[1]:
-                        state[1].remove(t)
-            if action[0] == 'PUTDOWN':
-                state[1].remove( ('IN', action[1], action[2]) )
-                state[1].append( ('NOT', 'IN', action[1], action[2]) )
-                state[1].append( ('EMPTY', action[2]) )
-                state[1].remove( ('NOT', 'EMPTY', action[2]) )
-                state[1].append( ('AT', action[1], action[5]) )
-                t = ('NOT', 'AT', action[1], action[5])
-                if t in state[1]:
-                    state[1].remove(t)
-                state[1].remove( ('ROBOTAT', action[3]) )
-                state[1].append( ('ROBOTAT', action[4]) )
-
-
-        action = hlplan[failStep+1]
-        if action[0] == 'PICKUP':
-            obj_to_pickup = action[1]
[…]

### 2015-04-18 scripts/motion_planner_server.py

@@ -1,143 +1,0 @@
-#!/usr/bin/env python
-
-import sys
-import rospy
-import re
-import moveit_commander
-from task_motion_planner.srv import *
-from task_motion_planner.msg import *
-from moveit_msgs.msg import *
-from geometry_msgs.msg import *
-from std_msgs.msg import String
-
-
-class MotionPlannerServer(object):
-    def __init__(self, max_planning_time):
-        self.max_planning_time = max_planning_time
-        self.planning_scene_pub = rospy.Publisher('planning_scene', PlanningScene)
-        
-    def get_motion_plan(self, req):
-        print "============ Starting Moveit Commander"
-        moveit_commander.roscpp_initialize(sys.argv)
-        
-        print "============ Setting current state"
-        robot = moveit_commander.RobotCommander()
-        scene = moveit_commander.PlanningSceneInterface()
-        
-        world_start_state = req.parameters.state.world
-        robot_start_state = req.parameters.state.robot
-        print "PREACTION:", req.parameters.action
-        action = re.split(',', req.parameters.action[1:-1])
-        print "ACTION: ", action
-        pose_goals = req.parameters.goals
-        
-        # Set attach/detach point
-        attach_detach_idx = 2
-    
-        # Add objects to planning scene
-        planning_scene = PlanningScene()
-        planning_scene.world = world_start_state
-        planning_scene.is_diff = True
-        
-        self.planning_scene_pub.publish(planning_scene)
-        
-        #for i in range(len(world_start_state.collision_objects)):
-        #    obj = world_start_state.collision_objects[i]
-        #    pose = PoseStamped()
-        #    pose.header = obj.header
-        #    pose.pose = obj.primitive_poses[0]
-        #    h = obj.primitives[0].dimensions[0]
-        #    r = obj.primitives[0].dimensions[1]
-        #    scene.add_box(obj.id, pose, (r, r, h))
-        
-        curr_state = robot_start_state
-        res = motion_plan()
-    
-        print "============ Planning actoin ", action[0]
-        for i in range(len(pose_goals)):
-            print "============ Move group ", action[2]
-            group = moveit_commander.MoveGroupCommander(action[2])
-        
-            group.set_planning_time(self.max_planning_time)
-            group.set_start_state(curr_state)
-            group.set_pose_target(pose_goals[i].pose)
-        
-            plan = group.plan()
-    
-            if len(plan.joint_trajectory.points) > 0:
-                print "============ Component ", i, " of motion plan succeeded"
[…]

### 2015-04-18 scripts/numObstructs.py

@@ -1,158 +1,0 @@
-#!/usr/bin/env python
-
-from task_motion_planner.msg import *
-
-# world is a world msg from generateWorldMsg
-# surface dim --> size of grid (default 17)
-def numObstructsWorld(world, surface_dim):
-    world = world.world
-    
-    surfaces = dict()
-    for surface in world.surfaces:
-        surfaces[surface.id] = [[0 for i in range(surface_dim)] for j in range(surface_dim)]
-    
-    for movable_object in world.movable_objects:
-        surface_id = movable_object.loc.surface_id
-        x = movable_object.loc.x
-        y = movable_object.loc.y
-        grasped = movable_object.loc.grasped
-
-        if not grasped:
-            surfaces[surface_id][y][x] = 1
-            
-    numObs = 0
-    for movable_object in world.movable_objects:
-        numObs += numObstructsObject(movable_object, surface_dim, surfaces)
-            
-    return numObs
-            
-def numObstructsObject(obj, surface_dim, surfaces):
-    numObs = 0
-    numObs += obstructsN(obj, surface_dim, surfaces)
-    numObs += obstructsNE(obj, surface_dim, surfaces)
-    numObs += obstructsE(obj, surface_dim, surfaces)
-    numObs += obstructsSE(obj, surface_dim, surfaces)
-    numObs += obstructsS(obj, surface_dim, surfaces)
-    numObs += obstructsSW(obj, surface_dim, surfaces)
-    numObs += obstructsW(obj, surface_dim, surfaces)
-    numObs += obstructsNW(obj, surface_dim, surfaces)
-    return numObs
-    
-def obstructsN(obj, surface_dim, surfaces):
-    surface_id = obj.loc.surface_id
-    x = obj.loc.x
-    y = obj.loc.y
-    
-    if y == 0 or surfaces[surface_id][y-1][x] == 0:
-        return False
-    else:
-        return True
-    
-def obstructsNE(obj, surface_dim, surfaces):
-    surface_id = obj.loc.surface_id
-    x = obj.loc.x
-    y = obj.loc.y
-    
-    if y == 0:
-        # cell to the right empty
-        if x < surface_dim-1 and surfaces[surface_id][y][x+1] == 0:
-                return False
-        else:
-            return False
-    elif x < surface_dim-1:
-        # above, above & right, right
[…]

### 2015-04-18 scripts/planner_server.py

@@ -1,53 +1,0 @@
-#!/usr/bin/env python
-
-from task_motion_planner.srv import *
-from task_motion_planner.msg import *
-import rospy
-import os
-
-class TaskPlannerServer(object):
-    def __init__(self, path, domain_file):
-        self.path = path
-        self.domain_file = domain_file
-        
-    def handle_pddl(self, req):
-        print "Serving task plan"
-        domain_file = "domain"
-        task_file = req.domain.task_file
-        ff_call = self.path + "./ff -o " + self.domain_file + " -f " + task_file + " > output" 
-        os.system(ff_call)
-
-        msg = hl_plan()
-        msg.error = True
-        actions = False
-
-        f = open('output')
-        s = ""
-        for line in f:
-            if line[0:4]=='step':
-                msg.error = False
-                actions = True
-                s = s + line[11:-1]
-            elif actions == True:
-                if line  == '\n':
-                    actions = False
-                else:
-                    s = s + '\n' + line[11:-1]
-        f.close()
-        msg.plan = s
-        #print "string: ", s
-
-        return msg
-
-    def run(self):
-        rospy.init_node('task_planner_server')
-        s = rospy.Service('task_server_service', task_service, self.handle_pddl)
-        print "Ready to serve task plans"
-        rospy.spin()
-
-if __name__ == "__main__":
-    #task_planner_server = TaskPlannerServer("/home/vmlane/catkin_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/vmlane/catkin_ws/src/6834-task-motion-planner/domain")
-    task_planner_server = TaskPlannerServer("/home/ragtz/Downloads/FF-v2.3/", "/home/ragtz/indigo_workspace/src/6834-task-motion-planner/domain")
-    #task_planner_server = TaskPlannerServer("/home/bhomberg/indigo_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/bhomberg/indigo_ws/src/6834-task-motion-planner/domain")
-    task_planner_server.run()
-    

### 2015-04-18 scripts/pose_generator.py

@@ -1,213 +1,0 @@
-#!/usr/bin/python
-
-import roslib
-import rospy
-from geometry_msgs.msg import *
-from task_motion_planner.msg import *
-import math
-import random
-import copy
-import re
-
-#TODO: right/left arm ---> standard pose is different
-
-# Generates a set of gripper poses given an action and a world description
-# The motion planner verifies that the set of candidate poses is valid 
-# (not obstructed by objects & objects are reachable) 
-class PoseGenerator:
-    def __init__(self, GRIPPER_OFFSET = .015):
-        # the height of the table in world coordinates
-        self.DIST_FROM_CYLINDER = .1
-        self.GRIPPER_OFFSET = GRIPPER_OFFSET
-
-    # Generates a set of gripper poses given an action and a world description
-    # action = a string containing (action, arm, object_name)
-    # world = a WorldState msg
-    def generate(self, action, world):
-        action = re.split(',', action[1:-1])
-        objects = world.world.collision_objects
-        obj = self._search_for_object(action[1], objects)
-        height = obj.primitives[0].dimensions[0]
-        radius = obj.primitives[0].dimensions[1]
-        
-        if action[0] == 'pickup':
-            pose = obj.primitive_poses[0]
-            return self.pickup(pose,height,radius)
-        elif action[0] == 'putdown':
-            table = self._search_for_object(action[-1], objects)
-            return self.putdown(table,height,radius)
-        else:
-            return
-
-    # Generates a set of gripper poses for a pickup action of a cylinder
-    # obj_pose = cylinder pose (position, orientation)
-    # height = cylinder height
-    # radius = cylinder radius
-    # return =  an array of 5 pose_gen messages each containing a pose and a
-    #           boolean - true if the gripper is open, false if closed
-    #           poses = stage, pre-grasp, grasp, lifted, standard pose
-    def pickup(self, obj_pose, height, radius):
-        CLEARANCE_HEIGHT = obj_pose.position.z + height
-        
-        # radius of circle around the cylinder where the gripper origin will lie
-        r = radius + self.DIST_FROM_CYLINDER
-        # height of gripper when grasping cylinder
-        z =  obj_pose.position.z
-
[…]

### 2015-04-18 scripts/pose_generator_motion_planner_test.py

@@ -1,140 +1,0 @@
-#!/usr/bin/env python
-
-import sys
-import rospy
-from task_motion_planner.srv import *
-from task_motion_planner.msg import *
-from pose_generator import *
-from std_msgs.msg import *
-from moveit_msgs.msg import *
-from shape_msgs.msg import *
-from geometry_msgs.msg import *
-from sensor_msgs.msg import *
-
-def pickupTest(action, motion_server, poseGen):
-    state = world_state()
-    state.world = PlanningSceneWorld()
-    
-    surf1 = CollisionObject()
-    surf1.header = Header()
-    surf1.header.frame_id = '1'
-    surf1.id = 'surf1'
-    primitive = SolidPrimitive()
-    primitive.type = 1
-    primitive.dimensions = [1, 1, 0.05]
-    surf1.primitives.append(primitive)
-    pose = Pose()
-    pose.position.x = 1
-    pose.position.y = 0
-    pose.position.z = 0
-    pose.orientation.w = 1
-    surf1.primitive_poses.append(pose)
-    state.world.collision_objects.append(surf1)
-    
-    obj1 = CollisionObject()
-    obj1.header = Header()
-    obj1.header.frame_id = '1'
-    obj1.id = 'obj1'
-    primitive = SolidPrimitive()
-    primitive.type = 3
-    primitive.dimensions = [.25, .02]
-    obj1.primitives.append(primitive)
-    pose = Pose()
-    pose.position.x = 0.9
-    pose.position.y = -.15
-    pose.position.z = 0.16
-    pose.orientation.w = 1
-    obj1.primitive_poses.append(pose)
-    state.world.collision_objects.append(obj1)
-
-    state.robot = RobotState()
-    state.robot.joint_state.name = ['head_pan', 'left_e0', 'left_e1', 'left_s0', 'left_s1', 'left_w0', 'left_w1', 'left_w2', 'right_e0', 'right_e1', 'right_s0', 'right_s1', 'right_w0', 'right_w1', 'right_w2']
-    state.robot.joint_state.position = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
-    state.robot.joint_state.velocity = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
-    state.robot.joint_state.effort = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
-
[…]

### 2015-04-18 scripts/small_tests.py

@@ -1,94 +1,0 @@
-#!/usr/bin/env python
-
-import time
-import sys
-import rospy
-from task_motion_planner.srv import *
-from task_motion_planner.msg import *
-from moveit_msgs.msg import *
-from geometry_msgs.msg import *
-import copy
-import itertools
-from random import shuffle
-from mockPoseGenerator import *
-from mockMotionPlanner import *
-from mockStateUpdate import *
-from interface_layer_organized import *
-from planner_server import *
-from generateWorldMsg import *
-from numObstructs import *
-import re
-from stateGeneratorSmall import *
-from generateSmallWorldMsg import *
-
-# rosrun mock motion planner srv
-# rosrun mock task planner srv
-
-numTests = 10
-
-genState =  StateGeneratorSmall()
-
-DIR_6834 = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
-
-# One Cover Bechmark
-out_file = open('smallTests.output','w')
-
-# set up the world
-worlds = generateWorlds()
-genState.generateStates()
-
-for filename,world in worlds.iteritems():
-	print world
-	
-	filepath = DIR_6834+"states/" + filename		
-	f = open(filepath,'r')
-	init_state_string = f.read()
-	state = [[]]*3
-	l = init_state_string.split('\n')
-	state[0] = l[0].split(',')
-	k = l[1].split(',')
-	state[1] = [tuple(i.split(' ')) for i in k]
-	k = l[2].split(',')
-	state[2] = [tuple(i.split(' ')) for i in k]
-	pose = l[3]
-
-	# Difficulty Metric
-	numBlocks = len(world.world.movable_objects)
-	numObs = numObstructsWorld(world, 17)
-
-	numMotionPlannerCalls = []
-	numTaskPlannerCalls = []
-	runTimes = []
-
-	fname=DIR_6834+"outputResults/"+filename+".output"
-	outFile = open(fname,'w')
-	# run multiple tests for this world
-	for i in range(numTests):
-		poseGen = MockPoseGenerator()
-		interfaceLayer = InterfaceLayer('task_server_service', 'motion_server_service', poseGen, mockStateUpdate, DIR_6834)
-		tic = time.time()
-		ret = interfaceLayer.run(state, world, pose)
-		runTime = time.time() - tic
[…]

### 2015-04-18 scripts/stateGenerator.py

@@ -1,82 +1,0 @@
-#!/usr/bin/python
-
-import sys
-
-# The number of blocks (including block 0)
-# set by command line args
-
-
-# Concatenate substrings & add numbers between them, do this for the number of blocks
-# strs = substrings to concatenate (with number between each substring)
-# the final character of the return strign
-# whether or not to add a number after the last substring
-# the block # to start at
-class StateGenerator:
-	def __init__(self):
-		self.NUMBLOCKS = 10
-
-	def concatMult(self,strs,last,end=False,start=0):
-		s = ''
-		r = len(strs) if end else len(strs)-1 
-		for i in range(start, self.NUMBLOCKS):
-			for x in range(r):
-				s += strs[x]+str(i)
-			if r < len(strs):
-				s += strs[-1]
-			if not i == self.NUMBLOCKS-1:
-				s += ","
-		s += last
-		return s
-
-	def generateString(self):
-		s = ''
-		# environment
-		s += self.concatMult(["BLOCK"," - physob"],",")
-		s += "LEFTARM - gripper,"
-		s += self.concatMult(["GP_BLOCK"," - pose"],",")
-		s += self.concatMult(["PDP_BLOCK","_S - pose"],",")
-		s += self.concatMult(["PDP_BLOCK","_I - pose"],",")
-		s += "INITPOSE - pose,"
-		s += "S - location,"
-		s += "I - location\n"
-		# initial conditions
-		s += "ROBOTAT INITPOSE,EMPTY LEFTARM,"
-		s += self.concatMult(["ISGPFG GP_BLOCK", " BLOCK"],",",True)
-		s += self.concatMult(["ISGPFPD PDP_BLOCK","_S BLOCK", " S"],",")
-		s += self.concatMult(["ISGPFPD PDP_BLOCK","_I BLOCK", " I"],",")
-		s += self.concatMult(["ISLFPD S BLOCK"],",",True)
-		s += self.concatMult(["ISLFPD I BLOCK"],",",True)
-		s += self.concatMult(["AT BLOCK", " I"],"\n")
-		# goal
-		s += "AT BLOCK0 S\n"
-		# initial pose
-		s += "INITPOSE"
-
-		return s
-
-	def generateFile(self,filename):
-		s = self.generateString()
-		f = open(filename, 'w')
-		f.write(s)
-		f.close()
-
-	def genStateFromWorld(self,world,filename):
[…]

### 2015-04-18 scripts/stateGeneratorSmall.py

@@ -1,132 +1,0 @@
-#!/usr/bin/python
-
-DIR = '../states/'
-
-class StateGeneratorSmall:
-	def __init__(self):
-		self.NUMBLOCKS = 10
-
-	# Concatenate substrings & add numbers between them, do this for the number of blocks
-	# strs = substrings to concatenate (with number between each substring)
-	# the final character of the return strign
-	# whether or not to add a number after the last substring
-	# the block # to start at
-	def concatMult(self,strs,last,end=False,start=0):
-		s = ''
-		r = len(strs) if end else len(strs)-1 
-		for i in range(start, self.NUMBLOCKS):
-			for x in range(r):
-				s += strs[x]+str(i)
-			if r < len(strs):
-				s += strs[-1]
-			if not i == self.NUMBLOCKS-1:
-				s += ","
-		s += last
-		return s
-
-	def generateString(self, surface_ids, initialPoses, goals):
-		s = ''
-		# environment
-		s += self.concatMult(["BLOCK"," - physob"],",")
-		s += "LEFTARM - gripper,"
-		s += self.concatMult(["GP_BLOCK"," - pose"],",")
-		for s_id in surface_ids:
-			s2 = "_" + s_id + " - pose"
-			s += self.concatMult(["PDP_BLOCK",s2],",")
-		s += "INITPOSE - pose,"
-
-		for i in range(len(surface_ids)):
-			s += surface_ids[i] + " - location"
-			if i < len(surface_ids) - 1:
-				s += ","
-			else:
-				s += "\n"
-		
-		# initial conditions
-		s += "ROBOTAT INITPOSE,EMPTY LEFTARM,"
-		s += self.concatMult(["ISGPFG GP_BLOCK", " BLOCK"],",",True)
-		for s_id in surface_ids:
-			middle = "_" + s_id + " BLOCK"
-			end = " " + s_id
-			s += self.concatMult(["ISGPFPD PDP_BLOCK",middle, end],",")
-		for s_id in surface_ids:
-			s2 = "ISLFPD " + s_id + " BLOCK"
-			s += self.concatMult([s2],",",True)
-		# initial block locations
-		for block in initialPoses:
-			s += "AT " + block[0] + " " + block[1] + ","
[…]

### 2015-04-18 scripts/stateupdate.py

@@ -1,53 +1,0 @@
-    def stateUpdate(self, state, failCause, failStep, hlplan, world):
-        # stateUpdate will need to be updated based on the specific problem
-        # currently set up for mocks
-        for i in range(failStep):
-            action = hlplan[i]
-            if action[0] == 'PICKUP':
-                state[1].remove( ('EMPTY', action[2]) )
-                state[1].append( ('NOT', 'EMPTY', action[2]) )
-                state[1].remove( ('ROBOTAT', action[3]) )
-                state[1].append( ('ROBOTAT', action[4]) )
-                state[1].append( ('NOT', 'ROBOTAT', action[3]) )
-                state[1].append( ('IN', action[1], action[2]) )
-                for obj in world.movable_objects:
-                    state[1].append( ('NOT', 'OBSTRUCTS', action[1], obj.id) )
-                    state[1].append( ('NOT', 'PDOBSTRUCTS', action[1], obj.id, 'S') ) # MOCK
-                    t = ('OBSTRUCTS', action[1], obj.id)
-                    if t in state[1]:
-                        state[1].remove(t)
-                    t = ('PDOBSTRUCTS', action[1], obj.id, 'S') # MOCK
-                    if t in state[1]:
-                        state[1].remove(t)
-                for loc in world.surfaces:
-                    t = ('AT', action[1], loc.id)
-                    if t in state[1]:
-                        state[1].remove(t)
-            if action[0] == 'PUTDOWN':
-                state[1].remove( ('IN', action[1], action[2]) )
-                state[1].append( ('NOT', 'IN', action[1], action[2]) )
-                state[1].append( ('EMPTY', action[2]) )
-                state[1].remove( ('NOT', 'EMPTY', action[2]) )
-                state[1].append( ('AT', action[1], action[5]) )
-                t = ('NOT', 'AT', action[1], action[5])
-                if t in state[1]:
-                    state[1].remove(t)
-                state[1].remove( ('ROBOTAT', action[3]) )
-                state[1].append( ('ROBOTAT', action[4]) )
-
-
-        action = hlplan[failStep]
-        if action[0] == 'PICKUP':
-            obj_to_pickup = action[1]
-            for obj in failCause:
-                state[1].append( ('OBSTRUCTS', obj, obj_to_pickup))
-                print "ADDED STATE (pickup): ", state[1][-1]
-                print state[1]
-        elif action[0] == 'PUTDOWN':
-            obj_to_putdown = action[1]
[…]

### 2015-04-18 src/motion_planner_server.cpp

@@ -1,104 +1,0 @@
-#include <ros/ros.h>
-
-#include <task_motion_planner/motion_service.h>
-#include <task_motion_planner/motion_plan_parameters.h>
-#include <task_motion_planner/motion_plan.h>
-
-#include <moveit/move_group_interface/move_group.h>
-#include <moveit/planning_scene_interface/planning_scene_interface.h>
-
-bool get_motion_plan(task_motion_planner::motion_service::Request &req, task_motion_planner::motion_service::Response &res) {
-    ROS_INFO("Setting current state");
-    moveit::planning_interface::PlanningSceneInterface planning_scene_interface;  
-    planning_scene_interface.addCollisionObjects(req.parameters.world.collision_objects);
-
-    moveit_msgs::RobotState curr_state = req.parameters.start;
-
-    for (int i = 0; i < req.parameters.group_names.size(); i++) {
-        ROS_INFO("Move group %s", req.parameters.group_names[i].c_str());
-        moveit::planning_interface::MoveGroup group(req.parameters.group_names[i]);
-    
-        group.setPlanningTime(5.0);
-        group.setStartState(curr_state);
-        group.setJointValueTarget(req.parameters.goals[i]);
-    
-        moveit::planning_interface::MoveGroup::Plan plan;
-        bool success = group.plan(plan);
-    
-        if (success) {
-            ROS_INFO("Motion plan succeeded");
-            res.plan.trajectory.trajectory_start = plan.start_state_;
-            res.plan.trajectory.trajectory.push_back(plan.trajectory_);
-        
-            // Determine new state after execution of plan
-            sensor_msgs::JointState joint_state;
-            sensor_msgs::MultiDOFJointState multi_dof_joint_state;
-            
-            // Extract last joint trajectory in the robot trajectory
-            trajectory_msgs::JointTrajectory last_joint_step = res.plan.trajectory.trajectory.back().joint_trajectory;
-            trajectory_msgs::MultiDOFJointTrajectory last_multi_dof_joint_step = res.plan.trajectory.trajectory.back().multi_dof_joint_trajectory;
-            
-            // Extract last position of each joint in the joint trajectories
-            joint_state.name = last_joint_step.joint_names;
-            for (int j = 0; j < joint_state.name.size(); j++) {
-                joint_state.position.push_back(last_joint_step.points[j].positions.back());
[…]

### 2015-04-18 documentation/draft.tex
added original algorithm results
added text to benchmarking section

--- 2015-04-18 documentation/draft.tex
@@
 We tested a variety of different grid shapes, including a square grid, an X, a cross, and lines. 
-We tested each grid shape over a range of sizes ranging from 3 to 13.
-ref{fig-benchmarks} The most difficult benchmark we tested was the 13x13 square grid.
-Larger tests caused the FF planner to segfault.
-The interface layer is designed to be independent of any specific task and motion planner libraries, therefore number of calls to the motion and task planner measures the performance of the interface layer.
+We tested each grid shape over a range of sizes ranging from 3 to 13. ref{fig-benchmarks} 
+The most difficult benchmark we tested was the 13x13 square grid. Larger tests caused the FF planner to segfault.
+
+Figure \ref{benchmark2} shows the results for the original algorithm, minus our modification.
+(Our modification always tries to find a perfect plan after adding a new high level plan section to the plan, rather than immediately trying to find a new partial trajectory.)  For the very simplest cases, the original algorithm performs better, since it makes the same number of motion and task planner calls but has less backtracking overhead.
+However, for the more complicated environments, the cross and the square, our algorithm was significantly faster, as shown in \ref{benchmark}.
+
+The interface layer is designed to be independent of any specific task and motion planner libraries, therefore number of calls to the motion and task planner measures the performance of the interface layer better than the total runtime, since the actual runtime will be very dependent on the motion planner and task planner chosen.
 
@@
 \end {tabular}
-\caption{Benchmark Tests}
+\caption{Benchmark Tests - Our Modified Algorithm}
 \label{benchmark}
+\end{figure}
+
+\begin{figure}
+\begin{tabular}[t]{|l|l|l|l|l|l|}
+\hline
+Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
+Horizontal Line & 3 & 12 & 3 & 1 & .016\\
+& 9 & 48 & 4 & 1 & .025\\
+& 13 & 72 & 4 & 1 & .033\\
+\hline
+Vertical Line & 3 & 12 & 4 & 1 & .022\\
+& 9 & 48 & 4 & 1 & .027\\
+& 13 & 72 & 4 & 1 & .031\\ 
+\hline
+X & 5 & 8 & 2 & 1 & .014\\
+& 17 & 32 & 2 & 1 & .031\\
+& 25 & 48 & 2 & 1 & .056\\ 
+\hline
+Cross & 5 & 20 & 47 & 5 & .15\\
+& 17 & 92 & 206 & 10 & .68\\
+& 25 & 140 & 390 & 14 & 1.56\\ 
+\hline
+Square & 9 & 56 & 145 & 11 & .45\\
+& 25 & 176 & 4354 & 143 & 16.55\\
+
+\hline
+
+\end {tabular}
+\caption{Benchmark Tests - Original Algorithm}
+\label{benchmark2}
 \end{figure}
@@
 If the motion planner and task planner are not efficient, the interface layer will not produce answers quickly.  
+In particular, the number of calls to the motion planner is very large in order to gather the environmental information needed to pass on to the task planner.  
+So in particular, the running time of this algorithm will depend on the running time of the motion planner.
 

### 2015-04-18 documentation/draft.tex
added algorithm figures

--- 2015-04-18 documentation/draft.tex
@@
 \usepackage{svg}
+\usepackage{caption}
+\usepackage{subfig}
 
@@
 
-Insert the figure 4 from the paper!
+\begin{figure}[t]
+\centering
+\includegraphics[width=\textwidth]{figures/figure4.png}
+\caption{Illustration of the interface layer’s refinement process. Action arguments have been abbreviated. [1]
+\label{fig:figure4}}
+\end{figure}
 
-This figure, included with text from [1], explains the flow of control of the interface layer through a variety of situations, including more than the simple case covers.  
+This figure (Fig. \ref{fig:figure4}), included with text from [1], explains the flow of control of the interface layer through a variety of situations, including more than the simple case covers.  
 The subfigures in this diagram explain on a high level the different steps the interface layer takes when solving a problem.  
@@
 
-\subsubsection{Algorithm Improvements}
-
-The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.
-Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.
-In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the high level plan more complicated.
-In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.
-An analysis of the benefits of this approach are outlined in the benchmarking section.
-
 \subsubsection{Algorithm 1}
 
-Include algorithm block 1 from paper
+\begin{figure}[t]
+	\centering
+	\subfloat{\includegraphics[width=.45\linewidth]{figures/algorithm1}}
+	\qquad
+	\subfloat{\includegraphics[width=.45\linewidth]{figures/algorithm2}}
+	\caption{Taken from[1]\label{fig:algorithms}}
+\end{figure}
 
@@
 The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.
-For our version of the algorithm, every time a new partial plan is generated, we first try to fill it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.
+Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.
+In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the plan more complicated.
+In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.
+An analysis of the benefits of this approach are outlined in the benchmarking section.
 
@@
 Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
-Horizontal Line & 3 & 12 & 3 & 1 & .023\\
-& 5 & 24 & 4 & 1 & .028\\
-& 7 & 36 & 4 & 1 & .029\\
-& 9 & 48 & 4 & 1 & .029\\
-& 11 & 60 & 4 & 1 & .034\\
-& 13 & 72 & 4 & 1 & .037\\
+Horizontal Line & 3 & ? & ? & ? & ?\\
+& 5 & ? & ? & ? & ?\\
+& 7 & ? & ? & ? & ?\\
+& 9 & ? & ? & ? & ?\\
+& 11 & ? & ? & ? & ?\\
+& 13 & ? & ? & ? & ?\\
 \hline
-Vertical Line & 3 & 12 & 4 & 1 & .024\\
-& 5 & 24 & 4 & 1 & .027\\
-& 7 & 36 & 4 & 1 & .028\\
-& 9 & 48 & 4 & 1 & .028\\
-& 11 & 60 & 4 & 1 & .037\\
-& 13 & 72 & 4 & 1 & .036\\ 
+Vertical lLne & 3 & ? & ? & ? & ?\\
+& 5 & ? & ? & ? & ?\\
+& 7 & ? & ? & ? & ?\\
+& 9 & ? & ? & ? & ?\\
+& 11 & ? & ? & ? & ?\\
+& 13 & ? & ? & ? & ?\\ 
 \hline
-X & 5 & 8 & 2 & 1 & .026\\
-& 9 & 16 & 2 & 1 & .034\\
-& 13 & 24 & 2 & 1 & .036\\
-& 17 & 32 & 2 & 1 & .047\\
-& 21 & 40 & 2 & 1 & .066\\
-& 25 & 48 & 2 & 1 & .079\\ 
+X & 5 & ? & ? & ? & ?\\
+& 9 & ? & ? & ? & ?\\
+& 13 & ? & ? & ? & ?\\
+& 17 & ? & ? & ? & ?\\
+& 21 & ? & ? & ? & ?\\
+& 25 & ? & ? & ? & ?\\ 
 \hline
-Cross & 5 & 20 & 39 & 3 & .16\\
-& 9 & 44 & 50 & 2 & .20\\
-& 13 & 68 & 59 & 2 & .23\\
-& 17 & 92 & 71 & 3 & .26\\
-& 21 & 116 & 78 & 3 & .31\\
-& 25 & 140 & 77 & 3 & .39\\ 
+Cross & 5 & ? & ? & ? & ?\\
+& 9 & ? & ? & ? & ?\\
+& 13 & ? & ? & ? & ?\\
+& 17 & ? & ? & ? & ?\\
+& 21 & ? & ? & ? & ?\\
+& 25 & ? & ? & ? & ?\\ 
 \hline
-Square & 9 & 56 & 54 & 2 & .16\\
-& 25 & 176 & 294 & 6 & 1.06\\
-& 49 & 360 & 818 & 10 & 5.07\\
-& 81 & 608 & 3177 & 24 & 34.68\\
-& 121 & 920 & 3681 & 22 & 87.06\\
-& 169 & 1296 & 14216 & 57 & 518.61\\ 
+Square & 9 & ? & ? & ? & ?\\
+& 25 & ? & ? & ? & ?\\
+& 49 & ? & ? & ? & ?\\
+& 81 & ? & ? & ? & ?\\
+& 121 & ? & ? & ? & ?\\
+& 169 & ? & ? & ? & ?\\ 
 \hline

### 2015-04-18 documentation/draft.tex

--- 2015-04-18 documentation/draft.tex
@@
 \usepackage{enumerate}
+\usepackage{svg}
+\usepackage{caption}
+\usepackage{subfig}
 
@@
 
-Include algorithm block 1 from paper
+\begin{figure}[t]
+	\centering
+	\subfloat{\includegraphics[width=.45\linewidth]{figures/algorithm1}}
+	\qquad
+	\subfloat{\includegraphics[width=.45\linewidth]{figures/algorithm2}}
+	\caption{Taken from[1]\label{fig:algorithms}}
+\end{figure}
 

### 2015-04-18 documentation/draft.tex
readded figures that were accidentally deleted

@@
 
-The interface layer starts by asking the task planner to generate a high level plan and has the motion planner instaniate motion plans corresponding to each action.  
+The interface layer starts by asking the task planner to generate a high level plan and has the motion planner instantiate motion plans corresponding to each action.  
 When it's not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner.  
@@
 If still no feasible motion plan is found, backtracking is required.  
-If a feasible motion plan is found with some subset of objects removed, then that information is relayed back to the task planner after the PDDL state is appropriatedly updated.
+If a feasible motion plan is found with some subset of objects removed, then that information is relayed back to the task planner after the PDDL state is appropriately updated.
 This update adds predicates corresponding to the object obstructions, and the task planner is asked to replan starting from the step where we failed to find a motion plan.
@@
 
-Consider the environment in FIGURE.  ***** include Fig 2 from the paper
+\begin{figure}[t]
+\centering
+\def\svgwidth{0.5\textwidth}
+\input{figures/smallEnv.pdf_tex}
+\caption{Small Environment Test Example. The goal was for the blue blocks to be on surface I and the red blocks to be on surface S.\label{fig:smallEnv}}
+\end{figure}
 
@@
 \includegraphics[width=\textwidth]{figures/figure4.png}
-\caption{Illustration of the interface layer’s refinement process. Action arguments have been abbreviated. [1]
+\caption{Illustration of the interface layer’s refinement process. Action arguments have been abbreviated. Taken from [1]
 \label{fig:figure4}}
@@
 
+\begin{figure}[t]
+\centering
+\def\svgwidth{\textwidth}
+\input{figures/benchmarks.pdf_tex}
+\caption{Benchmarking Test Examples. The goal was to move the green block to another surface.\label{fig:benchmark}}
+
+\end{figure}
 \subsection{Testing}
@@
 ref{fig-smallTest} Each test had three to four blocks initially placed on one or two surfaces.
-Some blocks were surrounded by three walls, and others were surrounded by 3 walls.
-This required the interface layer to find the pose that picked up the block in the correct location.
-Furthermore, some blocks which needed to be moved in order to achieve the goal were obstructed by other blocks, meaning that the other block had to be moved first.
+Some blocks were surrounded on 3 sides and others on all sides by walls and blocks.
+For blocks surrounded on 3 sides, the interface layer had to find the pose that picked up the block in the correct direction.
+For blocks surrounded on all sides, the interface layer needed to generate actions to move blocks in the way.
 

### 2015-04-18 documentation/draft.tex
made a few minor modifications
added walkthrough figure

@@
 \def\svgwidth{0.5\textwidth}
-\input{figures/smallEnv.pdf_tex}
-\caption{Small Environment Test Example. The goal was for the blue blocks to be on surface I and the red blocks to be on surface S.\label{fig:smallEnv}}
+\input{figures/walkthrough.pdf_tex}
+\caption{Walkthrough Example. The goal was for the red block to be on surface S.\label{fig:walkthrough}}
 \end{figure}
@@
 
-include algorithm block 2 from paper!  go with the one from the short version of the paper, since it's the version we're actually going with.  the algorithm block is shorter too
-
 In the TryRefine subroutine, the interface layer attempts to find motion plans corresponding to the various actions.  
@@
 \section{Benchmarking}
+\subsection{Testing}
+\begin{figure}[t]
+\centering
+\def\svgwidth{0.5\textwidth}
+\input{figures/smallEnv.pdf_tex}
+\caption{Small Environment Test Example. The goal was for the blue blocks to be on surface I and the red blocks to be on surface S.\label{fig:smallEnv}}
+\end{figure}
+We generated a set of small-scale tests to check the correctness of the interface layer.
+ref{fig-smallTest} Each test had three to four blocks initially placed on one or two surfaces.
+Some blocks were surrounded on 3 sides and others on all sides by walls and blocks.
+For blocks surrounded on 3 sides, the interface layer had to find the pose that picked up the block in the correct direction.
+For blocks surrounded on all sides, the interface layer needed to generate actions to move blocks in the way.
 
+\subsection{Procedure}
 \begin{figure}[t]
@@
 \end{figure}
-\subsection{Testing}
-We generated a set of small-scale tests to check the correctness of the interface layer.
-ref{fig-smallTest} Each test had three to four blocks initially placed on one or two surfaces.
-Some blocks were surrounded on 3 sides and others on all sides by walls and blocks.
-For blocks surrounded on 3 sides, the interface layer had to find the pose that picked up the block in the correct direction.
-For blocks surrounded on all sides, the interface layer needed to generate actions to move blocks in the way.
-
-\subsection{Procedure}
 

### 2015-04-18 documentation/draft.tex
added figure references

@@
 
-The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.
+The original version of the algorithm, as shown in \ref{fig:algorithms}, only attempts to find partial trajectories when it replans partway through the procedure.
 Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.
@@
 
-The original version of the algorithm, as shown in FIGURE, only attempts to find partial trajectories when it replans partway through the procedure.
+The original version of the algorithm, as shown in \ref{fig:algorithms}, only attempts to find partial trajectories when it replans partway through the procedure.
 For our version of the algorithm, every time a new partial plan is generated, we first try to fill it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.

### 2015-04-18 documentation/draft.tex

@@
 However, the number of required discretizations to solve the problem is generally very large and results in extremely large or infeasible problems. 
-The interface allows the task planner state space to use an abstract state space which ignores geometry. 
+An interface allows the task planner state space to use an abstract state space which ignores geometry. 
 The interface layer translates geometric constraints and passes them to the task planner.
@@
 
-In robotics, it is often necessary to create a plan for a series of motions of the robot in order to complete some high level plan.
+In robotics, it is often necessary to create a plan for a series of motions of the robot in order to achieve some high level objective.
 In order to find a task plan which is actually feasible, the task planner must have some knowledge of the geometry of the world.
-Without knowledge of the actual spatial configurations of objects in the world, the task planner would create plans where some actions cannot be completed, due to infeasible motion plans from blocking objects or interference between the robot and the environment.
+Without knowledge of the actual spatial configurations of objects in the world, the task planner would create plans that could not complete some actions, due to infeasible motion plans from blocking objects or interference between the robot and the environment.
 
 The high level problem this implementation addresses is to create a combined task and motion planner, following that presented in [1].  
-This approach allows the motion planner to give information to the task planner and allows us to keep the continuous variables continuous, rather than discretizing.  
+This approach allows the motion planner to give information to the task planner and keeps continuous variables continuous, rather than discretizing.  
 This prevents a combinatorial explosion of the state space that the task planner needs to search over.

### 2015-04-18 benchmarks/benchmark.py
Path issue resolved

@@ -1,12 +1,12 @@
 #!/usr/bin/env python
 
 import time
+import os
 import sys
+sys.path.append(os.path.abspath(os.path.dirname(__file__) + '/../src/'))
 import rospy
 from task_motion_planner.srv import *
 from task_motion_planner.msg import *
-from moveit_msgs.msg import *
-from geometry_msgs.msg import *
 import copy
 import itertools
 from random import shuffle
@@ -29,7 +29,7 @@ numTests = 10
 genWorld = generateWorldMsg()
 genState = StateGenerator()
 
-DIR_6834 = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
+DIR_6834 = '/home/ragtz/indigo_workspace/src/6834-task-motion-planner/'
 
 # One Cover Bechmark
 out_file = open('benchmark.output','w')

### 2015-04-18 src/full_test.py

@@ -1,41 +1,0 @@
-#!/usr/bin/env python
-
-from mockPoseGenerator import *
-from mockMotionPlanner import *
-import mockStateUpdate
-from interface_layer_organized import *
-from planner_server import *
-from generateWorldMsg import *
-
-DIR = '/home/vmlane/catkin_workspace/src/6834-task-motion-planner/'
-
-if __name__ == '__main__':
-
-    genWorld = generateWorldMsg()
-    
-    f = open(DIR+'states/one_cover','r')
-    init_state_string = f.read()
-    
-    state = [[]]*3
-    l = init_state_string.split('\n')
-    state[0] = l[0].split(',')
-    k = l[1].split(',')
-    state[1] = [i.split(' ') for i in k]
-    k = l[2].split(',')
-    state[2] = [i.split(' ') for i in k]
-    pose = l[3]
-
-    world = genWorld.generateWorld('SQUARE',3)
-
-    #task_planner_server = TaskPlannerServer(DIR+"/FF-v2.3/", DIR+"/domain")
-    #task_planner_server.run()
-    #motion_planner_server = MockMotionPlannerServer(17)
-    #motion_planner_server.run()
-    interfaceLayer = InterfaceLayer('task_server_service', 'motion_server_service', MockPoseGenerator, mockStateUpdate, DIR)
-    (hlplan, traj) = interfaceLayer.run(state, world, pose)
-    
-
-    print "\n\n\n OUTPUT FROM INTERFACE LAYER\n\n"
-    print hlplan
-    print traj
-

### 2015-04-18 src/interface_layer_organized.py

@@ -4,8 +4,6 @@ import sys
 import rospy
 from task_motion_planner.srv import *
 from task_motion_planner.msg import *
-from moveit_msgs.msg import *
-from geometry_msgs.msg import *
 import copy
 import itertools
 from random import shuffle

### 2015-04-18 src/server_tests.py

@@ -1,61 +1,0 @@
-#!/usr/bin/env python
-
-import sys
-import rospy
-from task_motion_planner.srv import *
-from task_motion_planner.msg import *
-from moveit_msgs.msg import *
-from geometry_msgs.msg import *
-
-def task_planner_client():
-    rospy.wait_for_service('task_server_service')
-    try:
-        task_server = rospy.ServiceProxy('task_server_service', task_service)
-        msg = task_domain()
-        msg.task_file = 'problem0'
-        resp = task_server(msg)
-        return resp.plan.error, resp.plan.plan
-    except rospy.ServiceException, e:
-        print "Service call failed: %s"%e
-        
-def motion_planner_client():
-    rospy.wait_for_service('motion_server_service')
-    try:
-        motion_server = rospy.ServiceProxy('motion_server_service', motion_service)
-        
-        msg = motion_plan_parameters()
-        
-        state = world_state()
-        state.world = PlanningSceneWorld()
-        state.robot = RobotState()
-        state.robot.joint_state.name = ['head_pan', 'left_e0', 'left_e1', 'left_s0', 'left_s1', 'left_w0', 'left_w1', 'left_w2', 'right_e0', 'right_e1', 'right_s0', 'right_s1', 'right_w0', 'right_w1', 'right_w2']
-        state.robot.joint_state.position = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
-        state.robot.joint_state.velocity = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
-        state.robot.joint_state.effort = [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]
-        msg.state = state
-        
-        msg.action = '(pickUp,left_arm,obj1)'
-        
-        msg.goals = [pose_gen()]
-        msg.goals[0].pose.position.x = 1.01273449356#0.74
-        msg.goals[0].pose.position.y = 0.278176133738#0.28
-        msg.goals[0].pose.position.z = 0.48067864592#0.34
-        msg.goals[0].pose.orientation.x = 0.0930396724127#0
-        msg.goals[0].pose.orientation.y = 0.701064150913#0
-        msg.goals[0].pose.orientation.z = -0.0989183493556#0
-        msg.goals[0].pose.orientation.w = 0.700048452482#1
-        
-        msg.goals[0].gripperOpen = True
-        
[…]

### 2015-04-18 src/simple_example.py

@@ -1,17 +1,0 @@
-#!/usr/bin/env python
-
-from mockPoseGenerator import *
-from mockStateUpdate import *
-from interface_layer import *
-
-if __name__ == "__main__":
-    state = None
-    world = None
-    pose = None
-
-    interfaceLayer = InterfaceLayer('task_server_service', 'motion_server_service', MockPoseGenerator, mockStateUpdate)
-    (hlplan, traj) = interfaceLayer.run(state, world, pose)
-    
-    print hlplan
-    print traj
-    

### 2015-04-18 src/stateGeneratorSmall.py

@@ -1,6 +1,8 @@
 #!/usr/bin/python
 
-DIR = '../states/'
+import os
+
+DIR = os.path.abspath(os.path.dirname(__file__) + '/../states/') + '/'
 
 class StateGeneratorSmall:
 	def __init__(self):

### 2015-04-18 tests/small_tests.py

@@ -2,11 +2,11 @@
 
 import time
 import sys
+import os
+sys.path.append(os.path.abspath(os.path.dirname(__file__) + '/../src/'))
 import rospy
 from task_motion_planner.srv import *
 from task_motion_planner.msg import *
-from moveit_msgs.msg import *
-from geometry_msgs.msg import *
 import copy
 import itertools
 from random import shuffle
@@ -28,7 +28,7 @@ numTests = 10
 
 genState =  StateGeneratorSmall()
 
-DIR_6834 = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
+DIR_6834 = '/home/ragtz/indigo_workspace/src/6834-task-motion-planner/'
 
 # One Cover Bechmark
 out_file = open('smallTests.output','w')

### 2015-04-18 documentation/draft.tex
added emails to draft, fixed grammar, added pdf

@@
 \title{Combined Task and Motion Planner through an Interface Layer}
-\author{Alex Gutierrez, Bianca Homberg, and Veronica Lane}
+\author{Alex Gutierrez (ragtz@mit.edu), Bianca Homberg (bhomberg@mit.edu), and Veronica Lane (vmlane@mit.edu)}
 
@@
 \input{figures/walkthrough.pdf_tex}
-\caption{Walkthrough Example. The goal was for the red block to be on surface S.\label{fig:walkthrough}}
+\caption{Walkthrough Example. The goal is for the red block to be on surface S.\label{fig:walkthrough}}
 \end{figure}
@@
 
-The original version of the algorithm, as shown in \ref{fig:algorithms}, only attempts to find partial trajectories when it replans partway through the procedure.
-Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.
-In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the high level plan more complicated.
+The original version of the algorithm, as shown in (Fig.
+\ref{fig:algorithms}), only attempts to find partial trajectories when it replans partway through the procedure.
+Our algorithm has a slight modification.
+Every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.
+In some scenarios, some poses will not work but others will, so it is better to try to make the simplest possible plan work before giving up and making the high level plan more complicated.
 In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.

### 2015-04-18 benchmarks/benchmark.py
Removed need to change paths in files

@@ -29,10 +29,10 @@ numTests = 10
 genWorld = generateWorldMsg()
 genState = StateGenerator()
 
-DIR_6834 = '/home/ragtz/indigo_workspace/src/6834-task-motion-planner/'
+DIR_6834 = os.path.abspath(os.path.dirname(__file__) + '/../') + '/'
 
 # One Cover Bechmark
-out_file = open('benchmark.output','w')
+out_file = open(DIR_6834 + 'benchmarks/benchmark.output','w')
 world_shapes = ["SQUARE","CROSS","X","HLINE","VLINE"]
 # world_shapes = ["CROSS","X","HLINE","VLINE"]
 world_sizes = xrange(3,14,2)

### 2015-04-18 src/interface_layer_organized.py

@@ -16,7 +16,7 @@ from generateWorldMsg import *
 
 MAX_TRAJ_COUNT = 50
 MAX_ITERS = 1000
-DIR = '/home/bhomberg/indigo_ws/src/6834-task-motion-planner/'
+DIR = os.path.abspath(os.path.dirname(__file__) + '/../') + '/'
 #DIR = '/home/vmlane/catkin_ws/src/6834-task-motion-planner/'
 
 class InterfaceLayer(object):    

### 2015-04-18 src/planner_server.py

@@ -47,7 +47,7 @@ class TaskPlannerServer(object):
 
 if __name__ == "__main__":
     #task_planner_server = TaskPlannerServer("/home/vmlane/catkin_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/vmlane/catkin_ws/src/6834-task-motion-planner/domain")
-    task_planner_server = TaskPlannerServer("/home/ragtz/Downloads/FF-v2.3/", "/home/ragtz/indigo_workspace/src/6834-task-motion-planner/domain")
+    task_planner_server = TaskPlannerServer(os.path.abspath(os.path.dirname(__file__) + '/../') + '/FF-v2.3/', os.path.abspath(os.path.dirname(__file__) + '/../') + '/domain')
     #task_planner_server = TaskPlannerServer("/home/bhomberg/indigo_ws/src/6834-task-motion-planner/FF-v2.3/", "/home/bhomberg/indigo_ws/src/6834-task-motion-planner/domain")
     task_planner_server.run()
     

### 2015-04-18 tests/small_tests.py

@@ -28,10 +28,10 @@ numTests = 10
 
 genState =  StateGeneratorSmall()
 
-DIR_6834 = '/home/ragtz/indigo_workspace/src/6834-task-motion-planner/'
+DIR_6834 = os.path.abspath(os.path.dirname(__file__) + '/../') + '/'
 
 # One Cover Bechmark
-out_file = open('smallTests.output','w')
+out_file = open(DIR_6834 + 'tests/smallTests.output','w')
 
 # set up the world
 worlds = generateWorlds()

### 2015-04-29 documentation/draft.tex
pose generator works for pickup

@@
 \title{Combined Task and Motion Planner through an Interface Layer}
-\author{Alex Gutierrez (ragtz@mit.edu), Bianca Homberg (bhomberg@mit.edu), and Veronica Lane (vmlane@mit.edu)}
+\author{Alex Gutierrez (ragtz@mit.edu), Bianca Homberg (bhomberg@mit.edu), \\and Veronica Lane (vmlane@mit.edu)}
 
@@
 \subsection{Results}
+\begin{figure}[t]
+	\centering
+	\subfloat{\includegraphics[width=.45\linewidth]{figures/bvm}}
+	\qquad
+	\subfloat{\includegraphics[width=.45\linewidth]{figures/bvt}}
+	\qquad
+	\subfloat{\includegraphics[width=.45\linewidth]{figures/bvrt}}
+	\qquad
+	\subfloat{\includegraphics[width=.45\linewidth]{figures/ovm}}
+	\qquad
+	\subfloat{\includegraphics[width=.45\linewidth]{figures/ovt}}
+	\qquad
+	\subfloat{\includegraphics[width=.45\linewidth]{figures/ovrt}}
+	\qquad
+	\subfloat{\includegraphics[width=.45\linewidth]{figures/square}}
+	\caption{Benchmarking plots\label{fig:benchmarkPlots}}
+\end{figure}
 The goal of each test was to move the green block, at the center of a grid of blocks, to a goal surface. 
@@
 We tested each grid shape over a range of sizes ranging from 3 to 13. ref{fig-benchmarks} 
-The most difficult benchmark we tested was the 13x13 square grid. Larger tests caused the FF planner to segfault.
+The most difficult benchmark we tested was the 13x13 square grid.
+Larger tests caused the FF planner to segfault.
+As seen in \ref{fig:benchmarkPlots}, as the size of the problem increases the number of calls increases.
 

### 2015-04-29 src/motion_planner_server.py

@@ -25,7 +25,7 @@ class MotionPlannerServer(object):
         moveit_commander.roscpp_initialize(sys.argv)
         
         print "============ Setting current state"
-        robot = moveit_commander.RobotCommander()
+        # robot = moveit_commander.RobotCommander
         scene = moveit_commander.PlanningSceneInterface()
         
         world_start_state = req.parameters.state.world

### 2015-04-29 src/pose_generator.py

@@ -79,11 +79,13 @@ class PoseGenerator:
         poseGen1 = pose()
         pose1 = poseGen1.pose
         # random yaw position
-        yaw = random.uniform(-math.pi, math.pi)
-        # x position along the circle around the cylinder
-        pose1.position.x = obj_pose.position.x + r*math.cos(yaw) + self.GRIPPER_OFFSET
-        pose1.position.y = obj_pose.position.y + r*math.sin(yaw)
+        # yaw = random.uniform(-math.pi, math.pi)
+        yaw = -math.pi/4
+        # x,y position along a circle around the cylinder
+        pose1.position.x = obj_pose.position.x + r * math.cos(yaw - math.pi)
+        pose1.position.y = obj_pose.position.y - r * math.sin(yaw - math.pi)
         pose1.position.z = z
+        print yaw
         pose1.orientation = self._rpy_to_orientation(math.pi/2.0,0,yaw)
         # yaw position s.t. the gripper points towards the cylinder
         poseGen1.gripperOpen = True
@@ -115,10 +117,10 @@ class PoseGenerator:
         # Standard Pose: A pose s.t. the group is out of the way of the other 
         # objects in a standard position
         poseGen5 = pose()
-        pose5 = poseGen5.pose
-        # x,y = 0,0
-        pose5.position.z = CLEARANCE_HEIGHT
-        pose5.orientation = self._rpy_to_orientation(math.pi/2.0,0,0)
+        poseGen5.pose.position.x = .8
+        poseGen5.pose.position.y = 1
+        poseGen5.pose.position.z = CLEARANCE_HEIGHT
+        poseGen5.pose.orientation = self._rpy_to_orientation(math.pi/2.0,0,0)
         poseGen5.gripperOpen = False
 
         # An array of pose messages
@@ -188,8 +190,10 @@ class PoseGenerator:
             
         # Move out of the way to the standard position
         poseGen6 = pose()
+        poseGen6.pose.position.x = .8
+        poseGen6.pose.position.y = 1
         poseGen6.pose.position.z = CLEARANCE_HEIGHT
-        poseGen6.pose.orientation = poseGen5.pose.orientation
+        poseGen6.pose.orientation = self._rpy_to_orientation(math.pi/2.0,0,0)
         poseGen6.gripperOpen = True
 
         # Return array of custom pose messages

### 2015-04-29 tests/pose_generator_motion_planner_test.py

@@ -42,8 +42,8 @@ def pickupTest(action, motion_server, poseGen):
     primitive.dimensions = [.25, .02]
     obj1.primitives.append(primitive)
     pose = Pose()
-    pose.position.x = 0.9
-    pose.position.y = -.15
+    pose.position.x = 0.8
+    pose.position.y = 0.15
     pose.position.z = 0.16
     pose.orientation.w = 1
     obj1.primitive_poses.append(pose)
@@ -137,10 +137,10 @@ if __name__ == "__main__":
     poseGen = PoseGenerator()
     
     #(pickup,obj1,left_arm,pose1,pose2)
-    for i in range(8):
-        pickupTest('(PICKUP,obj1,left_arm,pose1,pose2)', motion_server, poseGen)
+    # for i in range(8):
+    #     pickupTest('(PICKUP,obj1,left_arm,pose1,pose2)', motion_server, poseGen)
     
-    #(putdown,obj1,left_arm,pose1,pose2,tloc)
-    #for i in range(10):
-    #    putdownTest('(putdown,obj1,left_arm,pose1,pose2,surf1)', motion_server, poseGen)
+    # (putdown,obj1,left_arm,pose1,pose2,tloc)
+    for i in range(8):
+       putdownTest('(putdown,obj1,left_arm,pose1,pose2,surf1)', motion_server, poseGen)
         

### 2015-05-09 src/pose_generator.py
Change in slice handling

@@ -26,7 +26,7 @@ class PoseGenerator:
         self.sliceSize = 2 * math.pi/self.SLICES
         self.pickup_ub = -BOUND
         self.putdown_ub = -BOUND
-        self.MAX_COUNT = 10
+        self.MAX_COUNT = SLICES
 
     # Generates a gripper pose given an action and a world description
     # action = a string containing (action, arm, object_name)

### 2015-05-09 documentation/ps4.tex

--- 2015-04-18 documentation/draft.tex
@@
 The interface layer starts by asking the task planner to generate a high level plan and has the motion planner instantiate motion plans corresponding to each action.  
-When it's not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner.  
+When it is not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner.  
 Then, the task planner replans from that state and the process continues.  
@@
 At start time, the task planner is given a PDDL domain specifying the different actions that are feasible along with their preconditions and postconditions.  
-For individual calls to the task planner, the interface layer takes an internal `state' variable, converts it to PDDL format, and sends it along to be solved.  
+For individual calls to the task planner, the interface layer takes an internal \textit{state} variable, converts it to PDDL format, and sends it along to be solved.  
 The task planner responds with a high level plan or a notification that finding a plan failed.  
@@
 
-On each call to the motion planner, the interface layer provides the motion planner with the intended action, the world state, and a pose or set of poses  
-corresponding to sub-parts of the action. These poses are randomly generated for each action by a pose generator within the interface layer. 
+On each call to the motion planner, the interface layer provides the motion planner with the intended action, the world state, and a pose or set of poses corresponding to sub-parts of the action. 
+These poses are randomly generated for each action by a pose generator within the interface layer. 
 If it is possible to perform the action using the intermediary poses specified, the motion plan returns the trajectory and the updated world state.  
@@
 \item Call the task planner to create a high level plan.  
-In this case, the task planner doesn't yet know that block 2 is blocking block 1, so the plan is simply:
+In this case, the task planner has not yet inferred that block 2 is blocking block 1, so the plan is simply:
 
@@
 
-\item Next step is to call the motion planner to try and find a trajectory corresponding to each of these actions.  
+\item The next step is to call the motion planner to try to find a trajectory corresponding to each of these actions.  
 In this case, the motion planner fails to find a motion plan for step 1.
 
-\item The interface layer goes through removing objects to try to find what was causing the error for that action.  
+\item The interface layer removes objects to try to figure out which one was causing the error for that action.  
 The interface layer discovers that if it removes block 2, then the motion plan can be created just fine, so block 2 must be obstructing the path.
@@
 \item Now, we try to find a new high level plan.  
-Since block 2 is obstructing block 1, we can't pick up block 1 directly, so the task planner realizes it needs to move block 2 first before moving block 1. 
+Since block 2 is obstructing block 1, we cannot pick up block 1 directly, so the task planner realizes it needs to move block 2 first before moving block 1. 
 The new plan it creates is:
@@
 One of the key insights of this paper is that continuous variables can be referenced symbolically in the task planner within the PDDL domain.  
-For instance, consider the pose of the robot: this is a continuous, geometric state.  However, the task planner only keeps track of poses symbolically.  
-The task planner knows that there is some GPFG\_obj\_1 -- a Gripper Pose For Grasping -- for object 1, and it doesn't really care what that pose is, so long as it exists.  
+For instance, consider the pose of the robot: this is a continuous, geometric state.
+However, the task planner only keeps track of poses symbolically.  
+The task planner knows that there is some GPFG\_obj\_1 -- a Gripper Pose For Grasping -- for object 1, and it does not really care what that pose is, so long as it exists.  
 The task planner reasons over a variety of these symbolic variables, corresponding to poses and trajectories.  
@@
 
-We will follow [1] in using manipulation as an example environment.
-For any planning domain with some continuous variables and some discrete variables, it will be possible to transform the continuous variables to discrete symbolic references to continuous positions.
+We follow [1] in using manipulation as an example environment.
+For any planning domain with some continuous variables and some discrete variables, it is possible to transform the continuous variables to discrete symbolic references to continuous positions.
 For this example, we talk through the PICKUP action for a simple manipulator; the PUTDOWN action is analagous.
@@
 Here, we have three continuous variables that we represent symbolically: $traj$, for each of the trajectories, and $pose_1$ and $pose_2$, representing start and end locations for the robot's gripper.
-The preconditions and effects can also iterate over all of these symbolic variables, allowing us to mark that a picked up object doesn't obstruct any other objects, etc. 
+The preconditions and effects can also iterate over all of these symbolic variables, allowing us to mark that a picked up object does not obstruct any other objects, etc. 
 We have various predicates which describe different things about both the discrete variables and the continuous variables.
@@
 Neither the interface layer nor the task planner know what the poses correspond to in the real world.
-The pose generators instantiate specific poses which the motion planner verifies or discounts if it doesn't work.
+The pose generators instantiate specific poses which the motion planner verifies or discounts if it fails.
 Similarly, we have one trajectory for each potential pair of poses.  
-However, since the trajectory isn't actually used in any of the effects, we actually can ignore it entirely -- it doesn't change the high level plan and the interface layer will still know to have the motion planner create the relevant trajectories.
+However, since the trajectory is not actually used in any of the effects, we actually can ignore it entirely -- it does not change the high level plan and the interface layer will still know to have the motion planner create the relevant trajectories.
 So to make the plan more efficient, we actually cut out the $ISMP$ predicate and all references to trajectories.
@@
 It passes one pose to the interface layer at a time.  
-if none of the poses are feasible, the interface layer backtracks and resets the pose generator.
+If none of the poses are feasible, the interface layer backtracks and resets the pose generator. 
 The TryRefine method of the interface layer attempts to generate a feasible motion plan between each pose.
@@
 The subfigure a shows the motion planner's backtracking search when trying to instantiate motions for each of the high level actions.  
-Subfigure b shows the first possible scenario, where the backtracking search succeeds.  Subfigure c shows a second possible scenario, where the backtracking search doesn't succeed.  
+Subfigure b shows the first possible scenario, where the backtracking search succeeds.  Subfigure c shows a second possible scenario, where the backtracking search does not succeed.  
 There are multiple options of what can happen within this scenario: subfigure d shows an option where they determine that the block2 obstructs the trajectory.  
@@
 
-The original version of the algorithm, as shown in (Fig.
-\ref{fig:algorithms}), only attempts to find partial trajectories when it replans partway through the procedure.
+The original version of the algorithm, as shown in (Fig. \ref{fig:algorithms}), only attempts to find partial trajectories when it replans partway through the procedure.
 Our algorithm has a slight modification.
@@
 In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.  
-An analysis of the benefits of this approach are outlined in the benchmarking section.
+An analysis of the benefits of this approach are outlined in the results section.
 
@@
 
-If that doesn't succeed, we find a partial trajectory that goes as far as it can by calling the TryRefine subroutine in partial trajectory mode.  
+If that does not succeed, we find a partial trajectory that goes as far as it can by calling the TryRefine subroutine in partial trajectory mode.  
 This function returns a partial trajectory along with the step where it failed and the determined cause for failure.  
@@
 After we find this possible list of removed objects, we iterate through all of the objects we removed.  
-We attempt to add these objects in one by one, leaving added in all of those which don't obstruct our found motion plan.  
+We attempt to add these objects in one by one, leaving added in all of those which do not obstruct our found motion plan.  
 This leaves us with a local minimum of removed objects: it may be possible to find another smaller set of objects that, if removed, allow a valid motion plan.  
@@
 
-\section{Benchmarking}
-\subsection{Testing}
-\begin{figure}[t]
-\centering
-\def\svgwidth{0.5\textwidth}
-\input{figures/smallEnv.pdf_tex}
-\caption{Small Environment Test Example. The goal was for the blue blocks to be on surface I and the red blocks to be on surface S.\label{fig:smallEnv}}
-\end{figure}
-We generated a set of small-scale tests to check the correctness of the interface layer.
-ref{fig-smallTest} Each test had three to four blocks initially placed on one or two surfaces.
-Some blocks were surrounded on 3 sides and others on all sides by walls and blocks.
-For blocks surrounded on 3 sides, the interface layer had to find the pose that picked up the block in the correct direction.
-For blocks surrounded on all sides, the interface layer needed to generate actions to move blocks in the way.
-
-\subsection{Procedure}
+\section{Results}
+\subsection{Test Scenarios}
 \begin{figure}[t]
@@
 \def\svgwidth{\textwidth}
-\input{figures/benchmarks.pdf_tex}
-\caption{Benchmarking Test Examples. The goal was to move the green block to another surface.\label{fig:benchmark}}
+\input{figures/scenarios.pdf_tex}
+\caption{Test Examples. The goal is to move the green block to another surface.\label{fig:scenarios}}
 
@@
 
-We performed a variety of benchmarking tests to measure the performance of the interface.
-We measured the performance of each test by the number of calls to both the task planner and motion planner and the runtime.
-ref{table-benchmarkTable}
-The difficulty of a benchmark increased as the total number \textit{obstructions} increased.
-The total number of obstructions was counted by summing the number of directions around each block that were obstructed.
-For the ordinal directions, a neighboring block in any one of three locations obstructs the direction.
-For example, a neighboring block above, to the right or to the top right corner of a block obstructs the northeast direction of the block.
-Furthermore, as the number of blocks for a particular grid shape increased, the test difficulty increased, since the total number of obstructions increased.
+Baxter executes a variety of tests to measure the performance of the interface. 
+The goal of each test is to move the cylinder at the center of an arrangment of objects, to a goal surface. 
+We tested a variety of different 3x3 object arrangements on Baxter, including a square grid, an X, a cross, a vertical line, and a horizontal line [Fig. \ref{fig:scenarios}].
 
-\subsection{Results}
-The goal of each test was to move the green block, at the center of a grid of blocks, to a goal surface. 
-We tested a variety of different grid shapes, including a square grid, an X, a cross, and lines. 
-We tested each grid shape over a range of sizes ranging from 3 to 13. ref{fig-benchmarks} 
-The most difficult benchmark we tested was the 13x13 square grid. Larger tests caused the FF planner to segfault.
+The most difficult scenario we tested was the square grid.
+The difficulty of a scenario depends on the number of blocks for a particular grid shape. 
+As the total number of \textit{obstructions} increases, the test difficulty increased. 
+The total number of obstructions is measured by counting the number of directions around each object that were obstructed. 
+For the ordinal directions, a neighboring object in any one of three locations obstructs the direction. 
+For example, the northeast direction of an object is obstructed by a neighboring object above, to the right or to the top right corner.
 
-Figure \ref{benchmark2} shows the results for the original algorithm, minus our modification.
-(Our modification always tries to find a perfect plan after adding a new high level plan section to the plan, rather than immediately trying to find a new partial trajectory.)  For the very simplest cases, the original algorithm performs better, since it makes the same number of motion and task planner calls but has less backtracking overhead.
-However, for the more complicated environments, the cross and the square, our algorithm was significantly faster, as shown in \ref{benchmark}.
+During preliminary testing, the results for the original algorithm took significantly longer when tested in simulation.  
+Our modification always tries to find a perfect plan after adding a new high level plan section to the plan, rather than immediately trying to find a new partial trajectory. 
+Since our algorithm was significantly faster we used it for each of the test scenarios.
 
+We measured the performance of each test by the runtime and the number of calls to both the task planner and motion planner [Fig. \ref{benchmark}]. 
 The interface layer is designed to be independent of any specific task and motion planner libraries, therefore number of calls to the motion and task planner measures the performance of the interface layer better than the total runtime, since the actual runtime will be very dependent on the motion planner and task planner chosen.
+
+\subsection{Test Results}
 
@@
 Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
-Horizontal Line & 3 & 12 & 3 & 1 & .023\\
-& 5 & 24 & 4 & 1 & .028\\
-& 7 & 36 & 4 & 1 & .029\\
-& 9 & 48 & 4 & 1 & .029\\
-& 11 & 60 & 4 & 1 & .034\\
-& 13 & 72 & 4 & 1 & .037\\
+Horizontal Line & 3 & 12 & ? & ? & ?\\
 \hline
-Vertical Line & 3 & 12 & 4 & 1 & .024\\
-& 5 & 24 & 4 & 1 & .027\\
-& 7 & 36 & 4 & 1 & .028\\
-& 9 & 48 & 4 & 1 & .028\\
-& 11 & 60 & 4 & 1 & .037\\
-& 13 & 72 & 4 & 1 & .036\\ 
+Vertical Line & 3 & 12 & ? & ? & ?\\
 \hline
-X & 5 & 8 & 2 & 1 & .026\\
-& 9 & 16 & 2 & 1 & .034\\
-& 13 & 24 & 2 & 1 & .036\\
-& 17 & 32 & 2 & 1 & .047\\
-& 21 & 40 & 2 & 1 & .066\\
-& 25 & 48 & 2 & 1 & .079\\ 
+X & 5 & 8 & ? & ? & ?\\
 \hline
-Cross & 5 & 20 & 39 & 3 & .16\\
-& 9 & 44 & 50 & 2 & .20\\
-& 13 & 68 & 59 & 2 & .23\\
-& 17 & 92 & 71 & 3 & .26\\
-& 21 & 116 & 78 & 3 & .31\\
-& 25 & 140 & 77 & 3 & .39\\ 
+Cross & 5 & 20 & ? & ? & ?\\
 \hline
-Square & 9 & 56 & 54 & 2 & .16\\
-& 25 & 176 & 294 & 6 & 1.06\\
-& 49 & 360 & 818 & 10 & 5.07\\
-& 81 & 608 & 3177 & 24 & 34.68\\
-& 121 & 920 & 3681 & 22 & 87.06\\
-& 169 & 1296 & 14216 & 57 & 518.61\\ 
+Square & 9 & 56 & ? & ? & ?\\
 \hline
@@
 \end {tabular}
-\caption{Benchmark Tests - Our Modified Algorithm}
+\caption{Test Scenarios Performance}
 \label{benchmark}
@@
 
-\begin{figure}
-\begin{tabular}[t]{|l|l|l|l|l|l|}
-\hline
-Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
-Horizontal Line & 3 & 12 & 3 & 1 & .016\\
-& 9 & 48 & 4 & 1 & .025\\
-& 13 & 72 & 4 & 1 & .033\\
-\hline
-Vertical Line & 3 & 12 & 4 & 1 & .022\\
-& 9 & 48 & 4 & 1 & .027\\
-& 13 & 72 & 4 & 1 & .031\\ 
-\hline
-X & 5 & 8 & 2 & 1 & .014\\
-& 17 & 32 & 2 & 1 & .031\\
-& 25 & 48 & 2 & 1 & .056\\ 
-\hline
-Cross & 5 & 20 & 47 & 5 & .15\\
-& 17 & 92 & 206 & 10 & .68\\
-& 25 & 140 & 390 & 14 & 1.56\\ 
-\hline
-Square & 9 & 56 & 145 & 11 & .45\\
-& 25 & 176 & 4354 & 143 & 16.55\\
-
-\hline
-
-\end {tabular}
-\caption{Benchmark Tests - Original Algorithm}
-\label{benchmark2}
-\end{figure}
 \section{Limitations}
@@
 
-The two immediately relevant open questions are whether it's possible to design a similar interface between task and motion plans which returns optimal plans or which can be used to do online planning.
+The two immediately relevant open questions are whether it is possible to design a similar interface between task and motion plans which returns optimal plans or which can be used to do online planning.
 Currently, the interface layer works only in deterministic, fully observable environments.  

### 2015-05-12 documentation/ps4.tex
worked on documentation

@@
 
-\section{Introduction}
+\section{Test Scenarios}
 
-In order to achieve high level goals a robot must combine task and motion planning. 
-A robot uses task planning to determine its long term strategy and motion planning to determine the movements it  will execute to achieve the task. 
-Effectively combining task and motion planning is an open research problem. 
-We implemented an interface between the motion and task planning based on that outlined in [1]. 
-Our system uses off-the-shelf task and motion planners and makes few assumptions about their implementation.
+We present an interface between a task planner and motion planner [1].
+Baxter executes a variety of tests to measure the performance of the interface layer.
+The tests demonstrate that the interface layer respects all of the geometric constraints.
+Baxter picks up objects in a reasonable order to avoid collisions.
 
-An alternative approach to developing an interface between the task and motion planner is for the task planner to discretize the geometric state space. 
-However, the number of required discretizations to solve the problem is generally very large and results in extremely large or infeasible problems. 
-An interface allows the task planner state space to use an abstract state space which ignores geometry. 
-The interface layer translates geometric constraints and passes them to the task planner.
+The goal of the first test is to move the object at the center of a 3x3 square grid of objects to a goal surface. 
+The goal of the second test is to sort red, green, and blue blocks into separate bins.
+Figure \ref{fig:scenarios} shows the setup of the different test scenarios.
 
-\section{Problem Statement}
+\begin{figure}[h]
+\centering
+\def\svgwidth{.4\textwidth}
+\input{figures/scenarios.pdf_tex}
+\caption{Set up of test scenarios.\label{fig:scenarios}}
+\end{figure}
 
-In robotics, it is often necessary to create a plan for a series of motions of the robot in order to achieve some high level objective.
-In order to find a task plan which is actually feasible, the task planner must have some knowledge of the geometry of the world.
-Without knowledge of the actual spatial configurations of objects in the world, the task planner would create plans that could not complete some actions, due to infeasible motion plans from blocking objects or interference between the robot and the environment.
+\section{Technical Approach}
+The three components of our combined task and motion planner system are:  \(1\) the task planner, \(2\) the motion planner, and \(3\) the interface layer.
+The interface layer is composed of the state update and pose generator modules [Fig.
+\ref{fig:blockDiagram}].
 
-The high level problem this implementation addresses is to create a combined task and motion planner, following that presented in [1].  
-This approach allows the motion planner to give information to the task planner and keeps continuous variables continuous, rather than discretizing.  
-This prevents a combinatorial explosion of the state space that the task planner needs to search over.
-
-The main contribution of this implementation is an interface layer.  
-This interface layer is designed to be planner-independent: that is, it can work with any motion planner and task planner, so long as the outputs from each are conformed to the interface specification.
-The interface layer interleaves calls between the task planner and the motion planner, using geometric feasibility determined through the motion planner to affect the state given to the task planner to plan from.
-
-\section{High Level Approach}
-
-The interface layer starts by asking the task planner to generate a high level plan and has the motion planner instantiate motion plans corresponding to each action.  
-When it is not possible to generate a motion plan, the interface layer determines what geometric constraints are causing the problem and relays this back to the task planner.  
-Then, the task planner replans from that state and the process continues.  
-When necessary, backtracking occurs.
-
-At start time, the task planner is given a PDDL domain specifying the different actions that are feasible along with their preconditions and postconditions.  
-For individual calls to the task planner, the interface layer takes an internal \textit{state} variable, converts it to PDDL format, and sends it along to be solved.  
-The task planner responds with a high level plan or a notification that finding a plan failed.  
-If finding a plan failed, the interface layer begins backtracking.  
-If a high level plan is found, the interface layer begins searching for refinements of each action as a motion plan.
-
-On each call to the motion planner, the interface layer provides the motion planner with the intended action, the world state, and a pose or set of poses corresponding to sub-parts of the action. 
-These poses are randomly generated for each action by a pose generator within the interface layer. 
-If it is possible to perform the action using the intermediary poses specified, the motion plan returns the trajectory and the updated world state.  
-If not, it returns an error message.
-
-If the motion plan does not succeed, a variety of poses are tried.  
-Again, poses are generated randomly from a pose generator.  
-If no poses are successful, the interface layer determines what is blocking the motion plan from succeeding by removing objects from the environment until a feasible motion plan is found.  
-If still no feasible motion plan is found, backtracking is required.  
-If a feasible motion plan is found with some subset of objects removed, then that information is relayed back to the task planner after the PDDL state is appropriately updated.
-This update adds predicates corresponding to the object obstructions, and the task planner is asked to replan starting from the step where we failed to find a motion plan.
-This whole process continues until a feasible motion plan has been found.
-
-\subsection{Simple Example Walkthrough}
-
-\begin{figure}[t]
+\begin{figure}[h]
 \centering
 \def\svgwidth{0.5\textwidth}
-\input{figures/walkthrough.pdf_tex}
-\caption{Walkthrough Example. The goal is for the red block to be on surface S.\label{fig:walkthrough}}
+\input{figures/blockDiagram.pdf_tex}
+\caption{System Block Diagram\label{fig:blockDiagram}}
 \end{figure}
 
-In this environment, we have two objects, blocks 1 and 2, and our goal is to put block 1 into area S.  
-However, we cannot pick up block 1 directly since the walls and block 2 surround it.  
-Here we walk through the steps the interface layer takes when solving this problem in order to explain the details of the interface layer's construction.
+\subsection{Task Planner}
+We used the FF task planner. 
+Our software for the task planner is the same as the previous problem set. 
+The task planner takes in a PDDL file as input and receives a state from the interface layer. 
+It generates the planned actions.
 
-\begin{enumerate}[i.]
+\subsection{Motion Planner}
+We used the MoveIt! motion planner. 
+[TODO: Alex will write this]
 
-\item Call the task planner to create a high level plan.  
-In this case, the task planner has not yet inferred that block 2 is blocking block 1, so the plan is simply:
-
-\begin{enumerate}[1.]
-\item PICKUP BLOCK1 with GRIPPER
-
-\item PUTDOWN BLOCK1 on SURFACE S
-\end{enumerate}
-
-\item The next step is to call the motion planner to try to find a trajectory corresponding to each of these actions.  
-In this case, the motion planner fails to find a motion plan for step 1.
-
-\item The interface layer removes objects to try to figure out which one was causing the error for that action.  
-The interface layer discovers that if it removes block 2, then the motion plan can be created just fine, so block 2 must be obstructing the path.
-
-\item We add a predicate corresponding to BLOCK2 OBSTRUCTS BLOCK1 to the planner's state.
-
-\item Now, we try to find a new high level plan.  
-Since block 2 is obstructing block 1, we cannot pick up block 1 directly, so the task planner realizes it needs to move block 2 first before moving block 1. 
-The new plan it creates is:
-
-\begin{enumerate}[1.]
-\item PICKUP BLOCK2 	with GRIPPER
-\item PUTDOWN BLOCK2 on SURFACE S
-\item PICKUP BLOCK1 with GRIPPER
-\item PUTDOWN BLOCK1 on SURFACE S
-\end{enumerate}
-
-\item Now, we again go to the motion planner and try to find a motion plan corresponding to every action.
-In this case, there are no more obstructions, so the process works!
-
-\item Ultimately, the algorithm returns the high level plan in conjunction with a motion plan trajectory for every step of the high level plan.
-
-\end{enumerate}
-
-\section{Technical Details}
-
-In this section, we discuss the key insight of the original paper: the ability to avoid discretization by representing continuous variables symbolically via references.  
-We also discuss the pose generators which propose real-world instantiations of these references.  
-Finally, we walk through the algorithm in detail.
-
-\subsection{Representing Continuous Variables Symbolically}
-
-One of the key insights of this paper is that continuous variables can be referenced symbolically in the task planner within the PDDL domain.  
-For instance, consider the pose of the robot: this is a continuous, geometric state.
-However, the task planner only keeps track of poses symbolically.  
-The task planner knows that there is some GPFG\_obj\_1 -- a Gripper Pose For Grasping -- for object 1, and it does not really care what that pose is, so long as it exists.  
-The task planner reasons over a variety of these symbolic variables, corresponding to poses and trajectories.  
-The motion planner and pose generators take these symbolic variables and associate them with corresponding real locations and motions in the world.  
-This is the key insight which allows the task planner to reason about continuous variables without discretizing.
-
-We follow [1] in using manipulation as an example environment.
-For any planning domain with some continuous variables and some discrete variables, it is possible to transform the continuous variables to discrete symbolic references to continuous positions.
-For this example, we talk through the PICKUP action for a simple manipulator; the PUTDOWN action is analagous.
-
-\vspace{10pt}
-
-$PICKUP(obj_1, gripper, pose_1, pose_2, traj)$
-
-$\; precon \; EMPTY(gripper), ROBOTAT(pose_1), $
-
-$\; \; \;\; \; \; ISGPFG(pose_2, obj), ISMP(traj, pose_1, pose_2), $
-
-$\; \; \; \; \; \;\forall obj' \neg OBSTRUCTS(obj', traj, obj_1)$
-
-$\; effect \; IN(obj_1, gripper), \neg EMPTY(gripper), $
-
-$\; \; \;\; \; \; \forall obj', traj' \neg OBSTRUCTS(obj_1, traj', obj'), $
-
-$\; \; \; \; \; \;\forall obj' traj', tloc' \neg PDOBSTRUCTS(obj_1, traj', obj', tloc')$
-
-\vspace{10pt}
-
-Here, we have three continuous variables that we represent symbolically: $traj$, for each of the trajectories, and $pose_1$ and $pose_2$, representing start and end locations for the robot's gripper.
-The preconditions and effects can also iterate over all of these symbolic variables, allowing us to mark that a picked up object does not obstruct any other objects, etc. 
-We have various predicates which describe different things about both the discrete variables and the continuous variables.
-
-\vspace{10pt}
-
-$EMPTY(gripper)$ -- gripper is empty and thus available to hold a block.
-
-$ROBOTAT(pose_1)$ -- robot pose,  $pose_1$ is a symbolic reference to a continuous variable.
-
-$ISGPFG(pose, obj)$ -- $pose$ is a Gripper Pose For Grasping (GPFG) an object $obj$.
-
-$ISMP(traj, pose_1, pose_2)$ -- $traj$ is a motion plan from $pose_1$ to $pose_2$.
-
-$OBSTRUCTS(obj_1, traj, obj_2)$ -- $obj_1$ blocks $obj_2$ from being picked up along $traj$.
-
-$PDOBSTRUCTS(obj_1, traj, obj_2, tloc)$ -- $obj_1$ blocks $obj_2$ from placement at $tloc$ along $traj$.
-
-$IN(obj_1, gripper)$ -- $obj_1$ currently grasped by $gripper$.
-
-\vspace{10pt}
-
-How do we come up with all of these symbolic references?  
-We create as many as we need.  
-In this case, we need to have a pose where we can pick up each object and put each object down.  
-Neither the interface layer nor the task planner know what the poses correspond to in the real world.
-The pose generators instantiate specific poses which the motion planner verifies or discounts if it fails.
-Similarly, we have one trajectory for each potential pair of poses.  
-However, since the trajectory is not actually used in any of the effects, we actually can ignore it entirely -- it does not change the high level plan and the interface layer will still know to have the motion planner create the relevant trajectories.
-So to make the plan more efficient, we actually cut out the $ISMP$ predicate and all references to trajectories.
-
-How do we pass geometric information from the environment back to the task planner?  
-We do this via the $OBSTRUCTS$ and $PDOBSTRUCTS$ predicates.  
-These tell the task planner that certain objects are blocking motions related to other objects.  
-This allows the task planner to have the robot first move the blocking objects so it can get to the other objects.
-
-\subsection{Pose Generators}
-
-When the pose generator is called by the interface layer, it generates a set of random poses for each action. 
-Each pose is made up of a set of waypoints.
-For example for the PICKUP action, it generates the following waypoints: near the cylinder and pointing towards it, touching the cylinder, lifting the cylinder, and a standard home position.
-It passes one pose to the interface layer at a time.  
-If none of the poses are feasible, the interface layer backtracks and resets the pose generator. 
-The TryRefine method of the interface layer attempts to generate a feasible motion plan between each pose.
-The motion planner is called to create this motion plan, including motion plans between waypoints.
-
-\subsection{Main Interface Layer}
+\subsection{Interface}
 
@@
 \end{figure}
-
-This figure (Fig. \ref{fig:figure4}), included with text from [1], explains the flow of control of the interface layer through a variety of situations, including more than the simple case covers.  
-The subfigures in this diagram explain on a high level the different steps the interface layer takes when solving a problem.  
-The subfigure a shows the motion planner's backtracking search when trying to instantiate motions for each of the high level actions.  
-Subfigure b shows the first possible scenario, where the backtracking search succeeds.  Subfigure c shows a second possible scenario, where the backtracking search does not succeed.  
-There are multiple options of what can happen within this scenario: subfigure d shows an option where they determine that the block2 obstructs the trajectory.  
-This triggers the behavior discussed earlier, where the state is updated for the task planner.  
-Subfigure e shows the new task plan after replanning occurs.  
-After this, the interface layer will repeat the process of attempting to refine this new plan.  
-Subfigure f shows an alternative option, where the blocking object is determined to be the table, which is not movable.  
-Then, the state is updated as before and the task planner is called, but no solution is found, so backtracking occurs.
-
-\subsubsection{Algorithm Improvements}
-
-The original version of the algorithm, as shown in (Fig. \ref{fig:algorithms}), only attempts to find partial trajectories when it replans partway through the procedure.
-Our algorithm has a slight modification.
-Every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.
-In some scenarios, some poses will not work but others will, so it is better to try to make the simplest possible plan work before giving up and making the high level plan more complicated.  
-In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.  
-An analysis of the benefits of this approach are outlined in the results section.
 
@@
 
-The outer loop of the algorithm interfaces with the high level task planner.  
 We start with an initial state where no objects obstruct any motions.  
 From there, we look for a high level plan.  
-If the problem is not solvable even without any obstructions from the environment, then the problem is unsolvable and we immediately return that information.  
 If we do succeed at finding a high level task plan, we begin the process of attempting to find a motion corresponding to each action.
@@
 In error free mode, it performs backtracking search to try to find a full plan from start to finish.
-The backtracking search is over possible pose instantiations: since some poses may be infeasible and since previous choices may affect future choices, the backtracking search iterates over all possible poses in order to find a full solution if a full solution exists.
 
@@
 
+\subsubsection{State Update}
+
+When an action is infeasible because an object is blocking another object, the interface layer updates the state and calls the task planner. 
+If the object is movable, the task planner will generate a plan to move the object out of the way before moving the target object.
+If the object is not movable, such as the table, the interface will perform backtracking search to try to find a full plan from start to finish.
+The backtracking search is over possible pose instantiations: since some poses may be infeasible and since previous choices may affect future choices, the backtracking search iterates over all possible poses in order to find a full solution if a full solution exists.
+
+Every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.
+In our manipulation example, the interface tries to pick up blocks from all angles before giving up and assuming they must be blocked by something.
+
+\subsubsection{Pose Generator}
+
+When the pose generator is called by the interface layer, it generates a set of random poses for each action. 
+Each pose is made up of a set of waypoints.
+
+For the PICKUP action, it generates the following waypoints: near the object and pointing towards it, touching the object, lifting the object, and a standard home position. 
+The first waypoint is randomly generated and places the gripper about 15 centimeters away from the object.
+We divided the set of possible random yaw angles around the object into several distinct ranges, called \textit{slices}. 
+Each call to the pose generator generates a random angle in one of the ranges.
+The second waypoint moves the arm so that the gripper can object.
+The third waypoint is in the exact same position with the gripper closed.
+The next waypoint is directly above the previous waypoint, high enough so that the object is above all of the other objects on the table.
+Finally, the last waypoint goes to the standard home position for the square grid task and moves  above the correct bin for the sorting task.
+
+For the PUTDOWN action, the pose generator generates the following waypoints: above the target location, at the target location with the gripper closed, at the target location with the gripper open, 15 cm backed away from the target location, and the standard home position.
+The target location is randomly generated, but the pose generator checks to make sure that no objects are at or near the target location.
+
+To reiterate, a pose is a set of waypoints. 
+The pose generator keeps track of the number of poses it has generated, at least one for each slice.
+Once the pose generator has generated the maximum number of poses, it returns None, to indicate that no poses are feasible.
+The interface layer then backtracks and resets the pose generator.
+The TryRefine method of the interface layer attempts to generate a feasible motion plan between each pose.  
+The motion planner is called to create this motion plan, including motion plans between waypoints.
+
 \section{Results}
-\subsection{Test Scenarios}
-\begin{figure}[t]
-\centering
-\def\svgwidth{\textwidth}
-\input{figures/scenarios.pdf_tex}
-\caption{Test Examples. The goal is to move the green block to another surface.\label{fig:scenarios}}
-
-\end{figure}
-
-Baxter executes a variety of tests to measure the performance of the interface. 
-The goal of each test is to move the cylinder at the center of an arrangment of objects, to a goal surface. 
-We tested a variety of different 3x3 object arrangements on Baxter, including a square grid, an X, a cross, a vertical line, and a horizontal line [Fig. \ref{fig:scenarios}].
-
-The most difficult scenario we tested was the square grid.
-The difficulty of a scenario depends on the number of blocks for a particular grid shape. 
-As the total number of \textit{obstructions} increases, the test difficulty increased. 
-The total number of obstructions is measured by counting the number of directions around each object that were obstructed. 
-For the ordinal directions, a neighboring object in any one of three locations obstructs the direction. 
-For example, the northeast direction of an object is obstructed by a neighboring object above, to the right or to the top right corner.
-
-During preliminary testing, the results for the original algorithm took significantly longer when tested in simulation.  
-Our modification always tries to find a perfect plan after adding a new high level plan section to the plan, rather than immediately trying to find a new partial trajectory. 
-Since our algorithm was significantly faster we used it for each of the test scenarios.
 
 We measured the performance of each test by the runtime and the number of calls to both the task planner and motion planner [Fig. \ref{benchmark}]. 
-The interface layer is designed to be independent of any specific task and motion planner libraries, therefore number of calls to the motion and task planner measures the performance of the interface layer better than the total runtime, since the actual runtime will be very dependent on the motion planner and task planner chosen.
-
-\subsection{Test Results}
+The interface layer is designed to be independent of any specific task and motion planner libraries, therefore the number of calls to the motion and task planner measures the performance of the interface layer better than the total runtime.
+The actual runtime depends on the motion planner and task planner chosen.
 
@@
 
-\section{Limitations}
-
-It is important to note that this planner is not guaranteed to find an optimal solution, or even to find a solution at all.  
-We refer you to [1] for a proof that this algorithm is guaranteed to find a solution for problems with certain properties.  
-However, due to the random nature of the pose generators and that there are limits set on the number of iterations, a valid plan may not be found for all problems.
-
-Furthermore, this system is not intended for online replanning.  
-It may be possible to use it for online replanning for some systems if it runs quickly on the particular problem, but it is not an intended feature of this algorithm.
-
-Finally, the runtime of this algorithm is based on the speed of the motion planner and the task planner used within it.  
-If the motion planner and task planner are not efficient, the interface layer will not produce answers quickly.  
-In particular, the number of calls to the motion planner is very large in order to gather the environmental information needed to pass on to the task planner.  
-So in particular, the running time of this algorithm will depend on the running time of the motion planner.
-
-\section{Open Questions}
-
-The two immediately relevant open questions are whether it is possible to design a similar interface between task and motion plans which returns optimal plans or which can be used to do online planning.
-Currently, the interface layer works only in deterministic, fully observable environments.  
-It would be very interesting to develop similar algorithms to work in non-deterministic or partially observable environments as well.
-
-Other interesting and relevant extensions could include the addition of more grasp primitives, for instance, push grasp primitives.
-
 \section{References}
@@
 Abbeel.
-"Combined Task and Motion Planning Through an Extensible Planner-Independent Interface Layer".
+\"Combined Task and Motion Planning Through an Extensible Planner-Independent Interface Layer\".
 IEEE International Conference on Robotics and Automation (ICRA), 2014.

### 2015-05-12 documentation/ps4.tex
documentation: put all sentences on different lines, added baxter description
updates to final paper, plus launch file/playback changes from yesterday I forgot to push

@@
 \headsep=0.25in
-
+\graphicspath{{./figures/}}
 \DeclareGraphicsExtensions{.jpg,.png,.svg}
@@
 
-\section{Test Scenarios}
+\section{Testing}
+
+\subsection{Baxter Robot}
+
+We ran our test scenarios on the Baxter robot [Fig. \ref{fig:baxter}], designed by Rethink Robotics. 
+Baxter is a humanoid robot with two 7 degree of freedom arms. 
+Our tests used only the right arm with two finger gripper.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=.2\textwidth]{baxter}
+\caption{The Baxter Robot \label{fig:baxter}}
+\end{figure}
+
+\subsection{Test Scenarios}
 
@@
 The three components of our combined task and motion planner system are:  \(1\) the task planner, \(2\) the motion planner, and \(3\) the interface layer. 
-The interface layer is composed of the state update and pose generator modules [Fig.
-\ref{fig:blockDiagram}].
+The interface layer is composed of the state update and pose generator modules [Fig. \ref{fig:blockDiagram}].
 
@@
 Our software for the task planner is the same as the previous problem set. 
-The task planner takes in a PDDL file as input and receives a state from the interface layer. 
-It generates the planned actions.
+The task planner is instantiated with a given PDDL domain file.  
+As a ROS service, it takes in a PDDL problem specification of current state and goal from the interface layer. 
+It returns a set of actions leading to the desired goal state.
 
@@
 \includegraphics[width=\textwidth]{figures/figure4.png}
-\caption{Illustration of the interface layer’s refinement process. Action arguments have been abbreviated. Taken from [1]
+\caption{Illustration of the interface layer’s refinement process. 
+Action arguments have been abbreviated. 
+Taken from [1]
 \label{fig:figure4}}
@@
 
-To find the blocking objects, we start by iterating through a randomized list of the objects.  We continue removing objects until we find a successful motion plan.  
+To find the blocking objects, we start by iterating through a randomized list of the objects.  
+We continue removing objects until we find a successful motion plan.  
 We will eventually find a successful motion plan since if there are no other objects in the world, the motion should succeed.  
@@
 When an action is infeasible because an object is blocking another object, the interface layer updates the state and calls the task planner. 
-If the object is movable, the task planner will generate a plan to move the object out of the way before moving the target object.
-If the object is not movable, such as the table, the interface will perform backtracking search to try to find a full plan from start to finish.
-The backtracking search is over possible pose instantiations: since some poses may be infeasible and since previous choices may affect future choices, the backtracking search iterates over all possible poses in order to find a full solution if a full solution exists.
+The interface layer, as described above, determines a list of obstructing objects.
+The state update function goes through a section of a high level plan, performing all of the actions and updating the current state of the world.
+Once the state update function reaches the step where the tryRefine function failed, the state update function adds predicates to the state describing which blocks obstruct other blocks.
+The state function updates each action based on the preconditions and postconditions of each action: it confirms that all of the preconditions are satisfied and then adds true postconditions and removes falsified postconditions.
 
-Every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.
-In our manipulation example, the interface tries to pick up blocks from all angles before giving up and assuming they must be blocked by something.
+For instance, for the PICKUP action, the state update functions confirms that the gripper is empty, adds the postcondition that the gripper is full and that the object is in the gripper and removes the postcondition that the object is on whichever surface it started on.
+%If the object is movable, the task planner will generate a plan to move the object out of the way before moving the target object. 
+%If the object is not movable, such as the table, the interface will perform backtracking search to try to find a full plan from start to finish.
+%The backtracking search is over possible pose instantiations: since some poses may be infeasible and since previous choices may affect future choices, the backtracking search iterates over all possible poses in order to find a full solution if a full solution exists.
+
+%Every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.  
+%In our manipulation example, the interface tries to pick up blocks from all angles before giving up and assuming they must be blocked by something.
 

### 2015-05-12 documentation/ps4.tex
modifying results table

--- 2015-05-12 documentation/ps4.tex
@@
 \begin{figure}
-\begin{tabular}[t]{|l|l|l|l|l|l|}
+\begin{tabular}[t]{|l|l|l|l|l|l|l|}\extrarowheight
 \hline
-Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
-Horizontal Line & 3 & 12 & ? & ? & ?\\
+
+Shape & Blocks & \shortstack{Goal Number of\\Blocks to Move} & Obstructions & \shortstack{Motion Planner\\Calls} & \shortstack{Task Planner\\Calls} & Runtime \\ \hline
+Square & 9 & 56 &  & ? & ?&\\
 \hline
-Vertical Line & 3 & 12 & ? & ? & ?\\
-\hline
-X & 5 & 8 & ? & ? & ?\\
-\hline
-Cross & 5 & 20 & ? & ? & ?\\
-\hline
-Square & 9 & 56 & ? & ? & ?\\
+Sorting & 9 & 56 & ? & ? & ?&\\
 \hline
@@
 \end{figure}
+
+\section{Limitations}
+
+\section{Optimizations}
 

### 2015-05-12 documentation/ps4.tex
fixed compile error

@@
 \begin{figure}
-\begin{tabular}[t]{|l|l|l|l|l|l|l|}\extrarowheight
+\begin{tabular}[t]{|l|l|l|l|l|l|l|}
 \hline
@@
 Shape & Blocks & \shortstack{Goal Number of\\Blocks to Move} & Obstructions & \shortstack{Motion Planner\\Calls} & \shortstack{Task Planner\\Calls} & Runtime \\ \hline
-Square & 9 & 56 &  & ? & ?&\\
+Square & 9 & 56 & ? & ? & ?& ? \\
 \hline
-Sorting & 9 & 56 & ? & ? & ?&\\
+Sorting & 9 & 56 & ? & ? & ?& ?\\
 \hline

### 2015-05-12 documentation/ps4.tex
added improvements section draft

--- 2015-05-12 documentation/ps4.tex
@@
 
-To find the blocking objects, we start by iterating through a randomized list of the objects.  
-We continue removing objects until we find a successful motion plan.  
-We will eventually find a successful motion plan since if there are no other objects in the world, the motion should succeed.  
-After we find this possible list of removed objects, we iterate through all of the objects we removed.  
-We attempt to add these objects in one by one, leaving added in all of those which do not obstruct our found motion plan.  
-This leaves us with a local minimum of removed objects: it may be possible to find another smaller set of objects that, if removed, allow a valid motion plan.  
-However, for this set of this set of objects, no object can be added back in without obstructing the motion plan.
-
 As described above in Algorithm 1, once the list of blocking objects is returned, the interface layer updates the state and attempts to replan from there.
@@
 
+\section{Improvements}
+
+We implemented a number of improvements in order to increase the efficiency of the algorithm.
+
+\subsection{Error-free mode}
+
+\subsection{Motion Planner Heuristic}
+
+\subsection{O(n) Identification of Obstructions}
+
+To find the blocking objects, we start by iterating through a randomized list of the objects.  
+We continue removing objects until we find a successful motion plan.  
+We will eventually find a successful motion plan since if there are no other objects in the world, the motion should succeed.  
+After we find this possible list of removed objects, we iterate through all of the objects we removed.  
+We attempt to add these objects in one by one, leaving added in all of those which do not obstruct our found motion plan.  
+This leaves us with a local minimum of removed objects: it may be possible to find another smaller set of objects that, if removed, allow a valid motion plan.  
+However, for this set of this set of objects, no object can be added back in without obstructing the motion plan.
+This algorithm for determining obstructing objects is $O(n)$.
+
+The paper originally describes an $O(n^2)$ algorithm for determining obstructing objects, starting by removing each individual object, then pairs of objects, etc.  
+This ensures a minimum removal set but requires significantly more motion planner calls.
+
 \section{Results}

### 2015-05-12 documentation/ps4.tex
finished writing results section, need to fill out table and add link to simulation video

--- 2015-05-12 documentation/ps4.tex
@@
 \section{Results}
-
+\subsection{Metrics}
 We measured the performance of each test by the runtime and the number of calls to both the task planner and motion planner [Fig. \ref{benchmark}]. 
@@
 
+\subsection{Square Grid}
+We ran the square grid scenario on a simulated Baxter robot.
+The planner took approximately an hour to find a feasible plan. 
+In simulation, Baxter successfully moves blocks to reach the target center block and places the center block on the target surface.
+A video of the successful test trial in simulation can be found at [TODO: link here].
+
+\subsection{Sorting}
+We ran the sorting task in simulation and on the physical Baxter robot.
+The planner took approximately an hour to find a feasible plan. 
+We ran many test trials to achieve a successful run because the system was open-loop with respect to the environment.
+It had feedback on the world position of the arms, but not on the position of the arms relative to the objects. This mean that drift accumulated over time.
+Baxter successfully sorts green, red, and blue blocks into different bins. 
+A video of the successful test trial can be found at http://youtu.be/445_t_lUBdU.
 \begin{figure}

### 2015-05-12 documentation/ps4.tex

@@
 The motion planner is called to create this motion plan, including motion plans between waypoints.
+
+\section{Improvements}
+
+We implemented a number of improvements in order to increase the efficiency of the algorithm.
+
+\subsection{Error-free mode}
+
+\subsection{Motion Planner Heuristic}
+
+\subsection{O(n) Identification of Obstructions}
+
+To find the blocking objects, we start by iterating through a randomized list of the objects.  
+We continue removing objects until we find a successful motion plan.  
+We will eventually find a successful motion plan since if there are no other objects in the world, the motion should succeed.  
+After we find this possible list of removed objects, we iterate through all of the objects we removed.  
+We attempt to add these objects in one by one, leaving added in all of those which do not obstruct our found motion plan.  
+This leaves us with a local minimum of removed objects: it may be possible to find another smaller set of objects that, if removed, allow a valid motion plan.  
+However, for this set of this set of objects, no object can be added back in without obstructing the motion plan.
+This algorithm for determining obstructing objects is $O(n)$.
+
+The paper originally describes an $O(n^2)$ algorithm for determining obstructing objects, starting by removing each individual object, then pairs of objects, etc.  
+This ensures a minimum removal set but requires significantly more motion planner calls.
 

### 2015-05-12 documentation/ps4.tex
updates to improvements section

--- 2015-05-12 documentation/ps4.tex
@@
 
-The original version of the algorithm, as shown in \ref{fig:algorithms}, only attempts to find partial trajectories when it replans partway through the procedure.  
-For our version of the algorithm, every time a new partial plan is generated, we first try to fill it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.
+Every time a new partial plan is generated, we first try to fill it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.
 
@@
 
+The original version of the algorithm, as shown in \ref{fig:algorithms}, only attempts to find partial trajectories when it replans partway through the procedure.  
+For our version of the algorithm, every time a new partial plan is generated, we first try to fill it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.
+
+This enables us to find plans a lot more quickly: whenever a plan is possible, we find it by backtracking search.  
+Often, the first pose that's tried won't be viable but another pose will.  
+Partial trajectory mode will only try the first pose before giving up and identifying blocking objects.
+If partial trajectory mode is continually used, then often the plans created are much longer than necessary just because an invalid first pose is chosen when other options would have worked fine.
+Using the full backtracking search on each new high level plan avoids this problem.
+
 \subsection{Motion Planner Heuristic}
@@
 This ensures a minimum removal set but requires significantly more motion planner calls.
+
+\subsection{Future improvements}
+
+The interface layer winds up making a lot of duplicate calls to the motion planner.
+If the interface layer kept track of more state, perhaps via some memoization process of poses and actions, it would be able to save a lot of motion call attempts.
+Furthermore, when the interface layer finds obstructing objects, it finds obstructing objects for a particular pose.  
+If that pose were stored, then the interface layer would never attempt to use a different pose which might have different blocking objects, and would instead directly use the pose that the plan was optimized for.
 

### 2015-05-12 documentation/ps4.tex
limitations

--- 2015-05-12 documentation/ps4.tex
@@
 
+The interface does not scale well to large object state spaces, as this increases the number of geometric constraints. 
+This increase in geometric constraints causes the number of motion planner calls to explode, slowing down the planning stage. 
+In addition, in its current implementation it only works within deterministic, fully-observable environments and is infeasible for online replanning.
+
 \section{Optimizations}

### 2015-05-12 documentation/ps4.tex
now compiles with url
minor changes
added motion planner heuristic

@@
 \usepackage{svg}
+\usepackage{hyperref}
 \usepackage{caption}
@@
 
+We added a heuristic to avoid motion planner calls in cases where we could easily determine that it would fail.
+Specifically, the motion planner service would use the world geometry and basic collision geometry to determine if the pose obviously would cause the robot arm to intersect with obstacles.
+This greatly increased the efficiency for planning in crowded environments since it enabled the motion planner to return a fail much more quickly, rather than trying the full planning procedure when the end goal wasn't reachable.
+
 \subsection{O(n) Identification of Obstructions}
@@
 Baxter successfully sorts green, red, and blue blocks into different bins. 
-A video of the successful test trial can be found at http://youtu.be/445_t_lUBdU.
+A video of the successful test trial can be found at \url{http://youtu.be/445_t_lUBdU}.
+
 \begin{figure}

### 2015-05-13 documentation/ps4.tex
Edits to final paper

@@
 
-\subsection{Test Scenarios}
+\subsection{Test Scenarios} \label{tests}
 
-We present an interface between a task planner and motion planner [1]. 
+We present an interface between a task planner and motion planner [2]. 
 Baxter executes a variety of tests to measure the performance of the interface layer. 
@@
 \section{Technical Approach}
-The three components of our combined task and motion planner system are:  \(1\) the task planner, \(2\) the motion planner, and \(3\) the interface layer. 
-The interface layer is composed of the state update and pose generator modules [Fig. \ref{fig:blockDiagram}].
+Through the use of the interface layer implemented in the previous problem set, a task planner can operate in a geometry-independent abstract state space while handling geometric constraint discovery and requisite replanning via communication between the interface layer and the task and motion planners.
+
+The interface layer was implemented in python as a ROS package, which is set up to communicate with user-implemented task and motion planners via the client/server paradigm.
+More specifically, the task and motion planners were implemented as ROS services.
+The interface layer acts as client to both of these services.
+Figure \ref{fig:blockDiagram} diagrams the system framework.
+
+Given that the pose generation and state update vary between domains, we implement domain specific pose generator class and state update function for the scenarios described in section \ref{tests}.
+
+%The three components of our combined task and motion planner system are:  \(1\) the task planner, \(2\) the motion planner, and \(3\) the interface layer. 
+%The interface layer is composed of the state update and pose generator modules [Fig. \ref{fig:blockDiagram}].
 
@@
 \subsection{Task Planner}
-We used the FF task planner. 
+We used the FF task planner [1]. 
 Our software for the task planner is the same as the previous problem set. 
@@
 \subsection{Motion Planner}
-We used the MoveIt! motion planner. 
-[TODO: Alex will write this]
+We used the MoveIt! motion planner [3]. We implenented a ROS service wrapper for this off-the-shelf motion planner so as to comply with the API.
+It takes as input the state of the world, the action to be performed, and a pose goal (i.e. a series of waypoints to perform the action).
+MoveIt!
+is then used to instantiate motion plans between these waypoints.
+The motion planner service returns a boolean specifying the success/failure of the instantiation of the motion plan, the motion plan itself, and the updated world state (which can be unchanged if the action failed).
 
@@
 Action arguments have been abbreviated. 
-Taken from [1]
+Taken from [2]
 \label{fig:figure4}}
@@
 	\subfloat{\includegraphics[width=.45\linewidth]{figures/algorithm2}}
-	\caption{Taken from[1]\label{fig:algorithms}}
+	\caption{Pseudo-code for the underlying algorithms of the interface layer. Taken from [2]\label{fig:algorithms}}
 \end{figure}
@@
 Each call to the pose generator generates a random angle in one of the ranges.
-The second waypoint moves the arm so that the gripper can object. 
+The second waypoint moves the arm so that the object is in the gripper. 
 The third waypoint is in the exact same position with the gripper closed. 
@@
 
-\subsection{Motion Planner Heuristic}
+\subsection{Motion Planner Collision Heuristic}
 
@@
 This leaves us with a local minimum of removed objects: it may be possible to find another smaller set of objects that, if removed, allow a valid motion plan.  
-However, for this set of this set of objects, no object can be added back in without obstructing the motion plan.
+However, for this set of objects, no object can be added back in without obstructing the motion plan.
 This algorithm for determining obstructing objects is $O(n)$.
@@
 
-\subsection{Future improvements}
+\subsection{Future Improvements}
 
@@
 
-Shape & Blocks & \shortstack{Goal Number of\\Blocks to Move} & Obstructions & \shortstack{Motion Planner\\Calls} & \shortstack{Task Planner\\Calls} & Runtime \\ \hline
-Square & 9 & 56 & ? & ? & ?& ? \\
+Task & \shortstack{Number of \\Blocks} & \shortstack{Blocks to Move} & \shortstack{Number of \\TP Calls} & \shortstack{Number of \\MP Calls} & Runtime \\ \hline
+Square Grid & 9 & 1 & ? & ? & ?\\
 \hline
-Sorting & 9 & 56 & ? & ? & ?& ?\\
+Sorting & 9 & 9 & ? & ? & ?\\
 \hline
@@
 This increase in geometric constraints causes the number of motion planner calls to explode, slowing down the planning stage. 
-In addition, in its current implementation it only works within deterministic, fully-observable environments and is infeasible for online replanning.
-
-\section{Optimizations}
+In addition, in its current implementation it only works within deterministic, fully-observable environments and is not suitable for online replanning.
 
@@
 
-[1] S.
+[1] J. Hoffmann, B. Nebel. ``The FF planning system: fast plan generation through heuristic search''. J. Artif. Int. Res. 14, 1, 253-302, 2001.
+
+[2] S.
 Srivastava, E.
@@
 Abbeel.
-\"Combined Task and Motion Planning Through an Extensible Planner-Independent Interface Layer\".
+``Combined Task and Motion Planning Through an Extensible Planner-Independent Interface Layer''.
 IEEE International Conference on Robotics and Automation (ICRA), 2014.
 
+[3] I. A. Sucan and Sachin Chitta, ``MoveIt!''. [Online] Available: http://moveit.ros.org
+
 \end{document}

### 2015-05-13 documentation/ps4.tex
edits to final paper

@@
 Baxter is a humanoid robot with two 7 degree of freedom arms. 
-Our tests used only the right arm with two finger gripper.
+Our tests used only the right arm with the two finger gripper.
 
@@
 The state update function goes through a section of a high level plan, performing all of the actions and updating the current state of the world.
-Once the state update function reaches the step where the tryRefine function failed, the state update function adds predicates to the state describing which blocks obstruct other blocks.
+Once the state update function reaches the step where the TryRefine function failed, the state update function adds predicates to the state describing which blocks obstruct other blocks.
 The state function updates each action based on the preconditions and postconditions of each action: it confirms that all of the preconditions are satisfied and then adds true postconditions and removes falsified postconditions.
@@
 
+For the sorting task, the PUTDOWN pose generator behaves slightly differently, since objects are dropped into bins rather than placed.
+In this case, the pose generator had a fixed specified location to drop the object and had no randomization.
+
 To reiterate, a pose is a set of waypoints. 
@@
 The original version of the algorithm, as shown in \ref{fig:algorithms}, only attempts to find partial trajectories when it replans partway through the procedure.  
-For our version of the algorithm, every time a new partial plan is generated, we first try to fill it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.
+For our version of the algorithm, every time a new partial plan is generated, we first try to instantiate it completely using backtracking search (calling TryRefine in error-free mode) before giving up and resorting to the partial trajectory finding.
 
@@
 In simulation, Baxter successfully moves blocks to reach the target center block and places the center block on the target surface.
-A video of the successful test trial in simulation can be found at [TODO: link here].
+A video of the successful test trial in simulation can be found at [TODO: link here].  We did not run this test on the real Baxter robot.
 
@@
 We ran the sorting task in simulation and on the physical Baxter robot.
-The planner took approximately an hour to find a feasible plan. 
+The planner took approximately twenty minutes to find a feasible plan. 
 We ran many test trials to achieve a successful run because the system was open-loop with respect to the environment.
 It had feedback on the world position of the arms, but not on the position of the arms relative to the objects. This mean that drift accumulated over time.
+Additionally, the Baxter arm is shaky, and without very much room for error in the motion plans, Baxter sometimes hit adjacent objects due to wobbling outside of the planned motion.
 Baxter successfully sorts green, red, and blue blocks into different bins. 
@@
 
-[1] J. Hoffmann, B. Nebel. ``The FF planning system: fast plan generation through heuristic search''. J. Artif. Int. Res. 14, 1, 253-302, 2001.
+\hspace{.25in}[1] J. Hoffmann, B. Nebel. ``The FF planning system: fast plan generation through heuristic search''. J. Artif. Int. Res. 14, 1, 253-302, 2001.
 

### 2015-05-13 documentation/ps4.tex
made edits

@@
 We ran our test scenarios on the Baxter robot [Fig. \ref{fig:baxter}], designed by Rethink Robotics. 
-Baxter is a humanoid robot with two 7 degree of freedom arms. 
+Baxter is a humanoid robot with two 7 degree of freedom arms and a fixed based. 
 Our tests used only the right arm with the two finger gripper.
@@
 
-We present an interface between a task planner and motion planner [2]. 
+We present an interface between a task planner and a motion planner [2]. 
 Baxter executes a variety of tests to measure the performance of the interface layer. 
@@
 
-The goal of the first test is to move the object at the center of a 3x3 square grid of objects to a goal surface. 
+The goal of the first test is to move the object at the center of a $3\times3$ square grid of objects to a goal surface. 
+In order to achieve the goal, Baxter must move some of the blocks surrounding the center block before placing the center block on the target surface.
 The goal of the second test is to sort red, green, and blue blocks into separate bins.
+For this task, the high level plan must ensure that Baxter does not try to pick up a block that is surrounded by other blocks.
 Figure \ref{fig:scenarios} shows the setup of the different test scenarios.
@@
 
-Given that the pose generation and state update vary between domains, we implement domain specific pose generator class and state update function for the scenarios described in section \ref{tests}.
+Given that the pose generation and state update vary between domains, we implement domain specific pose generator class and state update function for the scenarios described in Section \ref{tests}.
 
@@
 \centering
-\def\svgwidth{0.5\textwidth}
+\def\svgwidth{0.7\textwidth}
 \input{figures/blockDiagram.pdf_tex}
@@
 \subsection{Motion Planner}
-We used the MoveIt! motion planner [3]. We implenented a ROS service wrapper for this off-the-shelf motion planner so as to comply with the API.
+We used the MoveIt! motion planner [3]. 
+We implenented a ROS service wrapper for this off-the-shelf motion planner so as to comply with the API.
 It takes as input the state of the world, the action to be performed, and a pose goal (i.e. a series of waypoints to perform the action).
-MoveIt!
-is then used to instantiate motion plans between these waypoints.
-The motion planner service returns a boolean specifying the success/failure of the instantiation of the motion plan, the motion plan itself, and the updated world state (which can be unchanged if the action failed).
+MoveIt! is then used to instantiate motion plans between these waypoints. 
+The motion planner service returns a boolean specifying the success or failure of the instantiation of the motion plan, the motion plan itself, and the updated world state (which can be unchanged if the action failed).
 
@@
 \centering
-\includegraphics[width=\textwidth]{figures/figure4.png}
+\includegraphics[width=\textwidth]{figure4}
 \caption{Illustration of the interface layer’s refinement process. 
@@
 	\centering
-	\subfloat{\includegraphics[width=.45\linewidth]{figures/algorithm1}}
+	\subfloat{\includegraphics[width=.45\linewidth]{algorithm1}}
 	\qquad
-	\subfloat{\includegraphics[width=.45\linewidth]{figures/algorithm2}}
+	\subfloat{\includegraphics[width=.45\linewidth]{algorithm2}}
 	\caption{Pseudo-code for the underlying algorithms of the interface layer. Taken from [2]\label{fig:algorithms}}
@@
 From there, we look for a high level plan.  
-If we do succeed at finding a high level task plan, we begin the process of attempting to find a motion corresponding to each action.
+If we succeed at finding a high level task plan, we begin the process of attempting to find a motion corresponding to each action.
 
@@
 Each pose is made up of a set of waypoints. 
+We generate multiple waypoints for an action to ensure that the motions avoid collisions.
 
-For the PICKUP action, it generates the following waypoints: near the object and pointing towards it, touching the object, lifting the object, and a standard home position. 
-The first waypoint is randomly generated and places the gripper about 15 centimeters away from the object.
+For the PICKUP action, it generates the following waypoints: a pre-grasp near the object and pointing towards it, touching the object, grasping the object, lifting the object, and a standard home position.
+The pre-grasp is randomly generated and places the gripper about 15 centimeters away from the object.
 We divided the set of possible random yaw angles around the object into several distinct ranges, called \textit{slices}. 
@@
 The second waypoint moves the arm so that the object is in the gripper. 
-The third waypoint is in the exact same position with the gripper closed. 
-The next waypoint is directly above the previous waypoint, high enough so that the object is above all of the other objects on the table. 
-Finally, the last waypoint goes to the standard home position for the square grid task and moves  above the correct bin for the sorting task.
+The grasping waypoint is in the exact same position with the gripper closed. 
+The lifting waypoint is directly above the grasping waypoint, high enough so that the object is above all of the other objects on the table. 
+Finally, the last waypoint goes to the standard home position.
 
-For the PUTDOWN action, the pose generator generates the following waypoints: above the target location, at the target location with the gripper closed, at the target location with the gripper open, 15 cm backed away from the target location, and the standard home position.
+For the PUTDOWN action, the pose generator generates the following waypoints: above the target location, a set down position with the gripper closed, a set down position with the gripper open, 15 cm backed away from the target location, and the standard home position.
 The target location is randomly generated, but the pose generator checks to make sure that no objects are at or near the target location.
@@
 This enables us to find plans a lot more quickly: whenever a plan is possible, we find it by backtracking search.  
-Often, the first pose that's tried won't be viable but another pose will.  
+Often, the first pose that is tried will not be viable but another pose will.  
 Partial trajectory mode will only try the first pose before giving up and identifying blocking objects.
@@
 In simulation, Baxter successfully moves blocks to reach the target center block and places the center block on the target surface.
-A video of the successful test trial in simulation can be found at [TODO: link here].  We did not run this test on the real Baxter robot.
+A video of the successful test trial in simulation can be found at [TODO: link here].  
+We did not run this test on the real Baxter robot.
 

### 2015-05-14 documentation/ps4.tex
Changes to final paper

@@
 In simulation, Baxter successfully moves blocks to reach the target center block and places the center block on the target surface.
-A video of the successful test trial in simulation can be found at [TODO: link here].  
+A video of the successful test trial in simulation can be found at \url{http://youtu.be/Jb9EOZ8B2lU}.  
 We did not run this test on the real Baxter robot.
@@
 
-Task & \shortstack{Number of \\Blocks} & \shortstack{Blocks to Move} & \shortstack{Number of \\TP Calls} & \shortstack{Number of \\MP Calls} & Runtime \\ \hline
-Square Grid & 9 & 1 & ? & ? & ?\\
+Task & Trial & \shortstack{Number of \\Blocks} &\shortstack{Blocks to Move} & \shortstack{Number of \\TP Calls} & \shortstack{Number of \\MP Calls} & Runtime (min) \\ \hline
+Square Grid & 1 & 9 & 1 & 3 & 721 & 21.45\\
 \hline
-Sorting & 9 & 9 & ? & ? & ?\\
+ & 2 &  &  & 3 & 1376 & 86.98\\
 \hline
+ & 3 &  &  & 3 & 1198 & 80.11\\
+\hline
+ & \textbf{Avg} &  &  & \textbf{3} & \textbf{1098.33} & \textbf{62.85}\\
+
+\hline
+Sorting & 1 & 9 & 9 & 8 & 353 & 22.33\\
+\hline
+ & 2 &  &  & 6 & 304 & 15.97\\
+\hline
+ & 3 &  &  & 6 & 379 & 20.76\\
+ \hline
+ & \textbf{Avg} &  &  & \textbf{6.67} & \textbf{345.33} & \textbf{19.69}\\
 
@@
 
-[3] I. A. Sucan and Sachin Chitta, ``MoveIt!''. [Online] Available: http://moveit.ros.org
+[3] I. A. Sucan and Sachin Chitta, ``MoveIt!''. [Online] Available: \url{http://moveit.ros.org}
 
